### 2019-09-24 paper.tex
Initial commit. Starting to expand to inlcude full results for journal

\documentclass{article}

\usepackage{booktabs}
\usepackage[ruled]{algorithm2e}

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[caption=false]{subfig}
\usepackage[capitalise]{cleveref}
\usepackage{todonotes}

\begin{document}

\title{TBA}

\author{TBA}

%\title{Bone-Conduction Audio Interface to Guide People with Visual Impairments}

%\author{Jacobus C. Lock\inst{1} \and 
%Iain D. Gilchrist\inst{2} \and
%Grzegorz Cielniak\inst{1} \and
%Nicola Bellotto\inst{1}}

%\institute{University of Lincoln, Lincoln, LN6 7TS, UK \email{\{jlock, gcielniak, nbellotto\}@lincoln.ac.uk} \and
	   %University of Bristol, Bristol, BS8 1TH, UK \email{i.d.gilchrist@bristol.ac.uk}}

%\authorrunning{Jacobus C. Lock et.\ al.}
%\titlerunning{Bone-conduction Interface For People with Visual Impairments}

\maketitle
%\setcounter{footnote}{0}

\begin{abstract}
  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
  To this end, we propose a new audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
  The vertical position on the median plan is given by adjusting the tone's pitch to overcome the audio localisation limitations of bone-conduction headphones. 
  This interface is validated through a set of experiments with blindfolded and visually impaired participants. 
%\keywords{Human-machine interface \and vision impairment \and spatialised sound \and varying pitch \and bone-conduction}
\end{abstract}

\section{Introduction}

In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society.
The UK's Royal National Institute of Blind People (RNIB) for example has prioritised improving access to everyday services and products, such as public transport and mobile apps~\cite{rnib2016uk}.
Improvements in modern computing have made it possible for new and innovative solutions to these problems to come to the fore.
In particular, researchers in the active vision field have have made much progress in enabling machines to autonomously manipulate cameras to gather information about an environment for mapping and object finding tasks~\cite{bajcsy2018revisiting,lock2019active}.
There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus on that point?
If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point or object of interest and identify an unknown scene.

The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to deliver a mobile guidance system that will ultimately be able to guide a user with vision impairments on the last leg of their journey, i.e.\ the so-called `last 10-yard problem'. 
The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango} and \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities. 
It also provides access to Android's full range of interface tools and I/O options. 
Furthermore, a set of bone-conduction headphones (pictured in \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
~
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).}
\end{figure}

Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can easily be interpreted without posing a significant cognitive load.
A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
A similar approach was used in~\cite{durette2008visuo}, but the study did not focus on or investigate the interface's efficacy.
Indeed, the work presented in this paper serves as an initial study into an interface that can effectively communicate the pan and elevation angles of a target location through a set of bone-conduction headphones using standard audio libraries and audio manipulations.
Furthermore, we demonstrate this approach's effectiveness through a simple experiment.

The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a discussion on the design and implementation of our interface in \cref{sec:interface-design}.
This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiment-and-results}.
Finally, the paper concludes with a summary and a short discussion on future research prospects in \cref{sec:conclusion}.

\section{Previous Work}\label{sec:prev-work}

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\cite{arditi2013user}.
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.

Researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\cite{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}. 
This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
However, these studies focussed on their system's total effectiveness, rather than the effectiveness of the pitch adjustment mechanism alone. In the next sections we want to investigate this more closely.

\section{Interface Description}\label{sec:interface-design}

\subsection{Hardware Selection}

Electronic navigation aids and guidance systems for people with vision impairments often have acceptability and usability problems due to limitations in academic research and prototypes, such as prohibitive costs, unfriendly user interfaces and significant hardware requirements (e.g.\ head-mounted cameras and GPS antennae)~\cite{golledge2004stated,yusif2016older,arditi2013user}.
Indeed, the traditional walking cane remains the standard tool for navigation and obstacle avoidance. 
With the ActiVis system, we aim to tackle the issue of cost, user-acceptance and usability by using only off-the-shelf devices and hardware, as far as possible, and avoiding any special requirements.
Following this design principle, we adopted a hand-held mobile device and a discreet headset to avoid the person standing out in public places while using the system.
The ActiVis system is based on a concept proposed in~\cite{lock2017portable,lock2019active} that uses a Google Tango device that is able to localise itself in real-time and has the benefit of a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.

A set of bone-conduction headphones is used as the audio transmission medium.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
Alternative solutions, such as open-back headphones, were also considered. These allow ambient noise through, but they still filter the incoming sound. The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.

\subsection{Human Audio Localisation}

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, tricking the brain into believing a sound is located at some arbitrary position.
An HRTF is a mathematical function that simulates the response signal of a human head and is derived by capturing key characteristics that affect the monaural and binaural responses, such as the user's hearing levels and head size.
Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\cite{gardner1995hrtf}.

\subsection{Interface Design}

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\cite{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.6\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis.}
\end{figure}

\subsubsection{Pan}

The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\cite{blauert1969sound}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume.

In this work, a pure sinusoidal wave was used. 
People typically have trouble localising a pure tone without a sufficiently rich spectral signature.
However, the ITD and ILD are independent of the tone's spectral make-up, while the elevation angle is given through a different mechanism. Therefore, a pure sine wave is suitable to convey the target's pan angle.
To transform and spatialise the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\cite{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.

\subsubsection{Elevation}

A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\cite{macdonald2006spatial,schonstein2008comparison}.
To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
When the camera vector is at the correct elevation, the tone pitch is set to neutral.
When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\cite{pratt1930spatial,blauert1997spatial}.
An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\cite{shepard1964circularity}.
The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.

The pitch is changed as a linear function of the elevation angle and the gradient is determined by setting the angle and pitch limits.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
After practical tests with the interface, we set the neutral pitch to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
We set the pitch limits to 2 octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
The linear function is visualised in \cref{fig:pitch-gain}.

\subsection{Implementation}

A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of the information flow.
When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
The audio generator then produces a tone based on the difference between the device and the target's positions. The tone is sent to the audio output channel, which plays it back to the user.
A WiFi recording module is constantly monitoring the different values of the device's parameters and of the target's position, as well as the system's output, recording everything to a remotely stored datafile.

\begin{figure}[t]
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.9\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
\end{figure}

\section{Experiments}\label{sec:experiment}

To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
The participants are given a Tango device running an app written for the experiment that generates a set of virtual targets and presents them to each participants, one at a time. 
The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
Each target's angular position is communicated to the participant through the audio interface, the output of which is adjusted in real-time as the participant points the device around. 
When a participant was confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
A total of 28 targets were generated per participant.

Two groups of participants were recruited for the experiments. 
Group \textit{G1} consisted of 10 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 4 people with severe visual impairments. 
Both groups were given some time before the experiments to familiarise with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
To minimise the speed/accuracy biases in the results, we asked the participants to focus on finding the targets, without worrying about the time it took.

\section{Results}\label{sec:results}

The data collected during the experiment were clustered together by participant groups and analysed.
Similar to the results from~\cite{macdonald2006spatial,schonstein2008comparison}, we use the absolute mean errors for each dimension, which allows us to compare our results to the aforementioned works'. 
These results are presented in the boxplots in \cref{fig:err-results-fig} and summarised in \cref{tab:results}.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:err-results-abs}\includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err_abs.png}}
\quad
  \subfloat[]{\label{fig:err-results}\includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err.png}}
  \caption{Boxplots of the absolute (top) and signed (bottom) angular errors collected during the pointing experiment. }\label{fig:err-results-fig}
\end{figure}

\begin{table}
  \centering
  \caption{A summary of the results collected from the experiment. }\label{tab:results}
  \begin{tabular}{p{1cm}p{2cm}p{2.2cm}@{\hskip 1cm}p{3.2cm}}
    \toprule
    &           & Mean absolute error [rad]  & Spearman Correlation score \\ \midrule
    \multirow{2}{*}{\textit{G1}} & Pan       & $0.23\pm0.24$ & $0.88\;(p<0.001)$ \\
				 & Elevation & $0.25\pm0.28$ & $0.64\;(p<0.001)$ \\ \midrule
    \multirow{2}{*}{\textit{G2}} & Pan       & $0.45\pm0.21$ & $0.41\;(p<0.001)$ \\
				 & Elevation & $0.36\pm0.32$ & $0.61\;(p<0.001)$ \\
    \bottomrule
  \end{tabular}
\end{table}

The average pan error from group \textit{G1} falls well within the ranges observed in~\cite{macdonald2006spatial,schonstein2008comparison} of $[0.16, 0.38]$ radians and $[0.17, 0.26]$ radians respectively. 
Indeed, the majority of samples fall even within the latter, more conservative range. 
However, the participants with visual impairments in group \textit{G2}  demonstrate a wider spread in error data and higher average error than \textit{G1} (0.23 vs. 0.45 radians, Kruskal-Wallis test $p<0.001$). 
The results in~\cite{katz2011spatial,zwiers2001spatial} reported a similar trend, although an investigation with a larger sample size for \textit{G2} should be considered before definitive conclusions can be made.

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous experimental results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2}, respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, all the participants in~\cite{stanley2006lateralization} had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for both groups are centred around the negative angle, as shown in \cref{fig:err-results}, indicating a possible underlying bias either in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization}. Further investigation with a larger participant pool is needed to determine this underlying bias, if any.

\begin{figure}
  \centering
  \includegraphics[width=1.0\columnwidth]{figures/correlation.png}
  \caption{Scatter plots that show the targets' actual positions and the participants' guesses, as well as the line of best fit showing the relationship between the data. }\label{fig:correlation-results}
\end{figure}

The error data was used to generate scatter plots that show the correlation between the target's direction presented by the guidance system to the participants and the one they thought the targets were.
These plots are given in \cref{fig:correlation-results} and show a reasonably positive correlation between the guidance and the selected targets, indicating that the participants correctly interpreted the interface's output in most of the cases. 
The Spearman correlation scores for each dataset, listed in \cref{tab:results}, confirm this, as well as the negative angle bias in the elevation dimensions.

\section{Conclusion}\label{sec:conclusion}

In this work, we proposed a new audio interface that conveys a target's pan and elevation angles through a spatialised audio tone.
The tone's pitch is adjusted to convey the elevation and compensate for the shortcomings of bone-conduction headsets in transmitting the elevation component of a spatialised signal.
The results obtained from a simple pointing experiment are encouraging as they show improved performance over purely spatialised signals transmitted via bone-conduction headphones.
Furthermore, the limitations of the latter were largely overcome by communicating the target's elevation with the tone's pitch, achieving pan and elevation errors comparable to that of normal over-ear headphones.

Future work should consider a more in-depth investigation with a larger participant pool and a more detailed statistical analysis.
Interesting questions include whether adjusting the gradient of the elevation function would make it easier for the user to guess the actual target's elevation, and to what degree the performance of participants with limited and healthy eyesight differs.
Furthermore, experiments with a large group of people with visual impairments would provide an opportunity to gauge their opinion on the interface and identify possible avenues of improvements.
Finally, it would be interesting to incorporate a co-adaptation mechanism between human and assistive device, as suggested in~\cite{gallina2015progressive}, to improve its usability and performance over time.

\paragraph{{\bf Acknowledgements.}}\label{sec:acknowledge}
This research is partly supported by a Google Faculty Research Award.
We would like to thank the Voluntary Centre Services UK for their help in facilitating the experiments with people with limited vision.

\bibliographystyle{splncs04}
\bibliography{bib}

\end{document}

### 2019-09-26 paper.tex
Restarting paper, added data processing

@@
 \documentclass{article}
-
-\usepackage{booktabs}
-\usepackage[ruled]{algorithm2e}
-
-\usepackage{siunitx}
-\usepackage{graphicx}
-\usepackage{multirow}
-\usepackage[caption=false]{subfig}
-\usepackage[capitalise]{cleveref}
-\usepackage{todonotes}
 
@@
 
-\title{TBA}
-
-\author{TBA}
-
-%\title{Bone-Conduction Audio Interface to Guide People with Visual Impairments}
-
-%\author{Jacobus C. Lock\inst{1} \and 
-%Iain D. Gilchrist\inst{2} \and
-%Grzegorz Cielniak\inst{1} \and
-%Nicola Bellotto\inst{1}}
-
-%\institute{University of Lincoln, Lincoln, LN6 7TS, UK \email{\{jlock, gcielniak, nbellotto\}@lincoln.ac.uk} \and
-	   %University of Bristol, Bristol, BS8 1TH, UK \email{i.d.gilchrist@bristol.ac.uk}}
-
-%\authorrunning{Jacobus C. Lock et.\ al.}
-%\titlerunning{Bone-conduction Interface For People with Visual Impairments}
-
-\maketitle
-%\setcounter{footnote}{0}
-
-\begin{abstract}
-  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
-  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
-  To this end, we propose a new audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
-  The vertical position on the median plan is given by adjusting the tone's pitch to overcome the audio localisation limitations of bone-conduction headphones. 
-  This interface is validated through a set of experiments with blindfolded and visually impaired participants. 
-%\keywords{Human-machine interface \and vision impairment \and spatialised sound \and varying pitch \and bone-conduction}
-\end{abstract}
-
 \section{Introduction}
 
-In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society.
-The UK's Royal National Institute of Blind People (RNIB) for example has prioritised improving access to everyday services and products, such as public transport and mobile apps~\cite{rnib2016uk}.
-Improvements in modern computing have made it possible for new and innovative solutions to these problems to come to the fore.
-In particular, researchers in the active vision field have have made much progress in enabling machines to autonomously manipulate cameras to gather information about an environment for mapping and object finding tasks~\cite{bajcsy2018revisiting,lock2019active}.
-There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus on that point?
-If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point or object of interest and identify an unknown scene.
+\section{Previous Work}
 
-The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to deliver a mobile guidance system that will ultimately be able to guide a user with vision impairments on the last leg of their journey, i.e.\ the so-called `last 10-yard problem'.
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango} and \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
-It also provides access to Android's full range of interface tools and I/O options. 
-Furthermore, a set of bone-conduction headphones (pictured in \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
+\section{System Description}
 
-\begin{figure}[t]
-  \centering
-  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
-~
-  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
-~
-  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
-  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).}
-\end{figure}
-
-Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can easily be interpreted without posing a significant cognitive load.
-A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
-In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
-However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-A similar approach was used in~\cite{durette2008visuo}, but the study did not focus on or investigate the interface's efficacy.
-Indeed, the work presented in this paper serves as an initial study into an interface that can effectively communicate the pan and elevation angles of a target location through a set of bone-conduction headphones using standard audio libraries and audio manipulations.
-Furthermore, we demonstrate this approach's effectiveness through a simple experiment.
-
-The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a discussion on the design and implementation of our interface in \cref{sec:interface-design}.
-This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiment-and-results}.
-Finally, the paper concludes with a summary and a short discussion on future research prospects in \cref{sec:conclusion}.
-
-\section{Previous Work}\label{sec:prev-work}
-
-Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
-The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
-In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
-However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
-Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
-Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\cite{arditi2013user}.
-Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
-
-Researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\cite{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
-However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
-This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
-In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
-However, these studies focussed on their system's total effectiveness, rather than the effectiveness of the pitch adjustment mechanism alone.
-In the next sections we want to investigate this more closely.
-
-\section{Interface Description}\label{sec:interface-design}
-
-\subsection{Hardware Selection}
-
-Electronic navigation aids and guidance systems for people with vision impairments often have acceptability and usability problems due to limitations in academic research and prototypes, such as prohibitive costs, unfriendly user interfaces and significant hardware requirements (e.g.\ head-mounted cameras and GPS antennae)~\cite{golledge2004stated,yusif2016older,arditi2013user}.
-Indeed, the traditional walking cane remains the standard tool for navigation and obstacle avoidance. 
-With the ActiVis system, we aim to tackle the issue of cost, user-acceptance and usability by using only off-the-shelf devices and hardware, as far as possible, and avoiding any special requirements.
-Following this design principle, we adopted a hand-held mobile device and a discreet headset to avoid the person standing out in public places while using the system.
-The ActiVis system is based on a concept proposed in~\cite{lock2017portable,lock2019active} that uses a Google Tango device that is able to localise itself in real-time and has the benefit of a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
+Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
+Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\cite{golledge2004stated,yusif2016older,arditi2013user}.
+To address these issues, we implemented a handheld mobile system that is based on a concept proposed in~\cite{lock2017portable,lock2019active} and tested in~\cite{lock2019bone} that uses a Google Tango device that is able to localise itself in real-time.
+This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
 
@@
 
-\subsection{Human Audio Localisation}
+\subsection{Audio Interface}
 
@@
 However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\cite{gardner1995hrtf}.
-
-\subsection{Interface Design}
 
@@
 
-\subsubsection{Pan}
+\subsubsection{Pan Dimension}
 
@@
 
-\subsubsection{Elevation}
+\subsubsection{Elevation Dimension}
 
@@
 
+\section{Experiments}
+
 \subsection{Implementation}
@@
 
-\section{Experiments}\label{sec:experiment}
+\subsection{Participant Characterisation}
+
+In addition to the target searching experiment, another set of experiments were conducted to characterise the participants' hearing characteristics.
+The characteristics that were measured were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies.
+These results will be used to provide context to the results captured during the target search experiment and provide additional insight on any possible biases or limitations.
+
+\subsubsection{Sound Localisation}
+
+In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
+To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
+The participant then had to select the direction the sound came from.
+The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it progressively harder to localise.
+
+For this progressive increase in difficulty, a 2-up, 1-down step process is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves.
+Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
+We also use 2 different step sequences, one starting at a large distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' progression respectively.
+The terminating condition for the experiment is when the 2 sequences converge to within 2 intervals of one another for 3 consecutive guesses.
+This gives a distance band within which the participant is capable of localising the sound source.
+Each participant performed this experiment three times.
+
+\subsubsection{Pitch Discrimination}
+
+Here we determined a participant's ability to differentiate the pitches of 2 tones being played to them, i.e.\ how well they can tell if a tone is high or low pitched.
+We played 2 tones to the participants in succession with the second tone being higher or lower-pitched than the first.
+The participants were then asked to select whether they interpreted the second tone as higher or lower-pitched than the first.
+
+The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
+The tone difference depends on how well the participant can tell the tones apart.
+Like the sound localisation experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved and is doubled for every incorrect answer.
+2 step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
+The termination condition is when the 2 step sequences are within 1 octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2^1$) for 3 consecutive answers.
+Each participant performed this experiment twice.
+
+\subsection{Target Search}
 
 To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
-The participants are given a Tango device running an app written for the experiment that generates a set of virtual targets and presents them to each participants, one at a time. 
+The participants were given a Tango device running an app written for the experiment that generates a set of virtual targets and presents them to each participants, one at a time. 
 The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
@@
 
+\subsection{Metrics}
+
+We use two different metrics to compare the three different pitch gradient settings: the acquisition accuracy and search time.
+The accuracy is given as the difference between the Tango's orientation at the time the participant confirmed they were on target, and the target's actual orientation.
+We separate the results of the tilt and pan dimensions in order to see how the different pitch gradients affect a participant's pointing accuracy.
+
+We also compare the performance of the three pitch gradient settings in terms of the time it takes each participant to find a target.
+However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
+Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
+It also provides a so-called `index of performance' that we can use as a metric to compare the results between the three configurations.
+
+Here we briefly summarise the equations and quantities involved in our metric.
+Fitts's Law is given by
+
+\begin{equation}
+  \label{eq:fitts-base}
+  t = a + bID,
+\end{equation}
+
+\noindent
+where $t$ is the time it takes to find a target, $a$ and $b$ are constants determined through regression and $ID$ is a description of the difficulty of the target, given as logarithmic function of the ratio between the distance to the target and the target's width.
+In our case, the targets have no width, since they are points in space, and we therefore use MacKenzie's modified form for $ID$, given by
+
+\begin{equation}
+  \label{eq:fitts-id}
+  ID = \log_2\left(\frac{\theta}{w_e} + 1\right).
+\end{equation}
+
+\noindent
+Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\cite{welford1968fundamentals}, given by
+
+\begin{equation}
+  \label{eq:fitts-we}
+  w_e = \sqrt{2\pi e}\sigma = 4.133\sigma,
+\end{equation}
+
+\noindent
+where $\sigma$ is the standard deviation of the error data, taken as the angle between the participant's target selection and target's actual angular position.
+Fitts's index of performance, $IP$, can then be calculated using
+
+\begin{equation}
+  \label{eq:fitts-performance}
+  IP = \frac{ID}{t},
+\end{equation}
+
+\noindent
+where $IP = \frac{1}{t}$ when $\sigma=0$.
+
+\subsection{Procedure}
+
 Two groups of participants were recruited for the experiments. 
-Group \textit{G1} consisted of 10 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 4 people with severe visual impairments. 
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 12 people with severe visual impairments. 
 Both groups were given some time before the experiments to familiarise with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
@@
 
-\section{Results}\label{sec:results}
+\section{Results}
 
-The data collected during the experiment were clustered together by participant groups and analysed.
-Similar to the results from~\cite{macdonald2006spatial,schonstein2008comparison}, we use the absolute mean errors for each dimension, which allows us to compare our results to the aforementioned works'.
-These results are presented in the boxplots in \cref{fig:err-results-fig} and summarised in \cref{tab:results}.
-
-\begin{figure}
-  \centering
-  \subfloat[]{\label{fig:err-results-abs}\includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err_abs.png}}
-\quad
-  \subfloat[]{\label{fig:err-results}\includegraphics[width=0.7\columnwidth]{figures/pan_tilt_err.png}}
-  \caption{Boxplots of the absolute (top) and signed (bottom) angular errors collected during the pointing experiment. }\label{fig:err-results-fig}
-\end{figure}
-
-\begin{table}
-  \centering
-  \caption{A summary of the results collected from the experiment. }\label{tab:results}
-  \begin{tabular}{p{1cm}p{2cm}p{2.2cm}@{\hskip 1cm}p{3.2cm}}
-    \toprule
-    &           & Mean absolute error [rad]  & Spearman Correlation score \\ \midrule
-    \multirow{2}{*}{\textit{G1}} & Pan       & $0.23\pm0.24$ & $0.88\;(p<0.001)$ \\
-				 & Elevation & $0.25\pm0.28$ & $0.64\;(p<0.001)$ \\ \midrule
-    \multirow{2}{*}{\textit{G2}} & Pan       & $0.45\pm0.21$ & $0.41\;(p<0.001)$ \\
-				 & Elevation & $0.36\pm0.32$ & $0.61\;(p<0.001)$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-The average pan error from group \textit{G1} falls well within the ranges observed in~\cite{macdonald2006spatial,schonstein2008comparison} of $[0.16, 0.38]$ radians and $[0.17, 0.26]$ radians respectively.
-Indeed, the majority of samples fall even within the latter, more conservative range. 
-However, the participants with visual impairments in group \textit{G2}  demonstrate a wider spread in error data and higher average error than \textit{G1} (0.23 vs.
-0.45 radians, Kruskal-Wallis test $p<0.001$).
-The results in~\cite{katz2011spatial,zwiers2001spatial} reported a similar trend, although an investigation with a larger sample size for \textit{G2} should be considered before definitive conclusions can be made.
-
-The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous experimental results on human audition~\cite{barfield1997visual}.
-The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2}, respectively.
-As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
-Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
-Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
-There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
-However, all the participants in~\cite{stanley2006lateralization} had healthy eyesight, making the latter comparison invalid. 
-Interestingly, the elevation errors for both groups are centred around the negative angle, as shown in \cref{fig:err-results}, indicating a possible underlying bias either in the participants or the interface.
-A similar trend was observed in~\cite{stanley2006lateralization}. Further investigation with a larger participant pool is needed to determine this underlying bias, if any.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=1.0\columnwidth]{figures/correlation.png}
-  \caption{Scatter plots that show the targets' actual positions and the participants' guesses, as well as the line of best fit showing the relationship between the data.
-}\label{fig:correlation-results}
-\end{figure}
-
-The error data was used to generate scatter plots that show the correlation between the target's direction presented by the guidance system to the participants and the one they thought the targets were.
-These plots are given in \cref{fig:correlation-results} and show a reasonably positive correlation between the guidance and the selected targets, indicating that the participants correctly interpreted the interface's output in most of the cases.
-The Spearman correlation scores for each dataset, listed in \cref{tab:results}, confirm this, as well as the negative angle bias in the elevation dimensions.
-
-\section{Conclusion}\label{sec:conclusion}
-
-In this work, we proposed a new audio interface that conveys a target's pan and elevation angles through a spatialised audio tone.
-The tone's pitch is adjusted to convey the elevation and compensate for the shortcomings of bone-conduction headsets in transmitting the elevation component of a spatialised signal.
-The results obtained from a simple pointing experiment are encouraging as they show improved performance over purely spatialised signals transmitted via bone-conduction headphones.
-Furthermore, the limitations of the latter were largely overcome by communicating the target's elevation with the tone's pitch, achieving pan and elevation errors comparable to that of normal over-ear headphones.
-
-Future work should consider a more in-depth investigation with a larger participant pool and a more detailed statistical analysis.
-Interesting questions include whether adjusting the gradient of the elevation function would make it easier for the user to guess the actual target's elevation, and to what degree the performance of participants with limited and healthy eyesight differs.
-Furthermore, experiments with a large group of people with visual impairments would provide an opportunity to gauge their opinion on the interface and identify possible avenues of improvements.
-Finally, it would be interesting to incorporate a co-adaptation mechanism between human and assistive device, as suggested in~\cite{gallina2015progressive}, to improve its usability and performance over time.
-
-\paragraph{{\bf Acknowledgements.}}\label{sec:acknowledge}
-This research is partly supported by a Google Faculty Research Award.
-We would like to thank the Voluntary Centre Services UK for their help in facilitating the experiments with people with limited vision.
-
-\bibliographystyle{splncs04}
-\bibliography{bib}
+\section{Conclusion}
 

### 2019-09-26 data_proc/DataClass.py

@@ -1,0 +1,1399 @@
+#!/usr/bin/python
+
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import csv 
+import matplotlib.pyplot as plt
+import matplotlib.mlab as ml
+import numpy as np
+import glob
+import math
+
+from scipy import stats, optimize
+from geo import Vector, Quaternion
+from scipy import interpolate as interp
+from mpl_toolkits.mplot3d import Axes3D
+from statsmodels.graphics.gofplots import qqplot
+from matplotlib.ticker import FormatStrFormatter
+from matplotlib.ticker import StrMethodFormatter
+
+class Utils:
+    def plot_user_time_to_target(self, data, user):
+        colour = ['r', 'g', 'b']
+        c = 0
+        for seq in data.keys():
+            for dset in data[seq]:
+                if user in dset.file:
+                    print(dset.file, user)
+                    diff = []
+                    for i in range(len(dset.target_indices) - 1):
+                        if dset.data['tz'][dset.target_indices[i + 1]] == 0 or dset.data['tz'][dset.target_indices[i]] == 0:
+                            continue
+                        diff.append(dset.data['time'][dset.target_indices[i + 1]] - dset.data['time'][dset.target_indices[i]])
+                    plt.plot(diff, colour[c], label=str(seq + ' average: ' + str(np.average(np.array(diff)))))
+                    plt.plot((0, len(diff)), (np.average(np.array(diff)), np.average(np.array(diff))), colour[c])
+                    c = (c + 1) % 3
+        plt.legend()
+        plt.grid()
+        plt.show()
+        
+    def get_angles(self, q):
+
+        q.normalise()
+        # Rotate Tango orientation to fall onto the world axis system
+        orientation = q
+        orientation.normalise()
+
+        forward_vector = Vector(0.0, 0.0, 1.0)
+        forward_facing_vector = forward_vector.rotate_vector(orientation)
+        forward_facing_vector.normalise()
+
+        tango_roll = Vector(forward_facing_vector.x, forward_facing_vector.y, 0)
+        tango_roll.normalise()
+        tango_pitch = Vector(0, forward_facing_vector.y, forward_facing_vector.z)
+        tango_pitch.normalise()
+        tango_yaw = Vector(forward_facing_vector.x, 0, forward_facing_vector.z)
+        tango_yaw.normalise()
+        
+        roll_axis = Vector(1, 1, 0)
+        roll_axis.normalise()
[…]

### 2019-09-26 data_proc/geo.py

@@ -1,0 +1,101 @@
+import math
+
+class Vector:
+    def __init__(self, x, y, z):
+        self.x = x
+        self.y = y
+        self.z = z
+        
+        self.len = math.sqrt(self.x ** 2 + self.y ** 2 + self.z ** 2)
+
+    def __str__(self):
+        return "{} {} {}".format(self.x, self.y, self.z)
+
+    def normalise(self):
+        try:
+            self.x /= self.len
+            self.y /= self.len
+            self.z /= self.len
+        except ZeroDivisionError:
+            print('Warning: Length of the vector seems to be zero.')
+
+    def dot_product(self, v):
+        return self.x * v.x + self.y * v.y + self.z * v.z
+
+    def inv_dot_product(self, v):
+        return math.acos(self.dot_product(v))
+
+    def cross_product(self, v):
+        return Vector(self.y * v.z - self.z * v.y, self.z * v.x - self.x * v.z, self.x * v.y - self.y * v.x)
+
+    def rotate_vector(self, q):
+        x = (1 - 2 * q.y * q.y - 2 * q.z * q.z) * self.x +\
+                2 * (q.x * q.y + q.w * q.z) * self.y +\
+                2 * (q.x * q.z - q.w * q.y) * self.z
+        y = 2 * (q.x * q.y - q.w * q.z) * self.x +\
+                (1 - 2 * q.x * q.x - 2 * q.z * q.z) * self.y +\
+                2 * (q.y * q.z + q.w * q.x) * self.z
+        z = 2 * (q.x * q.z + q.w * q.y) * self.x +\
+                2 * (q.y * q.z - q.w * q.x) * self.y +\
+                (1 - 2 * q.x * q.x - 2 * q.y * q.y) * self.z
+        # print('Pre-rotate: {} {} {}'.format(x, y, z))
+
+        return Vector(x, y, z)
+
+    def get_len(self):
+        return self.len
+
+class Quaternion:
+    def __init__(self, *args, **kwargs):
+        if kwargs.get('x') != None:
+            self.x = kwargs.get('x')
+            self.y = kwargs.get('y')
+            self.z = kwargs.get('z')
+            self.w = kwargs.get('w')
+
+        elif kwargs.get('vector') != None:
+            v = kwargs.get('vector')
+            d = kwargs.get('angle')
+
+            self.x = v.x * math.sin(d / 2.0)
+            self.y = v.y * math.sin(d / 2.0)
[…]

### 2019-09-26 paper.tex
Added bib to paper file
Added results section

@@
 \documentclass{article}
+
+\usepackage{cleveref}
+\usepackage{graphicx}
+\usepackage[caption=false]{subfig}
+\usepackage{siunitx}
 
@@
 
-Two groups of participants were recruited for the experiments. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 12 people with severe visual impairments. 
-Both groups were given some time before the experiments to familiarise with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
-To minimise the speed/accuracy biases in the results, we asked the participants to focus on finding the targets, without worrying about the time it took.
+Two groups of participants were recruited for the experiments on a volunteer basis. 
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 12 people with severe visual impairments (18-55 years old, 40 male, 14 female).
+None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
+Each participant performed 3 sets of experiments each, with the 2 characterisation experiments preceding the final target-search experiment. 
+Both groups were given some time before the experiment target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
+Furthermore, to minimise the speed/accuracy biases in the results for this experiment, we asked the participants to focus on finding the targets, without worrying about the time it took.
 
@@
 
+\subsection{Sound Localisation}
+
+\subsection{Pitch Discrimination}
+
+\subsection{Target Search}
+
 \section{Conclusion}
 
+\bibliographystyle{plain}
+\bibliography{bib}
+
 \end{document}

### 2019-10-04 paper.tex
Added new plots, refined existing plots to have correct labels, etc. Added discussions on results

@@
 
-\usepackage{cleveref}
+\usepackage{amsmath}
 \usepackage{graphicx}
@@
 \usepackage{siunitx}
+\usepackage{cleveref}
+\usepackage{todonotes}
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 12 people with severe visual impairments (18-55 years old, 40 male, 14 female).
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18-55 years old, 40 female, 16 female).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
@@
 
+\cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played to them from.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/sound_localisation.png}
+  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }
+  \label{fig:sound-localisation}
+\end{figure}
+
+From inspection of \cref{fig:sound-localisation}, it can be seen that the vast majority of guesses for both groups were correct.
+For Group \textit{G1}, the majority of erroneous guesses were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour and indicates that the participants consistently progressed through the distance intervals.
+We can therefore conclude that the participants from \textit{G1} had little difficulty determining sound direction.
+
+Group \textit{G2} also displays a concentration of erroneous guesses in the centre interval.
+However, it also has more incorrect guesses in other distance intervals and displays a more even progression through the distance intervals towards the centre.
+This could indicate that instead of terminating the experiment through bringing the 2 sequences within 1 interval of one another, there was more switching back and forth between the centre 3 intervals.
+
+These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy
+These results are in line with what we expected and are supported by literature which indicates that humans are very adept at localising a sound source, particularly in the pan dimension.
+
 \subsection{Pitch Discrimination}
 
+The results of the pitch discrimination experiment are shown in \cref{fig:pitch-discrimination} where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
+The latter is given in terms of semitone differences which is obtained with
+
+\begin{equation*}
+\label{eq:semitone-difference}
+  \Delta f = 12\log_2\frac{f_0}{f_1}.
+\end{equation*}
+
+For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone difference interval and as expected, the highest proportion of incorrect guesses occur in the $[-0.25, 0.25]$ semitone difference interval.
+The guesses from Group \textit{G2} is more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone difference interval.
+
+Assuming the differences are normally spread, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
+We then used each CDF's parameters to determine a frequency threshold where the participant could not longer reliably tell the tones apart. 
+The threshold is set to contain 75\% of each participant's correct guesses and an example of one participant's threshold can be seen in \todo{put in figure}.
+The median of these threshold values can then be used to estimate the frequency difference at which the participant population could no longer tell the difference between two tones and can be used to improve the next interface iteration's frequency profile and increase performance.
+\cref{fig:pitch-thresholds} shows a distribution of the thresholds values for each group, along with the median value. 
+The median is used here given the skewed plot and was found to be approximately 0.4 semitones for each group.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/pitch_discrimination.png}
+  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }
+  \label{fig:pitch-discrimination}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds.png}
+  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }
+  \label{fig:pitch-thresholds}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
+  \caption{}
+\end{figure}
+
 \subsection{Target Search}
+
+The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and tilt directions are plotted against each other.
+A set of box-plots of the pan errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
+The results are summarised in \cref{tab:target-results}\todo{tabulate results}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/target_errors.png}
+  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
+  \label{fig:target-errors}
+\end{figure}
+
+The Shapiro-Wilkes test for normality reveals that none of these distributions are normally spread and accordingly, the Pearson test is used to investigate the correlation between the actual target location and participants' pointing location.
+These results are included in \cref{tab:target-results}.
+The Pearson correlation scores for Group \text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.71, 0.76], p < 0.001; r_{elevation} \in [0.36, 0.48], p < 0.001$), showing that the both the pan and elevation cues roughly worked as expected.
+However, the correlation scores for Group \textit{G2} are significantly weaker, with a pan angle correlation of $r_{pan} \in [0.2, 0.48], p < 0.001$.
+The elevation correlation is somewhat stronger, with $r_{elevation} \in [0.46, 0.53], p < 0.001$.
+However, the correlation score for the elevation for the \textit{lo} setting is disregarded for having insufficient statistical relevance ($p > 0.05$).
+
+The repeated-measures procedure that was used for these experiments required the data for each participant to be grouped together for each setting.
+The medians of these groupings of error data are then used as individual samples that represent an individual participant's performance for each setting.
+\cref{fig:target-boxplot-error} shows this median data collected from each participant as a set of boxplots, while \cref{fig:target-boxplot-absolute-error} shows the absolute error data for these groupings.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
+  \caption{Boxplots of the median pan and elevation errors for each setting. }
+  \label{fig:target-boxplot-error}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
+  \caption{Boxplots of the absolute median pan and elevation errors for each setting. }
+  \label{fig:target-boxplot-absolute-error}
+\end{figure}
+
+The boxplots in \cref{fig:target-boxplot-error} shows that the error in the pan dimensions is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups and settings for the different settings.
+However, these divergences are determined to not be significant using the Friedman test for repeated measures ($p \gg 0.05$), showing that spatialisation perception and accuracy is not affected by changes in the tone's pitch.
+
+Analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
+A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely.
+This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$}, while Group \textot{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
+  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
+\end{figure}
 

### 2019-10-07 paper.tex
Adding proper IP plot

@@
 A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely.
-This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$}, while Group \textot{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+With these results, we can reasonably conclude that the \textit{hi} setting  
+The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to produce the lowest error.
+
+\subsection{Time to Target}
+
+To investigate if the interface has a Fitts-relationship, we plot the time to find the target as a function of the targets' indices of difficulty as defined in \cref{eq:fitts-base}.
+The data was binned in intervals of the effective target width as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
+A logarithmic line of best fit is fitted through the binned data's median values through means of regression and all the results are presented in \cref{fig:fitts-results}.
 
@@
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
+  \label{fig:fitts-results}
+\end{figure}
+
+For Group \textit{G1}, a Fitts relationship can be observed where the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
+This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
+This result allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figures/fitts_ips.png}
+  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
+  \label{fig:fitts-ips}
 \end{figure}

### 2019-10-07 paper.tex
Added Fitts IP figure, explanation

@@
 This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+It can also be noted that there is a significant negative error bias observed in all of the settings in both groups which is possible caused by a cognitive constraint introduced by the floor where the participants believed that the targets could not appear below the ground.
+Since this bias seems constant in nature, it can be addressed by adjusting the frequency parameters of the interface and shifting it by a constant offset.
+
 With these results, we can reasonably conclude that the \textit{hi} setting  
@@
 This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
-This result allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.
+Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency int eh time to target results for participants with severe sight impairments.
+However, the results for the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88, p_{med} = 0.019; r_{hi} = 0.89, p_{med} = 0.03$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.23, p_{lo} = 0.65$).
+
+These results allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.
 
@@
 
+For the results from Group\textit{G1}, there is a progressive improvement in performance between the \textit{lo}, \textit{med} and \textit{hi} settings respectively, with the \textit{hi} producing the highest level of performance between the 3 settings, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{hi} setting.
+This is supported by the results from the Friedman test ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show all 3 datasets are significantly different from one another ($p_{lo} = p_{med} = p_{hi} < 0.001$).
+The results for Group \textit{G2} shows far lower indices of performance for each setting, which is expected given the increased indices of difficulty observed in \cref{fig:fitts-results}.
+Indeed, the distributions are shown to be similar according to the Friedman test ($p = 0.1$) and we cannot conclude which setting produces the best performance. 
+\todo{explain why bad}
+
 \section{Conclusion}

### 2019-10-07 paper.tex
Added short discussion on results'

@@
   \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
-  \caption{}
+  \caption{Histrogram distibutions of the participants' 75\% cut-off thresholds. }
+  \label{fig:pitch-thresholds-hist}
 \end{figure}
@@
 
-These results allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-ip}, for each setting in \cref{fig:fitts-ips}.
+These results allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-performance}, for each setting in \cref{fig:fitts-ips}.
 
@@
 
+A possible reason why the \textit{hi} setting produces the highest level of performance is that the higher gradient makes it easier to perceive changes in the tone's pitch for each unit change in the device's pointing direction.
+The observed effect is that the \textit{hi} setting drives the user to the target location in in the least amount of time and with the highest level of accuracy.
+
+This trend of progressive improvement between the \textit{lo}, \textit{med} and \textit{hi} settings respectively seems indicate that that simply increasing the frequency gradient will lead to increased performance.
+However, \cref{fig:pitch-thresholds-hist} indicates that the frequency difference between the on-target tone and the selected tone in the \textit{hi} setting is approaching the cut-off frequency for Group \textit{G1}, indicating the point at which increasing the gradient produces diminishing returns on performance.
+Indeed, the participants from Group \textit{G2} seems to have passed this threshold and reached a saturation point where they could no longer reliably tell changes in the tone apart any longer.
+
 \section{Conclusion}

### 2019-10-11 paper.tex
Put in introduction

@@
 
-\section{Previous Work}
+In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society.
+The UK's Royal National Institute of Blind People (RNIB) for example has prioritised improving access to everyday services and products, such as public transport and mobile apps~\cite{rnib2016uk}.
+Improvements in modern computing have made it possible for new and innovative solutions to these problems to come to the fore.
+In particular, researchers in the active vision field have have made much progress in enabling machines to autonomously manipulate cameras to gather information about an environment for mapping and object finding tasks~\cite{bajcsy2018revisiting,lock2019active}.
+There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus on that point?
+If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point or object of interest and identify an unknown scene.
 
-\section{System Description}
+The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to deliver a mobile guidance system that will ultimately be able to guide a user with vision impairments on the last leg of their journey, i.e.\ the so-called `last 10-yard problem'.
+The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango} and \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
+It also provides access to Android's full range of interface tools and I/O options. 
+Furthermore, a set of bone-conduction headphones (pictured in \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
+
+\begin{figure}[t]
+  \centering
+  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
+~
+  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
+~
+  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
+  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).}
+\end{figure}
+
+Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can easily be interpreted without posing a significant cognitive load.
+A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
+In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
+However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
+A similar approach was used in~\cite{durette2008visuo} and further investigated in~\cite{lock2019bone}.
+However, in this work we expand the scope and investigate the perception limitations of the interface in order to find some design guidelines and we expand the pool of participants to more than 50 people.
+
+The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a discussion on the design and implementation of our interface in \cref{sec:system-description}.
+This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiments} and \cref{sec:results}.
+Finally, the paper concludes with a summary and a short discussion on future research prospects in \cref{sec:conclusion}.
+
+\section{Previous Work}\label{sec:prev-work}
+
+\section{System Description}\label{sec:system-description}
 
@@
 
-\section{Experiments}
+\section{Experiments}\label{sec:experiments}
 
@@
 
-\section{Results}
+\section{Results}\label{sec:results}
 
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 

### 2019-10-11 paper.tex
Added previous work section

@@
 
+\todo{Change?}
 In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society.
@@
 \section{Previous Work}\label{sec:prev-work}
+
+Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
+The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
+In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
+However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
+Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
+Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\cite{arditi2013user}.
+Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
+
+Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\cite{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
+Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\cite{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
+However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
+Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
+In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\cite{lock2019bone}.
+In the following sections, we investigate this performance even further.
+
+Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
+Fitts's Law was originally proposed for visual target search tasks, but has since been applied in non-visual target search tasks as well.
+For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
+However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
+Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
+Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
+Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
+These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
+However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.
 
@@
   \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
-  \caption{Histrogram distibutions of the participants' 75\% cut-off thresholds. }
+  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }
   \label{fig:pitch-thresholds-hist}

### 2019-10-11 paper.tex
Added result table

@@
 \usepackage{cleveref}
+\usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{todonotes}
@@
 
-\begin{equation*}
+\begin{equation}
 \label{eq:semitone-difference}
   \Delta f = 12\log_2\frac{f_0}{f_1}.
-\end{equation*}
+\end{equation}
 
@@
   \includegraphics[width=1.0\textwidth]{figures/pitch_discrimination.png}
-  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }
-  \label{fig:pitch-discrimination}
+  \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
 \end{figure}
@@
   \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds.png}
-  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }
-  \label{fig:pitch-thresholds}
+  \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
 \end{figure}
@@
   \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
-  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }
-  \label{fig:pitch-thresholds-hist}
+  \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
 \end{figure}
@@
   \includegraphics[width=1.0\textwidth]{figures/target_errors.png}
-  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
-  \label{fig:target-errors}
+  \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-errors}
 \end{figure}
+
+\begin{table}
+  \centering
+  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
+  \begin{tabular}{p{0.5cm}p{0.7cm}p{1cm}p{2cm}p{2.25cm}}
+    \toprule
+    &           & Setting      & Mean Angle Error [rad] & Spearman Correlation \\ \midrule
+    \multirow{6}{*}{\textit{G1}}
+    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.75, p < 0.001$ \\
+    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.77, p < 0.001$ \\
+    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.72, p < 0.001$ \\ \cline{3-5}
+    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.36, p < 0.001$ \\
+    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.49, p < 0.001$ \\
+    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.48, p < 0.001$ \\ \midrule
+    \multirow{6}{*}{\textit{G2}}
+    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.10, p = 0.03$  \\
+    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.13, p = 0.01$  \\
+    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.21, p < 0.001$ \\\cline{3-5}
+    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.03, p = 0.48$  \\
+    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.31, p < 0.001$ \\
+    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.40, p < 0.001$ \\ 
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2019-10-11 paper.tex
Minor change to text labels

@@
   \includegraphics[width=1.0\textwidth]{figures/sound_localisation.png}
-  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }
-  \label{fig:sound-localisation}
+  \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }\label{fig:sound-localisation}
 \end{figure}
@@
 We then used each CDF's parameters to determine a frequency threshold where the participant could not longer reliably tell the tones apart. 
-The threshold is set to contain 75\% of each participant's correct guesses and an example of one participant's threshold can be seen in \todo{put in figure}.
+The threshold is set to contain 75\% of each participant's correct guesses.% and an example of one participant's threshold can be seen in \todo{put in figure}.
 The median of these threshold values can then be used to estimate the frequency difference at which the participant population could no longer tell the difference between two tones and can be used to improve the next interface iteration's frequency profile and increase performance.
@@
 A set of box-plots of the pan errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
-The results are summarised in \cref{tab:target-results}\todo{tabulate results}.
+The results are summarised in \cref{tab:target-results}.
 
@@
   \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
-  \caption{Boxplots of the median pan and elevation errors for each setting. }
-  \label{fig:target-boxplot-error}
+  \caption{Boxplots of the median pan and elevation errors for each setting. }\label{fig:target-boxplot-error}
 \end{figure}
@@
   \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
-  \caption{Boxplots of the absolute median pan and elevation errors for each setting. }
-  \label{fig:target-boxplot-absolute-error}
+  \caption{Boxplots of the absolute median pan and elevation errors for each setting. }\label{fig:target-boxplot-absolute-error}
 \end{figure}
@@
   \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
-  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
-  \label{fig:fitts-results}
+  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-results}
 \end{figure}
@@
   \includegraphics[width=0.7\textwidth]{figures/fitts_ips.png}
-  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
-  \label{fig:fitts-ips}
+  \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
 \end{figure}

### 2019-10-11 paper.tex
Read through results section, small corrections

@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18-55 years old, 40 female, 16 female).
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18--55 years old, 40 female, 16 female).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
@@
 Both groups were given some time before the experiment target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
-Furthermore, to minimise the speed/accuracy biases in the results for this experiment, we asked the participants to focus on finding the targets, without worrying about the time it took.
+Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took.
 
@@
 
-\cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played to them from.
+\cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from.
 
@@
 Group \textit{G2} also displays a concentration of erroneous guesses in the centre interval.
-However, it also has more incorrect guesses in other distance intervals and displays a more even progression through the distance intervals towards the centre.
+However, it also has more incorrect guesses in other distance intervals and exhibits a more even progression through the distance intervals towards the centre.
 This could indicate that instead of terminating the experiment through bringing the 2 sequences within 1 interval of one another, there was more switching back and forth between the centre 3 intervals.
 
-These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy
-These results are in line with what we expected and are supported by literature which indicates that humans are very adept at localising a sound source, particularly in the pan dimension.
+These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy and are in line with what we expected based on literature that indicate that humans are very adept at localising a sound source, particularly in the pan dimension.
 
@@
 
-For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone difference interval and as expected, the highest proportion of incorrect guesses occur in the $[-0.25, 0.25]$ semitone difference interval.
-The guesses from Group \textit{G2} is more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone difference interval.
+For Group \textit{G1}, we see that their guesses seem normally spread around the 0 semitone difference interval and, as expected, the highest proportion of incorrect guesses occur in the $[-0.25, 0.25]$ semitone difference interval.
+The guesses from Group \textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone difference interval.
 
-Assuming the differences are normally spread, we fitted a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
-We then used each CDF's parameters to determine a frequency threshold where the participant could not longer reliably tell the tones apart. 
-The threshold is set to contain 75\% of each participant's correct guesses.% and an example of one participant's threshold can be seen in \todo{put in figure}.
-The median of these threshold values can then be used to estimate the frequency difference at which the participant population could no longer tell the difference between two tones and can be used to improve the next interface iteration's frequency profile and increase performance.
-\cref{fig:pitch-thresholds} shows a distribution of the thresholds values for each group, along with the median value. 
-The median is used here given the skewed plot and was found to be approximately 0.4 semitones for each group.
+Assuming these differences are normally spread, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
+We then used each CDF's parameters to determine a frequency cut-off threshold where the participant could not longer reliably tell tones apart and is set to contain 75\% of each participant's correct guesses.% and an example of one participant's threshold can be seen in \todo{put in figure}.
+The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones and can be used to improve the interface's frequency profile and performance.
+\cref{fig:pitch-thresholds} shows the threshold distribution for each group, along with the median value. 
+The median is used for each grouping given the skewed plot and was found to be approximately 0.4 semitones for each group.
 
@@
 
-The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and tilt directions are plotted against each other.
+The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other.
 A set of box-plots of the pan errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
@@
     \toprule
-    &           & Setting      & Mean Angle Error [rad] & Spearman Correlation \\ \midrule
+    &           & Setting      & Mean Angle Error [rad] & Pearson Correlation \\ \midrule
     \multirow{6}{*}{\textit{G1}}
@@
 These results are included in \cref{tab:target-results}.
-The Pearson correlation scores for Group \text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.71, 0.76], p < 0.001; r_{elevation} \in [0.36, 0.48], p < 0.001$), showing that the both the pan and elevation cues roughly worked as expected.
-However, the correlation scores for Group \textit{G2} are significantly weaker, with a pan angle correlation of $r_{pan} \in [0.2, 0.48], p < 0.001$.
-The elevation correlation is somewhat stronger, with $r_{elevation} \in [0.46, 0.53], p < 0.001$.
-However, the correlation score for the elevation for the \textit{lo} setting is disregarded for having insufficient statistical relevance ($p > 0.05$).
+The Pearson correlation scores for Group \text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77], p < 0.001; r_{elevation} \in [0.36, 0.49], p < 0.001$), showing that the both the pan and elevation cues roughly worked as expected.
+However, the correlation scores for Group \textit{G2} are significantly weaker, with a pan angle correlation of $r_{pan} \in [0.1, 0.21], p < 0.03$.
+With the exception of the \textit{lo} setting ($p_{lo} = 0.48$), the elevation correlation is somewhat stronger, with $r_{elevation} \in [0.31, 0.40], p < 0.001$.
 
-The repeated-measures procedure that was used for these experiments required the data for each participant to be grouped together for each setting.
-The medians of these groupings of error data are then used as individual samples that represent an individual participant's performance for each setting.
-\cref{fig:target-boxplot-error} shows this median data collected from each participant as a set of boxplots, while \cref{fig:target-boxplot-absolute-error} shows the absolute error data for these groupings.
+The repeated-measures procedure that was used for these experiments requires the data for each participant to be grouped together for each setting.
+The medians of these data groupings are then used as individual samples that represent an individual participant's performance for each setting.
+\cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots.
 
@@
   \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
-  \caption{Boxplots of the median pan and elevation errors for each setting. }\label{fig:target-boxplot-error}
+  \caption{Box-plots of the median pan and elevation errors for each setting. }\label{fig:target-boxplot-error}
 \end{figure}
 
-\begin{figure}
-  \centering
-  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
-  \caption{Boxplots of the absolute median pan and elevation errors for each setting. }\label{fig:target-boxplot-absolute-error}
-\end{figure}
+The box-plots in \cref{fig:target-boxplot-error} show that the error in the pan dimension is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
+However, using the Friedman test for repeated measures, these divergences are found to not be significant ($p \gg 0.05$), showing that spatial perception and accuracy is not affected by changes in the tone's pitch.
 
-The boxplots in \cref{fig:target-boxplot-error} shows that the error in the pan dimensions is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups and settings for the different settings.
-However, these divergences are determined to not be significant using the Friedman test for repeated measures ($p \gg 0.05$), showing that spatialisation perception and accuracy is not affected by changes in the tone's pitch.
+Further analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
+A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 significance threshold, was used to investigate the setting relationships more closely.
+This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+It is also noted that there is a significant negative error bias in all of the settings in both groups which is possibly caused by a cognitive constraint introduced by the floor where the participants believed that the targets could not appear below the ground.
+Since this bias seems constant in nature, it can be addressed in the future by adjusting the frequency parameters of the interface and shifting it by a constant offset.
 
-Analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
-A post-hoc analysis using the Wilcoxon signed rank test with a Holm-Bonferoni correction applied to the commonly used 0.05 statistical significance threshold was used to investigate the setting relationships more closely.
-This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
-It can also be noted that there is a significant negative error bias observed in all of the settings in both groups which is possible caused by a cognitive constraint introduced by the floor where the participants believed that the targets could not appear below the ground.
-Since this bias seems constant in nature, it can be addressed by adjusting the frequency parameters of the interface and shifting it by a constant offset.
-
-With these results, we can reasonably conclude that the \textit{hi} setting  
-The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to produce the lowest error.
+The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to use to minimise the error.
 
@@
 
-To investigate if the interface has a Fitts-relationship, we plot the time to find the target as a function of the targets' indices of difficulty as defined in \cref{eq:fitts-base}.
-The data was binned in intervals of the effective target width as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
-A logarithmic line of best fit is fitted through the binned data's median values through means of regression and all the results are presented in \cref{fig:fitts-results}.
+To investigate if the interface illicit a Fitts-like relationship, we plot the time to find the target as a function of the targets' indices of difficulty as defined in \cref{eq:fitts-base}.
+The data was binned in intervals of the effective target width ($w_e$) as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
+A logarithmic line of best fit is also fitted through the binned data's median values through means of regression and all the results are presented in \cref{fig:fitts-results}.
 
@@
 
-For Group \textit{G1}, a Fitts relationship can be observed where the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
+For Group \textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
 This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
-Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency int eh time to target results for participants with severe sight impairments.
+Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency in the time to target results for participants with severe sight impairments.
 However, the results for the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88, p_{med} = 0.019; r_{hi} = 0.89, p_{med} = 0.03$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.23, p_{lo} = 0.65$).
@@
 The results for Group \textit{G2} shows far lower indices of performance for each setting, which is expected given the increased indices of difficulty observed in \cref{fig:fitts-results}.
-Indeed, the distributions are shown to be similar according to the Friedman test ($p = 0.1$) and we cannot conclude which setting produces the best performance. 
+Indeed, the distributions are shown to be similar according to the Friedman test ($p = 0.1$) and we cannot draw definitive conclusions on which setting produces the best performance. 
 \todo{explain why bad}
@@
 The observed effect is that the \textit{hi} setting drives the user to the target location in in the least amount of time and with the highest level of accuracy. 
-
 This trend of progressive improvement between the \textit{lo}, \textit{med} and \textit{hi} settings respectively seems indicate that that simply increasing the frequency gradient will lead to increased performance.
@@
 \section{Conclusion}\label{sec:conclusion}
+\todo{conclude}
 

### 2019-10-14 paper.tex
Modified some plots to make them more accurate, changed somne discussions in the results, added a conclusion

@@
 A similar approach was used in~\cite{durette2008visuo} and further investigated in~\cite{lock2019bone}.
-However, in this work we expand the scope and investigate the perception limitations of the interface in order to find some design guidelines and we expand the pool of participants to more than 50 people.
+However, in this work we expand the scope and investigate the perception limitations of the interface in order to find some design guidelines and we expand the pool of participants to 50 people.
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18--55 years old, 40 female, 16 female).
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old, 40 female, 16 female).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
@@
 The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other.
-A set of box-plots of the pan errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
+A set of box-plots of the angle errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
 The results are summarised in \cref{tab:target-results}.
@@
   \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
-  \begin{tabular}{p{0.5cm}p{0.7cm}p{1cm}p{2cm}p{2.25cm}}
+  \begin{tabular}{p{0.5cm}p{0.7cm}p{0.7cm}p{1cm}p{2cm}p{2.25cm}}
     \toprule
-    &           & Setting      & Mean Angle Error [rad] & Pearson Correlation \\ \midrule
+    &           & Setting      & Mean Angle Error [rad] & Mean Absolute Angle Error [rad] &  Pearson Correlation \\ \midrule
     \multirow{6}{*}{\textit{G1}}
-    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.75, p < 0.001$ \\
-    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.77, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.72, p < 0.001$ \\ \cline{3-5}
-    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.36, p < 0.001$ \\
-    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.49, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.48, p < 0.001$ \\ \midrule
+    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.25\pm0.27$ & $0.75, p < 0.001$ \\
+    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.26\pm0.27$ & $0.77, p < 0.001$ \\
+    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72, p < 0.001$ \\ \cline{3-5}
+    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.42\pm0.31$ & $0.36, p < 0.001$ \\
+    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.44\pm0.24$ & $0.49, p < 0.001$ \\
+    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.36\pm0.29$ & $0.48, p < 0.001$ \\ \midrule
     \multirow{6}{*}{\textit{G2}}
-    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.10, p = 0.03$  \\
-    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.13, p = 0.01$  \\
-    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.21, p < 0.001$ \\\cline{3-5}
-    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.03, p = 0.48$  \\
-    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.31, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.40, p < 0.001$ \\ 
+    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.48\pm0.31$ & $0.10, p = 0.03$  \\
+    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.45\pm0.27$ & $0.13, p = 0.01$  \\
+    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21, p < 0.001$ \\\cline{3-5}
+    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.49\pm0.39$ & $0.03, p = 0.48$  \\
+    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.42\pm0.33$ & $0.31, p < 0.001$ \\
+    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.36\pm0.32$ & $0.40, p < 0.001$ \\ 
     \bottomrule
@@
 The medians of these data groupings are then used as individual samples that represent an individual participant's performance for each setting.
-\cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots.
+\cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots, while \cref{fig:target-boxplot-absolute-errors} shows the collection of absolute errors.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
+  \caption{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-boxplot-absolute-errors}
+\end{figure}
+
 The box-plots in \cref{fig:target-boxplot-error} show that the error in the pan dimension is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
 However, using the Friedman test for repeated measures, these divergences are found to not be significant ($p \gg 0.05$), showing that spatial perception and accuracy is not affected by changes in the tone's pitch.
+This is further demonstrated in the box-plots in \cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all 3 settings.
 
+Regarding the errors in the elevation dimension in \cref{fig:target-boxplot-error}, we observe in Group \textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings respectively and a median gradually approaching \SI{0}{\radian}.
+A similar pattern is observed for Group \textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group \textit{G1}.
+\cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the 3 settings in both groups.
 Further analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
+\todo{discuss post-hoc in more detail}
 A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 significance threshold, was used to investigate the setting relationships more closely.
@@
 
-The distributions in \cref{fig:target-boxplot-error} show that the \textit{hi} setting produces the smallest median angular error in the elevation dimension out of the 3 settings and the post-hoc tests performed allow us to make the conclusion that the \textit{hi} setting is indeed the best setting to use to minimise the error.
+Comparing the distributions for each setting between the 2 groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all 3 settings are not significantly different from one another for both groups in both the pan and elevation dimensions (the $p$-values are summarised in \cref{tab:inter-group-results}).
+This results confirms that the errors produced between the blindfolded and participants with severe sight impairments are statistically similar in nature and both groups can reasonably be expected to produce similar error levels should the experiments be repeated with a different population.
+Consequently, with the significantly smallest median elevation error, we can conclude that the \textit{hi} setting is the best setting to use to minimise the elevation angle error and that the pan error is completely independent of the setting in use.
+
+\begin{table}
+  \centering
+  \caption{A summary of the $p$-values comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions. }\label{tab:inter-group-results}
+  \begin{tabular}{lll}
+    \toprule
+                   & Pan      & Elevation \\ \midrule
+      \textit{lo}  & $p=0.77$ & $p=0.95$ \\
+      \textit{med} & $p=0.98$ & $p=0.07$ \\
+      \textit{hi}  & $p=0.72$ & $p=0.41$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
-To investigate if the interface illicit a Fitts-like relationship, we plot the time to find the target as a function of the targets' indices of difficulty as defined in \cref{eq:fitts-base}.
-The data was binned in intervals of the effective target width ($w_e$) as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
+To investigate if the interface generates a Fitts-like responce from the participants, we plot the time to find the target as a function of the targets' indices of difficulty as defined by \cref{eq:fitts-base}.
+The data is binned in intervals of the effective target width ($w_e$) as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
 A logarithmic line of best fit is also fitted through the binned data's median values through means of regression and all the results are presented in \cref{fig:fitts-results}.
@@
 For Group \textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
-This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.9, p_{lo} = 0.03; r_{med} = 0.92, p_{med}=0.009; r_{hi} = 0.86, p_{hi} = 0.02$).
+This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.0.76, p_{lo} = 0.045; r_{med} = 0.96, p_{med}<0.001; r_{hi} = 0.86, p_{hi} = 0.013$).
 Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency in the time to target results for participants with severe sight impairments.
-However, the results for the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88, p_{med} = 0.019; r_{hi} = 0.89, p_{med} = 0.03$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.23, p_{lo} = 0.65$).
+This could be a result of taking each participant's result as a single datum and the smaller population in Group \textit{G2}.
+Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88, p_{med} = 0.008; r_{hi} = 0.84, p_{med} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08, p_{lo} = 0.85$).
 
-These results allows us to calculate and plot the index of performance, as given in \cref{eq:fitts-performance}, for each setting in \cref{fig:fitts-ips}.
+These results allows us to calculate and plot an index of performance, as given in \cref{eq:fitts-performance}, for each setting in \cref{fig:fitts-ips}.
 
@@
 
-For the results from Group\textit{G1}, there is a progressive improvement in performance between the \textit{lo}, \textit{med} and \textit{hi} settings respectively, with the \textit{hi} producing the highest level of performance between the 3 settings, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{hi} setting.
-This is supported by the results from the Friedman test ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show all 3 datasets are significantly different from one another ($p_{lo} = p_{med} = p_{hi} < 0.001$).
-The results for Group \textit{G2} shows far lower indices of performance for each setting, which is expected given the increased indices of difficulty observed in \cref{fig:fitts-results}.
-Indeed, the distributions are shown to be similar according to the Friedman test ($p = 0.1$) and we cannot draw definitive conclusions on which setting produces the best performance. 
-\todo{explain why bad}
+For the results from Group\textit{G1}, there is a progressive improvement in performance between the 3 settings, with the \textit{lo} producing the highest indices of performance overall, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{lo} setting.
+This is supported by the results from the Friedman test that shows that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001, p_{lo-hi} < 0.001$), while the \textit{med} and \textit{hi} are not different to one another ($p_{med-hi} = 0.14$).
+The results for Group \textit{G2} shows generally lower indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
+Again, the \textit{lo} setting produces the highest performance by a large margin compared to the \textit{med} setting with the Wilcoxon test with Holm-Bonferronni corrections ($p_{lo-med}=0.01$). 
+However, the same test indicates that there is not a statistical difference between the \textit{lo} and \textit{hi} or the \textit{med} and \textit{hi} settings ($p_{lo-hi} = 0.1, p_{med-hi} = 0.038$).
+These results seem to indicate that for both groups, the \textit{lo} produces the highest level of performance followed, by the \textit{hi} setting.
 
-A possible reason why the \textit{hi} setting produces the highest level of performance is that the higher gradient makes it easier to perceive changes in the tone's pitch for each unit change in the device's pointing direction.
-The observed effect is that the \textit{hi} setting drives the user to the target location in in the least amount of time and with the highest level of accuracy. 
-This trend of progressive improvement between the \textit{lo}, \textit{med} and \textit{hi} settings respectively seems indicate that that simply increasing the frequency gradient will lead to increased performance.
+\todo{compare inter-group results}
+
+\subsection{Discussion}
+
+There seems to be an interesting contrast brought forward by the results for the accuracy and time performance.
+That is, the \textit{hi} produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings respectively. 
+However, this trend is almost reversed in the time to target performance given by Fitts's model where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
+Since Fitts's model takes the angular error into account, once might reasonably have expected that the results for both datasets would have been more similar. 
+However, Fitts's relationship does not model for different stimuli and we therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting that allows for finer adjustments to be made to the device's orientation and get it closer to pointing to the target, but at the cost of a higher average time to find the target.
+This seems to indicate a speed-accuracy trade-off in finding the targets and with the Fitts relationship obtained here, we can modify the interface to prioritise different metrics and produce the correct output.
+
+With respect to the target acquisition results, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings respectively, (see \cref{tab:target-results}) seems indicate that that simply increasing the frequency gradient will lead to increased performance.
 However, \cref{fig:pitch-thresholds-hist} indicates that the frequency difference between the on-target tone and the selected tone in the \textit{hi} setting is approaching the cut-off frequency for Group \textit{G1}, indicating the point at which increasing the gradient produces diminishing returns on performance.
@@
 \section{Conclusion}\label{sec:conclusion}
-\todo{conclude}
+
+In this work, we expanded upon the initial investigation from~\cite{lock2019bone} and performed a wider number of tests with more participants where we investigated using spatialised sound with a varying tone to direct a user's gaze in more detail.
+We found that the blindfolded participants and participants with severe sight impairments had similar levels of performance in localising sound and differentiating between tones. 
+We also found that both groups managed to find a set of targets with similar levels of accuracy.
+However, the blindfolded group managed to outperform the group with severe sight impairments in terms of time to find the target. 
+We also tested different pitch gain gradient settings for the pitch and found that the performance in the pan dimension that uses spatialised signals, is independent of the pitch gradient setting.
+Furthermore, we found a speed-accuracy trade off between the settings, where a steeper pitch gain gradient produces a smaller angular error at the cost of decreased time performance. 
+This, along with the Fitts-like relationship that was found, can be used to improve and refine the interface in order to prioritise speed or accuracy and produce the desired output.
+
+The next steps for the project is to implement this interface into a guidance system and test the complete system's performance. 
+Implementing an auto-adaptive interface scheme can also now be considered.
+
+\section{Acknowledgements}
+
+This project is partly funded and supported by the Google Winter Award (2016).
 

### 2019-10-17 paper.tex
Rewrote introduction

@@
 
-\todo{Change?}
-In recent years, governments have spearheaded numerous initiatives to support people with disabilities and enable them to play a more active role in modern society.
-The UK's Royal National Institute of Blind People (RNIB) for example has prioritised improving access to everyday services and products, such as public transport and mobile apps~\cite{rnib2016uk}.
-Improvements in modern computing have made it possible for new and innovative solutions to these problems to come to the fore.
-In particular, researchers in the active vision field have have made much progress in enabling machines to autonomously manipulate cameras to gather information about an environment for mapping and object finding tasks~\cite{bajcsy2018revisiting,lock2019active}.
-There is, however, a significant research question about whether techniques from active machine vision can be applied to humans, i.e.\ can a machine identify a point of interest in a scene and direct a human, instead of an electronic servo, to focus on that point?
-If this can be done, it would be beneficial to people with visual impairments and will augment their ability to search for an arbitrary point or object of interest and identify an unknown scene.
+The ActiVis\footnote{https://lcas.github.io/ActiVis/} project is working towards building an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
+Improvements to computer vision and machine learning techniques, as well as mobile commuting hardware improvements are exploited to make this system possible.
+In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
+However, in literature, these techniques are typically limited to electro-mechanical servos~\cite{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
+In previous work we implemented a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to humans as well~\cite{lock2019active}.
 
-The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to deliver a mobile guidance system that will ultimately be able to guide a user with vision impairments on the last leg of their journey, i.e.\ the so-called `last 10-yard problem'.
 The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango} and \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-A similar approach was used in~\cite{durette2008visuo} and further investigated in~\cite{lock2019bone}.
-However, in this work we expand the scope and investigate the perception limitations of the interface in order to find some design guidelines and we expand the pool of participants to 50 people.
+In~\cite{lock2019bone}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
+We expand upon the initial investigation in~\cite{lock2019bone} with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
+The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
 

### 2019-10-17 paper.tex
Fixed plots, added new short descriptions on results sections

@@
 This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
-Alternative solutions, such as open-back headphones, were also considered.
-These allow ambient noise through, but they still filter the incoming sound.
+Alternative solutions, such as open-back headphones which allow ambient noise through, were also considered, but they still filter the incoming sound and were disregarded.
 The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.
@@
 Assuming these differences are normally spread, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
-We then used each CDF's parameters to determine a frequency cut-off threshold where the participant could not longer reliably tell tones apart and is set to contain 75\% of each participant's correct guesses.% and an example of one participant's threshold can be seen in \todo{put in figure}.
+We then used each CDF's parameters to determine a frequency cut-off threshold where the participant could not longer reliably tell tones apart and is set to contain 75\% of each participant's correct guesses.
 The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones and can be used to improve the interface's frequency profile and performance.
@@
   \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
-  \begin{tabular}{p{0.5cm}p{0.7cm}p{0.7cm}p{1cm}p{2cm}p{2.25cm}}
+  \begin{tabular}{p{0.5cm}p{1.3cm}p{0.9cm}p{2cm}p{2cm}p{2.25cm}}
     \toprule
@@
     & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.26\pm0.27$ & $0.77, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72, p < 0.001$ \\ \cline{3-5}
+    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72, p < 0.001$ \\ \cline{2-6}
     &           & \textit{lo}  & $-0.12\pm0.51$ & $0.42\pm0.31$ & $0.36, p < 0.001$ \\
@@
     & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.45\pm0.27$ & $0.13, p = 0.01$  \\
-    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21, p < 0.001$ \\\cline{3-5}
+    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21, p < 0.001$ \\\cline{2-6}
     &           & \textit{lo}  & $-0.30\pm0.59$ & $0.49\pm0.39$ & $0.03, p = 0.48$  \\
@@
 The box-plots in \cref{fig:target-boxplot-error} show that the error in the pan dimension is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
-However, using the Friedman test for repeated measures, these divergences are found to not be significant ($p \gg 0.05$), showing that spatial perception and accuracy is not affected by changes in the tone's pitch.
+However, using the Friedman test for repeated measures on the medians of absolute errors, these divergences are found to not be significant ($p_{G1} = 0.17, p_{G2} = 0.09$), showing that spatial perception and accuracy is not affected by changes in the tone's pitch.
 This is further demonstrated in the box-plots in \cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all 3 settings.
@@
 Regarding the errors in the elevation dimension in \cref{fig:target-boxplot-error}, we observe in Group \textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings respectively and a median gradually approaching \SI{0}{\radian}.
-A similar pattern is observed for Group \textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group \textit{G1}.
-\cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the 3 settings in both groups.
-Further analysis of the elevation data with the Friedman test reveals that the results for the different settings within each group are indeed significantly different from one another with a reasonable degree of confidence ($p_{G1} = 0.03, p_{G2} = 0.01$).
-\todo{discuss post-hoc in more detail}
-A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 significance threshold, was used to investigate the setting relationships more closely.
-This analysis reveals that there is only 1 significant difference between the performances generated by the \textit{med} and \textit{hi} settings for Group \textit{G1} ($p_{med-hi} = 0.002$), while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+A similar trent is observed for Group \textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group \textit{G1}.
+\cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the 3 settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
+Further analysis of the medians of the absolute elevation error data with the Friedman test reveals that the results for the different settings only Group \textit{G1} are significantly different from one another ($p_{G1} = 0.002, p_{G2} = 0.32$).
+A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
+This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group \textit{G1} ($p_{lo-med} = 0.003, p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which of the \textit{med} and \textit{hi} settings are better for Group \textit{G1}.
+Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group \textit{G2}, but this may be caused by the relatively small sample size for each setting.
+%while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
 It is also noted that there is a significant negative error bias in all of the settings in both groups which is possibly caused by a cognitive constraint introduced by the floor where the participants believed that the targets could not appear below the ground.
@@
                    & Pan      & Elevation \\ \midrule
-      \textit{lo}  & $p=0.77$ & $p=0.95$ \\
-      \textit{med} & $p=0.98$ & $p=0.07$ \\
-      \textit{hi}  & $p=0.72$ & $p=0.41$ \\
+      \textit{lo}  & $p=0.18$ & $p=0.90$  \\
+      \textit{med} & $p=0.86$ & $p=0.34$  \\
+      \textit{hi}  & $p=0.28$ & $p=0.38$  \\
     \bottomrule
@@
 
-To investigate if the interface generates a Fitts-like responce from the participants, we plot the time to find the target as a function of the targets' indices of difficulty as defined by \cref{eq:fitts-base}.
+To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty as defined by \cref{eq:fitts-base}.
 The data is binned in intervals of the effective target width ($w_e$) as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
@@
 For Group \textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
-This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.0.76, p_{lo} = 0.045; r_{med} = 0.96, p_{med}<0.001; r_{hi} = 0.86, p_{hi} = 0.013$).
+This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.76, p_{lo} = 0.045; r_{med} = 0.96, p_{med}<0.001; r_{hi} = 0.86, p_{hi} = 0.013$).
 Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency in the time to target results for participants with severe sight impairments.
@@
 These results allows us to calculate and plot an index of performance, as given in \cref{eq:fitts-performance}, for each setting in \cref{fig:fitts-ips}.
+Their results are summarised in \cref{tab:fitts-results}.
 
@@
 
-For the results from Group\textit{G1}, there is a progressive improvement in performance between the 3 settings, with the \textit{lo} producing the highest indices of performance overall, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{lo} setting.
-This is supported by the results from the Friedman test that shows that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001, p_{lo-hi} < 0.001$), while the \textit{med} and \textit{hi} are not different to one another ($p_{med-hi} = 0.14$).
-The results for Group \textit{G2} shows generally lower indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
-Again, the \textit{lo} setting produces the highest performance by a large margin compared to the \textit{med} setting with the Wilcoxon test with Holm-Bonferronni corrections ($p_{lo-med}=0.01$). 
-However, the same test indicates that there is not a statistical difference between the \textit{lo} and \textit{hi} or the \textit{med} and \textit{hi} settings ($p_{lo-hi} = 0.1, p_{med-hi} = 0.038$).
+\begin{table}
+  \centering
+  \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:fitts-results}
+  \begin{tabular}{p{0.5cm}p{1.2cm}p{2.3cm}}
+    \toprule
+    & Setting      & Mean Index of Performance \\ \midrule
+    & \textit{lo}  & $0.056\pm0.005$ \\
+    \textit{G1} & \textit{med} & $0.053\pm0.008$ \\
+		& \textit{hi}  & $0.051\pm0.007$ \\ \cline{2-3}
+    & \textit{lo}  & $0.034\pm0.009$ \\
+    \textit{G2} & \textit{med} & $0.014\pm0.002$ \\
+    & \textit{hi}  & $0.022\pm0.006$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+For the results from Group \textit{G1}, there is a fairly consistent level of performance between the 3 settings, with the \textit{lo} producing the highest indices of performance overall, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{lo} setting.
+This is supported by the results from the Friedman test that shows that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001, p_{lo-hi} < 0.001$), while the \textit{med} and \textit{hi} are not different to one another ($p_{med-hi} = 0.85$).
+The results for Group \textit{G2} shows generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
+Again, following results from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin compared to the \textit{med} setting with the Wilcoxon test with Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results respectively.
 These results seem to indicate that for both groups, the \textit{lo} produces the highest level of performance followed, by the \textit{hi} setting.
 
-\todo{compare inter-group results}
+From \cref{fig:fitts-ips}, there is significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
+This is further supported by the Kruskal-Wallis test that reveals that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001, p_{med} < 0.001, p_{hi} < 0.001$).
+The significant difference between the blindfolded group and the group with severely sight impaired participants seems to indicate that the latter group take significantly longer to find the target. 
+However, it is unclear whether this is a systematic cause or a difference in search strategy between the 2 groups, e.g.\ \textit{G2} preferring, on average, a slower more methodical approach.
 

### 2019-10-21 paper.tex
Preparing for submission to TandF journal

@@
-\documentclass{article}
+\documentclass[]{interact}
 
@@
 \usepackage{multirow}
-\usepackage{todonotes}
+\usepackage[natbibapa,nodoi]{apacite}
+
+\setlength\bibhang{12pt}
+\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}
 
 \begin{document}
+
+\articletype{Review Draft}
+
+\title{NEW TITLE}
+
+\author{%
+  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchirst\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
+  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
+}
+
+\maketitle
+
+\begin{abstract}
+  Cool and informative abstract
+\end{abstract}
+
+\begin{keywords}
+  Visual impairment; active vision; guidance system; audio interface; Fitts Law
+\end{keywords}
 
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{apacite}
 \bibliography{bib}

### 2019-10-21 paper.tex
Added keywords and abstract

@@
 \begin{abstract}
-  Cool and informative abstract
+  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
+  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
+  In prior work, we implemented and tested a audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
+  This approach was shown to work well and in this work we expand the number of tests and metrics to provide a more more in-depth evaluation of the proposed audio interface.
+  Specifically, we used a larger number of participants and found design limitations and a Fitts's Law-compliant trend that we can use to improve and refine the audio signals. 
 \end{abstract}
@@
 In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
-However, in literature, these techniques are typically limited to electro-mechanical servos~\cite{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
-In previous work we implemented a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to humans as well~\cite{lock2019active}.
+However, in literature, these techniques are typically limited to electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
+In previous work we implemented a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to humans as well~\citep{lock2019active}.
 
@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In~\cite{lock2019bone}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
-We expand upon the initial investigation in~\cite{lock2019bone} with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\citep{lock2019bone,macdonald2006spatial} and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
@@
 Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
-The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
-In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
+The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
+In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
 However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
 Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
-Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\cite{arditi2013user}.
+Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
 Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
 
-Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\cite{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\cite{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
+Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
 The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
 However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
-This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
-In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
-We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\cite{lock2019bone}.
+Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
+In~\citep{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
 In the following sections, we investigate this performance even further.
 
-Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
+Researchers have previously used Fitts's Law~\citep{fitts1954information}, and more recently MacKenzie's modified version of it~\citep{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
 Fitts's Law was originally proposed for visual target search tasks, but has since been applied in non-visual target search tasks as well.
-For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
+For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\citep{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
 However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
-Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
+Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\citep{marentakis2006effects}.
 Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
 Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
-These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
+These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\citep{wu2010fitts}.
 However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.
@@
 Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
-Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\cite{golledge2004stated,yusif2016older,arditi2013user}.
-To address these issues, we implemented a handheld mobile system that is based on a concept proposed in~\cite{lock2017portable,lock2019active} and tested in~\cite{lock2019bone} that uses a Google Tango device that is able to localise itself in real-time.
+Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
+To address these issues, we implemented a handheld mobile system that is based on a concept proposed in~\citep{lock2017portable,lock2019active} and tested in~\citep{lock2019bone} that uses a Google Tango device that is able to localise itself in real-time.
 This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
@@
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
+This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\citep{lichtenstein2012headphone}.
 Alternative solutions, such as open-back headphones which allow ambient noise through, were also considered, but they still filter the incoming sound and were disregarded.
@@
 
-Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
+Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
@@
 Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
-However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\cite{gardner1995hrtf}.
+However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.
 
 The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
-Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\cite{klatzky2006cognitive}.
+Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
 However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
-The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
 
@@
 
-The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\cite{blauert1969sound}.
+The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
 The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
@@
 Therefore, a pure sine wave is suitable to convey the target's pan angle.
-To transform and spatialise the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\cite{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
+To transform and spatialise the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
 
@@
 
-A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\cite{macdonald2006spatial,schonstein2008comparison}.
+A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison}.
 To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
@@
 When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
-This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\cite{pratt1930spatial,blauert1997spatial}.
-An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\cite{shepard1964circularity}.
+This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\citep{pratt1930spatial,blauert1997spatial}.
+An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\citep{shepard1964circularity}.
 The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.
@@
 
-For this progressive increase in difficulty, a 2-up, 1-down step process is used~\cite{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves.
+For this progressive increase in difficulty, a 2-up, 1-down step process is used~\citep{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves.
 Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
@@
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
-Instead, we use Fitts's Law~\cite{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\cite{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
+Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
 It also provides a so-called `index of performance' that we can use as a metric to compare the results between the three configurations.
@@
 \noindent
-Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\cite{welford1968fundamentals}, given by
+Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\citep{welford1968fundamentals}, given by
 
@@
 
-In this work, we expanded upon the initial investigation from~\cite{lock2019bone} and performed a wider number of tests with more participants where we investigated using spatialised sound with a varying tone to direct a user's gaze in more detail.
+In this work, we expanded upon the initial investigation from~\citep{lock2019bone} and performed a wider number of tests with more participants where we investigated using spatialised sound with a varying tone to direct a user's gaze in more detail.
 We found that the blindfolded participants and participants with severe sight impairments had similar levels of performance in localising sound and differentiating between tones. 

### 2019-10-22 paper.tex
initial comments to sec 1 and 2

--- 2019-10-17 paper.tex
@@
 \usepackage{todonotes}
+
+\usepackage{soul}
+\DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}
 
@@
 
-Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can easily be interpreted without posing a significant cognitive load.
+Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
 A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In~\cite{lock2019bone}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
+In~\cite{lock2019bone}\tofix{fix this citation in bibtex}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
 We expand upon the initial investigation in~\cite{lock2019bone} with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
+
+\tofix{spell out here the research contributions of this paper with a bullet-points list}
 
@@
 In the following sections, we investigate this performance even further.
+\tofix{downplay the workshop paper (i.e. ``preliminary study'') and emphasize the importance of this new ``throughout investigation''}
 

### 2019-10-22 paper.tex
Addressed Nicola's concerns

@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In~\cite{lock2019bone}\tofix{fix this citation in bibtex}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
+In~\cite{lock2019bone}, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\cite{macdonald2006spatial}.
 We expand upon the initial investigation in~\cite{lock2019bone} with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
@@
 
-\tofix{spell out here the research contributions of this paper with a bullet-points list}
+The main contributions of this paper are two-fold:
+
+\begin{itemize}
+  \item we provide more comprehensive experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
+  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
+\end{itemize}
 
@@
 We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\cite{lock2019bone}.
-In the following sections, we investigate this performance even further.
-\tofix{downplay the workshop paper (i.e. ``preliminary study'') and emphasize the importance of this new ``throughout investigation''}
+We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
 

### 2019-10-31 paper.tex
minor fixes to sec 3

@@
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\cite{golledge2004stated,yusif2016older,arditi2013user}.
-To address these issues, we implemented a handheld mobile system that is based on a concept proposed in~\cite{lock2017portable,lock2019active} and tested in~\cite{lock2019bone} that uses a Google Tango device that is able to localise itself in real-time.
+To address these issues, we implemented a handheld mobile system that is based on a concept proposed in~\cite{lock2017portable,lock2019active} and tested in~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
 This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
@@
 This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
-Alternative solutions, such as open-back headphones which allow ambient noise through, were also considered, but they still filter the incoming sound and were disregarded.
+Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
 The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.
@@
 
-Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
+Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
@@
 
-When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, tricking the brain into believing a sound is located at some arbitrary position.
+When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, making the brain believe a sound is located at some arbitrary position.
 An HRTF is a mathematical function that simulates the response signal of a human head and is derived by capturing key characteristics that affect the monaural and binaural responses, such as the user's hearing levels and head size.
@@
 However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
-The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
 

### 2019-11-01 paper.tex

@@
 \usepackage{multirow}
-\usepackage{todonotes}
+\usepackage[natbibapa,nodoi]{apacite}
+
+\setlength\bibhang{12pt}
+\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}
 
@@
 
+\articletype{Review Draft}
+
+\title{NEW TITLE}
+
+\author{%
+  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchirst\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
+  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
+}
+
+\maketitle
+
+\begin{abstract}
+  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
+  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
+  In prior work, we implemented and tested a audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
+  This approach was shown to work well and in this work we expand the number of tests and metrics to provide a more more in-depth evaluation of the proposed audio interface.
+  Specifically, we used a larger number of participants and found design limitations and a Fitts's Law-compliant trend that we can use to improve and refine the audio signals. 
+\end{abstract}
+
+\begin{keywords}
+  Visual impairment; active vision; guidance system; audio interface; Fitts Law
+\end{keywords}
+
 \section{Introduction}
@@
 Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
-The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
-In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
+The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
+In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
 However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
 Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
-Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\cite{arditi2013user}.
+Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
 Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
 
-Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\cite{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\cite{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
+Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
 The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
@@
 
-Researchers have previously used Fitts's Law~\cite{fitts1954information}, and more recently MacKenzie's modified version of it~\cite{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
+Researchers have previously used Fitts's Law~\citep{fitts1954information}, and more recently MacKenzie's modified version of it~\citep{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
 Fitts's Law was originally proposed for visual target search tasks, but has since been applied in non-visual target search tasks as well.
-For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\cite{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
+For example, experiments with a haptic feedback pointing device have been performed to evaluate how effective it was at directing a user towards a target~\citep{ahmaniemi2009augmented} and the authors showed that the search time adheres to Fitts's Law.
 However, they also note that it is not a perfect fit, citing the fact that Fitts's Law does not take into account a user's search strategy.
-Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\cite{marentakis2006effects}.
+Another group of researchers conducted experiments using a spatial audio interface to describe the position of a target on the horizontal plane~\citep{marentakis2006effects}.
 Here, participants pointed to where they thought the targets were, on their left or right, as they traversed a path.
 Their results show a good relation between target difficulty and search time, providing a strong argument that Fitts's Law can be used to describe the performance of a spatial audio interface.
-These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\cite{wu2010fitts}.
+These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\citep{wu2010fitts}.
 However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.
@@
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
+=======
 This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
@@
 Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
-However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\cite{gardner1995hrtf}.
+However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.
 
 The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
-Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\cite{klatzky2006cognitive}.
+Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
 However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 

### 2019-11-01 paper.tex
Minor fix in text to describe the 3 settings

@@
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-=======
 This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
@@
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
+After practical tests with the interface, we set the neutral, on-target pitch the HMI emits to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
 The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
-After practical tests with the interface, we set the neutral pitch to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
-We set the pitch limits to 2 octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
-The linear function is visualised in \cref{fig:pitch-gain}.
 
@@
 A total of 28 targets were generated per participant.
+
+As part of this experiment, we wanted to see how changing the gradient of the pitch function affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
+Pitch limits of 1, 2 and 3 octaves above and below the neutral tone was then set of the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively.
+These linear gain functions are visualised in \cref{fig:pitch-gain}.
 

### 2019-11-01 paper.tex
revised sec 4

@@
 
+% \usepackage{soul}
+% \DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}
+\usepackage{color}
+\newcommand{\tofix}[1]{\textcolor{red}{\bf{[#1]}}}
+
 \setlength\bibhang{12pt}
 \renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}
-
-\usepackage{soul}
-\DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}
 
@@
   \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
-~
-  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.6\columnwidth]{figures/pitch_gain_function.png}}
+\hfil
+  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
   \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
@@
 The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
+After practical tests with the interface, we set the neutral pitch to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
+We set the pitch limits to two octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
+The linear function is visualised in \cref{fig:pitch-gain}.
 
@@
 
-\subsection{Implementation}
+\tofix{Add a short intro for this section, similar to what you had in the original paper.}
 
-A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of the information flow.
+\subsection{System Setup}
+
+A diagram of the experimental system pipeline is shown in~\cref{fig:pipeline}, where the arrows indicate the direction of the information flow.
 When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
 The audio generator then produces a tone based on the difference between the device and the target's positions. The tone is sent to the audio output channel, which plays it back to the user.
-A WiFi recording module is constantly monitoring the different values of the device's parameters and of the target's position, as well as the system's output, recording everything to a remotely stored datafile.
+A WiFi recording module is constantly monitoring the different values of the device's parameters and of the target's position, as well as the system's output, recording everything in a remotely stored datafile.
 
@@
   \centering
-  \includegraphics[clip=true, trim=0 120 80 50, width=0.9\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
+  \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
+  \caption{A diagram of the individual system components and their communication pipelines.
+$F$ indicates a feedback signal and $P$ a pose signal.
+\tofix{Remove ``Vibration, Voice Output'' from top box.} }\label{fig:pipeline}
 \end{figure}
 
-\subsection{Participant Characterisation}
+\subsection{Participant Characterisation} \label{sec:participant_characterisation}
 
-In addition to the target searching experiment, another set of experiments were conducted to characterise the participants' hearing characteristics.
-The characteristics that were measured were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies.
-These results will be used to provide context to the results captured during the target search experiment and provide additional insight on any possible biases or limitations.
+In addition to the target searching experiment, another set of experiments \tofix{You haven't talked about target search yet, maybe start with ``A preliminary set of experiments''} were conducted to characterise the participants' hearing characteristics.
+The measured characteristics were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
+These results will be used to provide context to the following target search experiment and provide additional insight on any possible biases or limitations.
 
@@
 The participant then had to select the direction the sound came from.
-The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it progressively harder to localise.
+The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly harder to localise.
 
-For this progressive increase in difficulty, a 2-up, 1-down step process is used~\citep{wetherill1965sequential,levitt1971transformed}, meaning that for every 2 correct answers, the distance to the centre halves.
+For this progressive increase in difficulty, a ``2-up, 1-down'' step process is used~\citep{wetherill1965sequential,levitt1971transformed}, meaning that for every two correct answers, the distance to the centre halves.
 Conversely, the task becomes easier for each incorrect answer by doubling the sound source's distance from the centre.
-We also use 2 different step sequences, one starting at a large distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' progression respectively.
-The terminating condition for the experiment is when the 2 sequences converge to within 2 intervals of one another for 3 consecutive guesses.
-This gives a distance band within which the participant is capable of localising the sound source.
+We also use two different step sequences, one starting at a large angular distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' progression respectively.
+The terminating condition for the experiment is when the two sequences converge to within two intervals of one another \tofix{Not clear, can you rephrase it?} for three consecutive guesses.
+This gives a distance band where the participant is capable of localising the sound source.
 Each participant performed this experiment three times.
@@
 
-Here we determined a participant's ability to differentiate the pitches of 2 tones being played to them, i.e.\ how well they can tell if a tone is high or low pitched.
-We played 2 tones to the participants in succession with the second tone being higher or lower-pitched than the first.
-The participants were then asked to select whether they interpreted the second tone as higher or lower-pitched than the first.
+Here we determined a participant's ability to differentiate the pitches of two different tones, i.e.\ how well they can tell if a tone is high or low pitched.
+We played two tones to the participants, in succession, with the second tone being higher or lower-pitched than the first.
+The participants were then asked to select which tone was higher or lower.
 
@@
 The tone difference depends on how well the participant can tell the tones apart.
-Like the sound localisation experiment, a 2-up, 1-down step process is used: for every 2 consecutive correct answers, the pitch difference between the tones is halved and is doubled for every incorrect answer.
-2 step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
-The termination condition is when the 2 step sequences are within 1 octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2^1$) for 3 consecutive answers.
+Like the sound localisation experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
+Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
+The termination condition is when the two-step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2$) for three consecutive answers.
 Each participant performed this experiment twice.
 
-\subsection{Target Search}
+\subsection{Target Search} \label{sec:target_search}
 
 To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
-The participants were given a Tango device running an app written for the experiment that generates a set of virtual targets and presents them to each participants, one at a time. 
+
+The participants were given a Tango device running an app that implements the experimental setup in~\cref{fig:pipeline}.
+The app generates a set of virtual targets and presents them to each participants through the audio interface, one at a time.
 The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
-Each target's angular position is communicated to the participant through the audio interface, the output of which is adjusted in real-time as the participant points the device around. 
-When a participant was confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
+Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
+When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
 The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
@@
 
-As part of this experiment, we wanted to see how changing the gradient of the pitch function affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
-Pitch limits of 1, 2 and 3 octaves above and below the neutral tone was then set of the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively.
-These linear gain functions are visualised in \cref{fig:pitch-gain}.
+As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\cref{fig:pitch-gain}, affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
+Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings, respectively.
 
-\subsection{Metrics}
+\subsection{Metrics} \tofix{If this is for the Target Search experiments only, it should be a \textbackslash subsubsection}
 
-We use two different metrics to compare the three different pitch gradient settings: the acquisition accuracy and search time.
+We use two different metrics to compare the three different pitch gradient settings \tofix{Which three settings? Clarify}: acquisition accuracy and search time.
 The accuracy is given as the difference between the Tango's orientation at the time the participant confirmed they were on target, and the target's actual orientation.
@@
   \label{eq:fitts-base}
-  t = a + bID,
+  t = a + b~ID,
 \end{equation}
@@
   \label{eq:fitts-we}
-  w_e = \sqrt{2\pi e}\sigma = 4.133\sigma,
+  w_e = \sqrt{2\pi e}~\sigma = 4.133~\sigma,
 \end{equation}
@@
 \noindent
-where $IP = \frac{1}{t}$ when $\sigma=0$.
+where $IP = \frac{1}{t}$ when $\sigma=0$ \tofix{Why? Also from [38]?}.
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old, 40 female, 16 female).
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old; 40 female, 16 female \tofix{Males?
+Numbers don't match...}).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
-Each participant performed 3 sets of experiments each, with the 2 characterisation experiments preceding the final target-search experiment. 
-Both groups were given some time before the experiment target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
-Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took.
+Each participant performed three sets of experiments each, with the two characterisation experiments in Sec.~\ref{sec:participant_characterisation} preceding the final target-search experiment in Sec.~\ref{sec:target_search}.
+Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
+Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
 

### 2019-11-01 paper.tex
Addressed Nicola's concerns and edits

@@
 
-\tofix{Add a short intro for this section, similar to what you had in the original paper.}
+We performed a set of experiments with the audio interface to determine how effective it is at directing a user to adjust the pan and elevation angles of a camera for point it to a target.
+Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics.
+The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
+We also tested the system with a group of severely sight impaired participants and compared their data to the blindfolded dataset.
+The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
 
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines.
-$F$ indicates a feedback signal and $P$ a pose signal.
-\tofix{Remove ``Vibration, Voice Output'' from top box.} }\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
 \end{figure}
 
-\subsection{Participant Characterisation} \label{sec:participant_characterisation}
+\subsection{Participant Characterisation}\label{sec:participant_characterisation}
 
-In addition to the target searching experiment, another set of experiments \tofix{You haven't talked about target search yet, maybe start with ``A preliminary set of experiments''} were conducted to characterise the participants' hearing characteristics.
+A preliminary set of experiments were conducted to characterise the participants' hearing characteristics.
 The measured characteristics were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
@@
 We also use two different step sequences, one starting at a large angular distance (\SI{45}{\degree}) from the user and the other at the minimum distance (approximately \SI{1}{\degree}), giving an `easy' and a `hard' progression respectively.
-The terminating condition for the experiment is when the two sequences converge to within two intervals of one another \tofix{Not clear, can you rephrase it?} for three consecutive guesses.
+The terminating condition for the experiment is when the two sequences converge to within two intervals of one another for three consecutive guesses.
+For example, the experiment will terminate when one sequence is set to \SI{11.25}{\degree} and the other is between \SI{2.8}{\degree} or \SI{45}{\degree} for three consecutive guesses.
 This gives a distance band where the participant is capable of localising the sound source.
@@
 The termination condition is when the two-step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2$) for three consecutive answers.
+For example, the experiment will terminate when one sequence is set to \SI{64}{\hertz} and the other is between \SI{32}{\hertz} or \SI{128}{\hertz} for three consecutive guesses.
 Each participant performed this experiment twice.
@@
 
-\subsection{Metrics} \tofix{If this is for the Target Search experiments only, it should be a \textbackslash subsubsection}
-
-We use two different metrics to compare the three different pitch gradient settings \tofix{Which three settings? Clarify}: acquisition accuracy and search time.
+We use two different metrics to compare the three different pitch gradient settings: acquisition accuracy and search time.
 The accuracy is given as the difference between the Tango's orientation at the time the participant confirmed they were on target, and the target's actual orientation.
@@
 \noindent
-where $IP = \frac{1}{t}$ when $\sigma=0$ \tofix{Why? Also from [38]?}.
+where $IP = \frac{1}{t}$ when $\sigma=0$.% When sigma=0, then ID=log2(0/we + 1) = log2(1) = 0
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old; 40 female, 16 female \tofix{Males?
-Numbers don't match...}).
+Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old; 36 female, 14 male).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.

### 2019-11-04 paper.tex
revised up to sec 5.2

@@
 
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango} and \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
+The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango} and \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
 It also provides access to Android's full range of interface tools and I/O options. 
-Furthermore, a set of bone-conduction headphones (pictured in \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
+Furthermore, a set of bone-conduction headphones (pictured in \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
 
@@
 
-The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a discussion on the design and implementation of our interface in \cref{sec:system-description}.
-This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiments} and \cref{sec:results}.
-Finally, the paper concludes with a summary and a short discussion on future research prospects in \cref{sec:conclusion}.
+The rest of the paper starts by discussing previous relevant works and research in \Cref{sec:prev-work}, followed by a discussion on the design and implementation of our interface in \Cref{sec:system-description}.
+This is followed by a description of the experiments that were conducted and a discussion of their results in \Cref{sec:experiments} and \Cref{sec:results}.
+Finally, the paper concludes with a summary and a short discussion on future research prospects in \Cref{sec:conclusion}.
 
@@
 Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
-The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.
+The AfterShockz headphones (\Cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.
 
@@
 
-The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
+The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \Cref{fig:cam-coords}.
 Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
@@
 We set the pitch limits to two octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
-The linear function is visualised in \cref{fig:pitch-gain}.
+The linear function is visualised in \Cref{fig:pitch-gain}.
 
@@
 
-A diagram of the experimental system pipeline is shown in~\cref{fig:pipeline}, where the arrows indicate the direction of the information flow.
+A diagram of the experimental system pipeline is shown in~\Cref{fig:pipeline}, where the arrows indicate the direction of the information flow.
 When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
@@
 
-\subsubsection{Sound Localisation}
+\subsubsection{Sound Localisation} \label{sec:sound_localisation}
 
@@
 
-\subsubsection{Pitch Discrimination}
+\subsubsection{Pitch Discrimination} \label{sec:pitch_discrimination}
 
@@
 
-The participants were given a Tango device running an app that implements the experimental setup in~\cref{fig:pipeline}.
+The participants were given a Tango device running an app that implements the experimental setup in~\Cref{fig:pipeline}.
 The app generates a set of virtual targets and presents them to each participants through the audio interface, one at a time.
@@
 
-As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\cref{fig:pitch-gain}, affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
+As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\Cref{fig:pitch-gain}, affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
 Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings, respectively.
@@
   \label{eq:fitts-performance}
-  IP = \frac{ID}{t},
+  IP = \frac{ID}{t}.
 \end{equation}
 
-\noindent
-where $IP = \frac{1}{t}$ when $\sigma=0$.% When sigma=0, then ID=log2(0/we + 1) = log2(1) = 0
+% \noindent
+% where $IP = \frac{1}{t}$ when $\sigma=0$.% When sigma=0, then ID=log2(0/we + 1) = log2(1) = 0
 
@@
 
-\subsection{Sound Localisation}
+\subsection{Characterisation of Sound Localisation}
 
-\cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from.
+\Cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from. 
+%
+It can be seen that the vast majority of guesses for both groups were correct.
+For Group \textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
+This indicates that the participants in \textit{G1} consistently progressed through the distance intervals and we can therefore conclude they had little difficulty determining sound direction.
 
@@
 
-From inspection of \cref{fig:sound-localisation}, it can be seen that the vast majority of guesses for both groups were correct.
-For Group \textit{G1}, the majority of erroneous guesses were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour and indicates that the participants consistently progressed through the distance intervals.
-We can therefore conclude that the participants from \textit{G1} had little difficulty determining sound direction.
+Group \textit{G2} also displays a concentration of erroneous guesses in the central interval.
+However, it also shows more errors in other distance intervals and a more even progression towards the centre.
+This could indicate that, instead of terminating the experiment by bringing the two sequences within one interval of one another \tofix{I would just say ``terminating the experiment as explained in Sec.~\ref{sec:sound_localisation}'', but then there you said within two intervals, not one...}, there was more switching back and forth between the three central intervals.
 
-Group \textit{G2} also displays a concentration of erroneous guesses in the centre interval.
-However, it also has more incorrect guesses in other distance intervals and exhibits a more even progression through the distance intervals towards the centre.
-This could indicate that instead of terminating the experiment through bringing the 2 sequences within 1 interval of one another, there was more switching back and forth between the centre 3 intervals.
+These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy.
+These results are in line previous literature, confirming that humans are very adept at localising a sound source, particularly in the pan dimension.
 
-These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy and are in line with what we expected based on literature that indicate that humans are very adept at localising a sound source, particularly in the pan dimension.
+\subsection{Characterisation of Pitch Discrimination}
 
-\subsection{Pitch Discrimination}
-
-The results of the pitch discrimination experiment are shown in \cref{fig:pitch-discrimination} where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
-The latter is given in terms of semitone differences which is obtained with
+The results of the pitch discrimination experiment are shown in \Cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
+\tofix{The $\Delta f$ explanation should be moved to Sec.~\ref{sec:pitch_discrimination}}
+The latter is given in terms of semitone-differences which is obtained with
 
@@
 
-For Group \textit{G1}, we see that their guesses seem normally spread around the 0 semitone difference interval and, as expected, the highest proportion of incorrect guesses occur in the $[-0.25, 0.25]$ semitone difference interval.
-The guesses from Group \textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone difference interval.
+For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.
+The guesses from Group \textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.
 
-Assuming these differences are normally spread, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
-We then used each CDF's parameters to determine a frequency cut-off threshold where the participant could not longer reliably tell tones apart and is set to contain 75\% of each participant's correct guesses.
-The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones and can be used to improve the interface's frequency profile and performance.
-\cref{fig:pitch-thresholds} shows the threshold distribution for each group, along with the median value. 
-The median is used for each grouping given the skewed plot and was found to be approximately 0.4 semitones for each group.
+Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
+We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
+The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones.
+It can also be used to improve the interface's frequency profile and performance.
+\Cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value,
+%The median is used for each grouping given the skewed plot and
+which was found to be approximately 0.4 semitones for each group.
 
@@
 
-The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other.
-A set of box-plots of the angle errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
-The results are summarised in \cref{tab:target-results}.
+The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \Cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other.
+A set of box-plots of the angle errors are also given in \Cref{fig:target-boxplot-error} for each audio setting.
+The results are summarised in \Cref{tab:target-results}.
 
@@
 The Shapiro-Wilkes test for normality reveals that none of these distributions are normally spread and accordingly, the Pearson test is used to investigate the correlation between the actual target location and participants' pointing location.
-These results are included in \cref{tab:target-results}.
+These results are included in \Cref{tab:target-results}.
 The Pearson correlation scores for Group \text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77], p < 0.001; r_{elevation} \in [0.36, 0.49], p < 0.001$), showing that the both the pan and elevation cues roughly worked as expected.
@@
 The medians of these data groupings are then used as individual samples that represent an individual participant's performance for each setting.
-\cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots, while \cref{fig:target-boxplot-absolute-errors} shows the collection of absolute errors.
+\Cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots, while \Cref{fig:target-boxplot-absolute-errors} shows the collection of absolute errors.
 
@@
 
-The box-plots in \cref{fig:target-boxplot-error} show that the error in the pan dimension is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
+The box-plots in \Cref{fig:target-boxplot-error} show that the error in the pan dimension is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
 However, using the Friedman test for repeated measures on the medians of absolute errors, these divergences are found to not be significant ($p_{G1} = 0.17, p_{G2} = 0.09$), showing that spatial perception and accuracy is not affected by changes in the tone's pitch.
-This is further demonstrated in the box-plots in \cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all 3 settings.
+This is further demonstrated in the box-plots in \Cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all 3 settings.
 
-Regarding the errors in the elevation dimension in \cref{fig:target-boxplot-error}, we observe in Group \textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings respectively and a median gradually approaching \SI{0}{\radian}.
+Regarding the errors in the elevation dimension in \Cref{fig:target-boxplot-error}, we observe in Group \textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings respectively and a median gradually approaching \SI{0}{\radian}.
 A similar trent is observed for Group \textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group \textit{G1}.
-\cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the 3 settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
+\Cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the 3 settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
 Further analysis of the medians of the absolute elevation error data with the Friedman test reveals that the results for the different settings only Group \textit{G1} are significantly different from one another ($p_{G1} = 0.002, p_{G2} = 0.32$).
@@
 
-Comparing the distributions for each setting between the 2 groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all 3 settings are not significantly different from one another for both groups in both the pan and elevation dimensions (the $p$-values are summarised in \cref{tab:inter-group-results}).
+Comparing the distributions for each setting between the 2 groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all 3 settings are not significantly different from one another for both groups in both the pan and elevation dimensions (the $p$-values are summarised in \Cref{tab:inter-group-results}).
 This results confirms that the errors produced between the blindfolded and participants with severe sight impairments are statistically similar in nature and both groups can reasonably be expected to produce similar error levels should the experiments be repeated with a different population.
@@
 
-To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty as defined by \cref{eq:fitts-base}.
-The data is binned in intervals of the effective target width ($w_e$) as given by \cref{eq:fitts-we} and are plotted for each gradient setting. 
-A logarithmic line of best fit is also fitted through the binned data's median values through means of regression and all the results are presented in \cref{fig:fitts-results}.
+To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty as defined by \Cref{eq:fitts-base}.
+The data is binned in intervals of the effective target width ($w_e$) as given by \Cref{eq:fitts-we} and are plotted for each gradient setting. 
+A logarithmic line of best fit is also fitted through the binned data's median values through means of regression and all the results are presented in \Cref{fig:fitts-results}.
 
@@
 
-These results allows us to calculate and plot an index of performance, as given in \cref{eq:fitts-performance}, for each setting in \cref{fig:fitts-ips}.
-Their results are summarised in \cref{tab:fitts-results}.
+These results allows us to calculate and plot an index of performance, as given in \Cref{eq:fitts-performance}, for each setting in \Cref{fig:fitts-ips}.
+Their results are summarised in \Cref{tab:fitts-results}.
 
@@
 This is supported by the results from the Friedman test that shows that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001, p_{lo-hi} < 0.001$), while the \textit{med} and \textit{hi} are not different to one another ($p_{med-hi} = 0.85$).
-The results for Group \textit{G2} shows generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
+The results for Group \textit{G2} shows generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \Cref{fig:fitts-results}.
 Again, following results from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin compared to the \textit{med} setting with the Wilcoxon test with Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results respectively.
@@
 
-From \cref{fig:fitts-ips}, there is significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
+From \Cref{fig:fitts-ips}, there is significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
 This is further supported by the Kruskal-Wallis test that reveals that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001, p_{med} < 0.001, p_{hi} < 0.001$).
@@
 
-With respect to the target acquisition results, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings respectively, (see \cref{tab:target-results}) seems indicate that that simply increasing the frequency gradient will lead to increased performance.
-However, \cref{fig:pitch-thresholds-hist} indicates that the frequency difference between the on-target tone and the selected tone in the \textit{hi} setting is approaching the cut-off frequency for Group \textit{G1}, indicating the point at which increasing the gradient produces diminishing returns on performance.
+With respect to the target acquisition results, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings respectively, (see \Cref{tab:target-results}) seems indicate that that simply increasing the frequency gradient will lead to increased performance.
+However, \Cref{fig:pitch-thresholds-hist} indicates that the frequency difference between the on-target tone and the selected tone in the \textit{hi} setting is approaching the cut-off frequency for Group \textit{G1}, indicating the point at which increasing the gradient produces diminishing returns on performance.
 Indeed, the participants from Group \textit{G2} seems to have passed this threshold and reached a saturation point where they could no longer reliably tell changes in the tone apart any longer.

### 2019-11-04 paper.tex
Moved Delta_f to other section

@@
 
-\subsubsection{Pitch Discrimination} \label{sec:pitch_discrimination}
+\subsubsection{Pitch Discrimination}\label{sec:pitch_discrimination}
 
@@
 For example, the experiment will terminate when one sequence is set to \SI{64}{\hertz} and the other is between \SI{32}{\hertz} or \SI{128}{\hertz} for three consecutive guesses.
+Pitch differences are measured in semitones, which can be obtained with
+
+\begin{equation}
+\label{eq:semitone-difference}
+  \Delta f = 12\log_2\frac{f_0}{f_1}, 
+\end{equation}
+
+\noindent where $f_0$ and $f_1$ are the frequencies of the first and second tone respectively.
 Each participant performed this experiment twice.
 
-\subsection{Target Search} \label{sec:target_search}
+\subsection{Target Search}\label{sec:target_search}
 
@@
 However, it also shows more errors in other distance intervals and a more even progression towards the centre.
-This could indicate that, instead of terminating the experiment by bringing the two sequences within one interval of one another \tofix{I would just say ``terminating the experiment as explained in Sec.~\ref{sec:sound_localisation}'', but then there you said within two intervals, not one...}, there was more switching back and forth between the three central intervals.
+This could indicate that, instead of terminating the experiment as described in \cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals.
 
@@
 The results of the pitch discrimination experiment are shown in \Cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
-\tofix{The $\Delta f$ explanation should be moved to Sec.~\ref{sec:pitch_discrimination}}
-The latter is given in terms of semitone-differences which is obtained with
-
-\begin{equation}
-\label{eq:semitone-difference}
-  \Delta f = 12\log_2\frac{f_0}{f_1}.
-\end{equation}
-
 For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.

### 2019-11-06 paper.tex
finished revision of sec 5

@@
 Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
+The authors generally report favorable results for this guidance approach when used with standard over-ear headphones or speakers. 
 However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
-This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\cite{stanley2006lateralization}.
-In~\cite{durette2008visuo}, they transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
-We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\cite{lock2019bone}.
+Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
+\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
 We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
@@
 Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
-Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\cite{golledge2004stated,yusif2016older,arditi2013user}.
-To address these issues, we implemented a handheld mobile system that is based on a concept proposed in~\cite{lock2017portable,lock2019active} and tested in~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
+Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
+To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
 This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
@@
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\cite{lichtenstein2012headphone}.
+This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\citep{lichtenstein2012headphone}.
 Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
@@
 However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
-The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old; 36 female, 14 male).
+Group~\textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old; 36 female, 14 male).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
-Each participant performed three sets of experiments each, with the two characterisation experiments in Sec.~\ref{sec:participant_characterisation} preceding the final target-search experiment in Sec.~\ref{sec:target_search}.
+Each participant performed three sets of experiments each, with the two characterisation experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
 Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
@@
 It can be seen that the vast majority of guesses for both groups were correct.
-For Group \textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
+For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
 This indicates that the participants in \textit{G1} consistently progressed through the distance intervals and we can therefore conclude they had little difficulty determining sound direction.
@@
 
-Group \textit{G2} also displays a concentration of erroneous guesses in the central interval.
+Group~\textit{G2} also displays a concentration of erroneous guesses in the central interval.
 However, it also shows more errors in other distance intervals and a more even progression towards the centre.
-This could indicate that, instead of terminating the experiment as described in \cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals.
+This could indicate that, instead of terminating the experiment as described in \Cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals.
 
@@
 The results of the pitch discrimination experiment are shown in \Cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
-For Group \textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.
-The guesses from Group \textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.
+For Group~\textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.
+The guesses from Group~\textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.
 
@@
 %The median is used for each grouping given the skewed plot and
-which was found to be approximately 0.4 semitones for each group.
+which was found to be approximately 0.4 semitones for each group. \tofix{And \Cref{fig:pitch-thresholds-hist}?}
 
@@
 
-The results from the target search experiment in the pan dimension are given on the abscissa of the 2D histograms in \Cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other.
+The results from the target search experiment shown on the 2D histograms in \Cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other. 
 A set of box-plots of the angle errors are also given in \Cref{fig:target-boxplot-error} for each audio setting.
@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
+  \caption{Box-plots of the median pan and elevation errors for each audio setting. }\label{fig:target-boxplot-error}
+\end{figure}
+
 \begin{table}
@@
   \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
-  \begin{tabular}{p{0.5cm}p{1.3cm}p{0.9cm}p{2cm}p{2cm}p{2.25cm}}
+  \begin{tabular}{p{0.5cm}p{1.5cm}p{1.5cm}p{3.0cm}p{3.0cm}p{3.0cm}}
     \toprule
@@
     \multirow{6}{*}{\textit{G1}}
-    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.25\pm0.27$ & $0.75, p < 0.001$ \\
-    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.26\pm0.27$ & $0.77, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72, p < 0.001$ \\ \cline{2-6}
-    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.42\pm0.31$ & $0.36, p < 0.001$ \\
-    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.44\pm0.24$ & $0.49, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.36\pm0.29$ & $0.48, p < 0.001$ \\ \midrule
+    &           & \textit{lo}  & $-0.02\pm0.37$ & $0.25\pm0.27$ & $0.75,~p < 0.001$ \\
+    & Pan       & \textit{med} & $-0.01\pm0.37$ & $0.26\pm0.27$ & $0.77,~p < 0.001$ \\
+    &           & \textit{hi}  & $-0.03\pm0.39$ & $0.26\pm0.29$ & $0.72,~p < 0.001$ \\ \cline{2-6}
+    &           & \textit{lo}  & $-0.12\pm0.51$ & $0.42\pm0.31$ & $0.36,~p < 0.001$ \\
+    & Elevation & \textit{med} & $-0.11\pm0.41$ & $0.44\pm0.24$ & $0.49,~p < 0.001$ \\
+    &           & \textit{hi}  & $-0.15\pm0.44$ & $0.36\pm0.29$ & $0.48,~p < 0.001$ \\ \midrule
     \multirow{6}{*}{\textit{G2}}
-    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.48\pm0.31$ & $0.10, p = 0.03$  \\
-    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.45\pm0.27$ & $0.13, p = 0.01$  \\
-    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21, p < 0.001$ \\\cline{2-6}
-    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.49\pm0.39$ & $0.03, p = 0.48$  \\
-    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.42\pm0.33$ & $0.31, p < 0.001$ \\
-    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.36\pm0.32$ & $0.40, p < 0.001$ \\ 
+    &           & \textit{lo}  & $-0.01\pm0.37$ & $0.48\pm0.31$ & $0.10,~p = 0.03$  \\
+    & Pan       & \textit{med} & $ 0.04\pm0.53$ & $0.45\pm0.27$ & $0.13,~p = 0.01$  \\
+    &           & \textit{hi}  & $ 0.03\pm0.48$ & $0.36\pm0.22$ & $0.21,~p < 0.001$ \\\cline{2-6}
+    &           & \textit{lo}  & $-0.30\pm0.59$ & $0.49\pm0.39$ & $0.03,~p = 0.48$  \\
+    & Elevation & \textit{med} & $-0.42\pm0.45$ & $0.42\pm0.33$ & $0.31,~p < 0.001$ \\
+    &           & \textit{hi}  & $-0.37\pm0.43$ & $0.36\pm0.32$ & $0.40,~p < 0.001$ \\ 
     \bottomrule
@@
 
-The Shapiro-Wilkes test for normality reveals that none of these distributions are normally spread and accordingly, the Pearson test is used to investigate the correlation between the actual target location and participants' pointing location.
+The Shapiro-Wilkes test for normality reveals that none of these distributions are normally spread.
+Therefore, the Pearson test is used to investigate the correlation between the actual target location and participants' pointing location.
 These results are included in \Cref{tab:target-results}.
-The Pearson correlation scores for Group \text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77], p < 0.001; r_{elevation} \in [0.36, 0.49], p < 0.001$), showing that the both the pan and elevation cues roughly worked as expected.
-However, the correlation scores for Group \textit{G2} are significantly weaker, with a pan angle correlation of $r_{pan} \in [0.1, 0.21], p < 0.03$.
-With the exception of the \textit{lo} setting ($p_{lo} = 0.48$), the elevation correlation is somewhat stronger, with $r_{elevation} \in [0.31, 0.40], p < 0.001$.
+The Pearson correlation scores for Group~\text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.
+However, the correlation scores for Group~\textit{G2} are significantly weaker, with a pan angle correlation $r_{pan} \in [0.1, 0.21],~p < 0.03$.
+With the exception of the \textit{lo} setting ($p_{lo} = 0.48$), the elevation correlation is generally stronger, with $r_{elevation} \in [0.31, 0.40],~p < 0.001$.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
-  \caption{Box-plots of the median pan and elevation errors for each setting. }\label{fig:target-boxplot-error}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 
-The box-plots in \Cref{fig:target-boxplot-error} show that the error in the pan dimension is roughly centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
-However, using the Friedman test for repeated measures on the medians of absolute errors, these divergences are found to not be significant ($p_{G1} = 0.17, p_{G2} = 0.09$), showing that spatial perception and accuracy is not affected by changes in the tone's pitch.
-This is further demonstrated in the box-plots in \Cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all 3 settings.
+The box-plots in \Cref{fig:target-boxplot-error} show that the error in the pan dimension is approximately centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
+However, using the Friedman test for repeated measures on the medians of absolute errors, these divergences are found to be not significant ($p_{G1} = 0.17,~p_{G2} = 0.09$), showing that spatial perception and accuracy are not affected by changes in the tone's pitch.
+This is further demonstrated in the box-plots in \Cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all three settings.
 
-Regarding the errors in the elevation dimension in \Cref{fig:target-boxplot-error}, we observe in Group \textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings respectively and a median gradually approaching \SI{0}{\radian}.
-A similar trent is observed for Group \textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group \textit{G1}.
-\Cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the 3 settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
-Further analysis of the medians of the absolute elevation error data with the Friedman test reveals that the results for the different settings only Group \textit{G1} are significantly different from one another ($p_{G1} = 0.002, p_{G2} = 0.32$).
+Regarding the errors in the elevation dimension in \Cref{fig:target-boxplot-error}, we observe in Group~\textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings, respectively, and a median gradually approaching \SI{0}{\radian}.
+A similar trent is observed for Group~\textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group~\textit{G1}.
+\Cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the three settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
+Further analysis of the medians of the absolute elevation error with the Friedman test reveals that the results for the different settings are significantly different from each other only for Group~\textit{G1} ($p_{G1} = 0.002,~p_{G2} = 0.32$).
+
 A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
-This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group \textit{G1} ($p_{lo-med} = 0.003, p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which of the \textit{med} and \textit{hi} settings are better for Group \textit{G1}.
-Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group \textit{G2}, but this may be caused by the relatively small sample size for each setting.
-%while Group \textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
-It is also noted that there is a significant negative error bias in all of the settings in both groups which is possibly caused by a cognitive constraint introduced by the floor where the participants believed that the targets could not appear below the ground.
-Since this bias seems constant in nature, it can be addressed in the future by adjusting the frequency parameters of the interface and shifting it by a constant offset.
+This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}.
+Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may be caused by the relatively small sample size for each setting.
+%while Group~\textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
+We also noted that there is a significant negative error bias in the elevation for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
+Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset.
 
-Comparing the distributions for each setting between the 2 groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all 3 settings are not significantly different from one another for both groups in both the pan and elevation dimensions (the $p$-values are summarised in \Cref{tab:inter-group-results}).
-This results confirms that the errors produced between the blindfolded and participants with severe sight impairments are statistically similar in nature and both groups can reasonably be expected to produce similar error levels should the experiments be repeated with a different population.
-Consequently, with the significantly smallest median elevation error, we can conclude that the \textit{hi} setting is the best setting to use to minimise the elevation angle error and that the pan error is completely independent of the setting in use.
+Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \Cref{tab:inter-group-results}).
+This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
+Consequently, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.
 
@@
 
-\subsection{Time to Target}
+\subsection{Time-to-Target}
 
-To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty as defined by \Cref{eq:fitts-base}.
-The data is binned in intervals of the effective target width ($w_e$) as given by \Cref{eq:fitts-we} and are plotted for each gradient setting. 
-A logarithmic line of best fit is also fitted through the binned data's median values through means of regression and all the results are presented in \Cref{fig:fitts-results}.
+To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty, as defined by \Cref{eq:fitts-base}.
+The data is binned in intervals of the effective target width~($w_e$), given by \Cref{eq:fitts-we}, and are plotted for each pitch gradient setting. \tofix{The word 'low' is missing in the figure} 
+A logarithmic line is fitted through the bins' median values by regression and all the results are presented in \Cref{fig:fitts-results}.
 
@@
 
-For Group \textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all 3 settings. 
-This is confirmed with strong Pearson correlation scores for each setting ($r_{lo} = 0.76, p_{lo} = 0.045; r_{med} = 0.96, p_{med}<0.001; r_{hi} = 0.86, p_{hi} = 0.013$).
-Regarding Group \textit{G2}¸ we observe larger spreads for each binned dataset, indicating less consistency in the time to target results for participants with severe sight impairments.
-This could be a result of taking each participant's result as a single datum and the smaller population in Group \textit{G2}.
-Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88, p_{med} = 0.008; r_{hi} = 0.84, p_{med} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08, p_{lo} = 0.85$).
+For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
+This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.76,~p_{lo} = 0.045;~r_{med} = 0.96,~p_{med}<0.001;~r_{hi} = 0.86,~p_{hi} = 0.013$).
+Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data plots, indicating less consistency in the time-to-target results for participants with severe sight impairments.
+This could be due to each participant's result taken as a single datum and to the smaller population in Group~\textit{G2}.
+Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{med} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).
 
-These results allows us to calculate and plot an index of performance, as given in \Cref{eq:fitts-performance}, for each setting in \Cref{fig:fitts-ips}.
-Their results are summarised in \Cref{tab:fitts-results}.
-
-\begin{figure}
+\begin{figure}[t]
   \centering
-  \includegraphics[width=0.7\textwidth]{figures/fitts_ips.png}
+  \includegraphics[width=1.0\textwidth]{figures/fitts_ips.png}
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
 \end{figure}
+
+These results allows us to calculate and plot in \Cref{fig:fitts-ips} an index of performance, as given by \Cref{eq:fitts-performance}, for each audio setting.
+The results are summarised in \Cref{tab:fitts-results}.
+For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
+This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001,~p_{lo-hi} < 0.001$).
+The \textit{med} and \textit{hi}, instead, are not significantly different from each other ($p_{med-hi} = 0.85$).
+The results for Group~\textit{G2} show generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \Cref{fig:fitts-results}.
+Again, from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin, compared to the \textit{med} setting, with the Wilcoxon test and Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results, respectively.
+This seems to indicate that, for both groups, the \textit{lo} setting produces the highest level of performance, followed by the \textit{hi} setting.
 
@@
   \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:fitts-results}
-  \begin{tabular}{p{0.5cm}p{1.2cm}p{2.3cm}}
+  \begin{tabular}{p{0.5cm}p{1.5cm}p{2.5cm}}
     \toprule
@@
 
-For the results from Group \textit{G1}, there is a fairly consistent level of performance between the 3 settings, with the \textit{lo} producing the highest indices of performance overall, i.e.\ the participants found the targets with the smallest error in the least about of time with the \textit{lo} setting.
-This is supported by the results from the Friedman test that shows that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections that show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001, p_{lo-hi} < 0.001$), while the \textit{med} and \textit{hi} are not different to one another ($p_{med-hi} = 0.85$).
-The results for Group \textit{G2} shows generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \Cref{fig:fitts-results}.
-Again, following results from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin compared to the \textit{med} setting with the Wilcoxon test with Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results respectively.
-These results seem to indicate that for both groups, the \textit{lo} produces the highest level of performance followed, by the \textit{hi} setting.
-
-From \Cref{fig:fitts-ips}, there is significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
-This is further supported by the Kruskal-Wallis test that reveals that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001, p_{med} < 0.001, p_{hi} < 0.001$).
-The significant difference between the blindfolded group and the group with severely sight impaired participants seems to indicate that the latter group take significantly longer to find the target. 
-However, it is unclear whether this is a systematic cause or a difference in search strategy between the 2 groups, e.g.\ \textit{G2} preferring, on average, a slower more methodical approach.
+\Cref{fig:fitts-ips} shows a significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
+This is further supported by the Kruskal-Wallis test, revealing that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001,~p_{med} < 0.001,~p_{hi} < 0.001$).
+The significant difference between the blindfolded group and the group of participants with visual impairments seems to indicate that the latter require significantly more time to find the target. 
+However, it is unclear whether this is a systematic cause or a difference in search strategy between the two groups, e.g.\ \textit{G2} preferring, on average, a slower and more methodical approach.
 
@@
 
-There seems to be an interesting contrast brought forward by the results for the accuracy and time performance.
-That is, the \textit{hi} produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings respectively. 
-However, this trend is almost reversed in the time to target performance given by Fitts's model where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
-Since Fitts's model takes the angular error into account, once might reasonably have expected that the results for both datasets would have been more similar. 
-However, Fitts's relationship does not model for different stimuli and we therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting that allows for finer adjustments to be made to the device's orientation and get it closer to pointing to the target, but at the cost of a higher average time to find the target.
-This seems to indicate a speed-accuracy trade-off in finding the targets and with the Fitts relationship obtained here, we can modify the interface to prioritise different metrics and produce the correct output.
+The results for the accuracy and time performance with the proposed audio interface shows an interesting contrast.
+That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
+However, this trend is almost reversed in the time-to-target Fitts's model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings, respectively.
+Since the Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
+However, the Fitts's model does not account for different stimuli.
+We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
+This seems to indicate a speed/accuracy trade-off in finding the targets.
+With the Fitts's model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
+\tofix{I reworded a few bits, check if still correct}
 
-With respect to the target acquisition results, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings respectively, (see \Cref{tab:target-results}) seems indicate that that simply increasing the frequency gradient will lead to increased performance.
-However, \Cref{fig:pitch-thresholds-hist} indicates that the frequency difference between the on-target tone and the selected tone in the \textit{hi} setting is approaching the cut-off frequency for Group \textit{G1}, indicating the point at which increasing the gradient produces diminishing returns on performance.
-Indeed, the participants from Group \textit{G2} seems to have passed this threshold and reached a saturation point where they could no longer reliably tell changes in the tone apart any longer.
+Regarding the target acquisition, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings (see \Cref{tab:target-results}) seems to indicate that simply increasing the pitch gradient leads to better target-pointing performance.
+However, \Cref{fig:pitch-thresholds-hist} shows that the frequency difference between the ``on-target'' tone and the selected one with the \textit{hi} setting approaches the cut-off frequency of Group~\textit{G1}, indicating the point at which increasing a gradient increase reduces the final performance.
+Indeed, the participants from Group~\textit{G2} seems to go beyond this threshold and reach a saturation point where they can no longer distinguish different tones.
+\tofix{I reworded a few bits, check if still correct}
 

### 2019-11-07 paper.tex
Minor typo fixes, fixed todos, modified plot

@@
 Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-The authors generally report favorable results for this guidance approach when used with standard over-ear headphones or speakers. 
+The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
 However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
@@
 This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
 We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
@@
 
-Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
+Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
@@
 It can also be used to improve the interface's frequency profile and performance. 
-\Cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value,
+\Cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
+\Cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
 %The median is used for each grouping given the skewed plot and
-which was found to be approximately 0.4 semitones for each group. \tofix{And \Cref{fig:pitch-thresholds-hist}?}
 
@@
 To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty, as defined by \Cref{eq:fitts-base}.
-The data is binned in intervals of the effective target width~($w_e$), given by \Cref{eq:fitts-we}, and are plotted for each pitch gradient setting. \tofix{The word 'low' is missing in the figure} 
+The data is binned in intervals of the effective target width~($w_e$), given by \Cref{eq:fitts-we}, and are plotted for each pitch gradient setting. 
 A logarithmic line is fitted through the bins' median values by regression and all the results are presented in \Cref{fig:fitts-results}.
@@
 This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.76,~p_{lo} = 0.045;~r_{med} = 0.96,~p_{med}<0.001;~r_{hi} = 0.86,~p_{hi} = 0.013$).
-Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data plots, indicating less consistency in the time-to-target results for participants with severe sight impairments.
-This could be due to each participant's result taken as a single datum and to the smaller population in Group~\textit{G2}.
+Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data plot, indicating less consistency in the time-to-target results for participants with severe sight impairments.
+This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}.
 Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{med} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).
@@
 That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
-However, this trend is almost reversed in the time-to-target Fitts's model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings, respectively.
+However, this trend is almost wholly reversed in the time-to-target results from the Fitts's model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
 Since the Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
@@
 With the Fitts's model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
-\tofix{I reworded a few bits, check if still correct}
 
-Regarding the target acquisition, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings (see \Cref{tab:target-results}) seems to indicate that simply increasing the pitch gradient leads to better target-pointing performance.
-However, \Cref{fig:pitch-thresholds-hist} shows that the frequency difference between the ``on-target'' tone and the selected one with the \textit{hi} setting approaches the cut-off frequency of Group~\textit{G1}, indicating the point at which increasing a gradient increase reduces the final performance.
-Indeed, the participants from Group~\textit{G2} seems to go beyond this threshold and reach a saturation point where they can no longer distinguish different tones.
-\tofix{I reworded a few bits, check if still correct}
+Regarding target acquisition, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings (see \Cref{tab:target-results}) seems to indicate that simply increasing the pitch gradient leads to better target-pointing performance.
+However, \Cref{fig:pitch-thresholds-hist} shows that the frequency difference between the ``on-target'' tone and the selected one with the \textit{hi} setting approaches the cut-off frequency of Group~\textit{G1}, indicating an inflection point where increasing the gradient reduces the final performance.
+Indeed, the participants from Group~\textit{G2} seem to go beyond this threshold and reach a saturation point where they can no longer reliably distinguish different tones.
 

### 2019-11-07 paper.tex
revised abstract and conclusions

@@
 
-\title{NEW TITLE}
+\title{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
 
@@
 \begin{abstract}
-  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
-  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
-  In prior work, we implemented and tested a audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
-  This approach was shown to work well and in this work we expand the number of tests and metrics to provide a more more in-depth evaluation of the proposed audio interface.
-  Specifically, we used a larger number of participants and found design limitations and a Fitts's Law-compliant trend that we can use to improve and refine the audio signals. 
+  Sound perception is a fundamentally important skill for many people with severe sight impairments.
+The research presented in this paper is part of the ActiVis project, the aim of which is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
+  This system requires an effective non-visual interface and therefore uses bone-conduction headphones to transmit audio instructions to the user.
+  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
+  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments.
+We analyse pros and cons of our design choices, and found that a Fitts's Law metric can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
+\tofix{Reworded, check if OK}
 \end{abstract}
@@
 
-The ActiVis\footnote{https://lcas.github.io/ActiVis/} project is working towards building an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
+The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
 Improvements to computer vision and machine learning techniques, as well as mobile commuting hardware improvements are exploited to make this system possible.
@@
   \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
-  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).}
+  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).
+\tofix{Update this figures to differ from AEIT)}}
 \end{figure}
@@
   \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
-Note the logarithmic scale of the frequency axis.}
+Note the logarithmic scale of the frequency axis.
+\tofix{Update this figure (e.g.
+use colors) to differ from AEIT)}}
 \end{figure}
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines.
+$F$ indicates a feedback signal and $P$ a pose signal.
+\tofix{Update this figure (e.g.
+use colors) to differ from AEIT)}}\label{fig:pipeline}
 \end{figure}
@@
 
-In this work, we expanded upon the initial investigation from~\citep{lock2019bone} and performed a wider number of tests with more participants where we investigated using spatialised sound with a varying tone to direct a user's gaze in more detail.
-We found that the blindfolded participants and participants with severe sight impairments had similar levels of performance in localising sound and differentiating between tones. 
-We also found that both groups managed to find a set of targets with similar levels of accuracy.
-However, the blindfolded group managed to outperform the group with severe sight impairments in terms of time to find the target. 
-We also tested different pitch gain gradient settings for the pitch and found that the performance in the pan dimension that uses spatialised signals, is independent of the pitch gradient setting.
-Furthermore, we found a speed-accuracy trade off between the settings, where a steeper pitch gain gradient produces a smaller angular error at the cost of decreased time performance. 
-This, along with the Fitts-like relationship that was found, can be used to improve and refine the interface in order to prioritise speed or accuracy and produce the desired output.
+In this paper we investigated the use of spatialised audio interface with varying pitch to guide a visually impaired user in a target pointing task.
+We found that the blindfolded participants and those with severe sight impairments performed similarly in localising sound sources and differentiating between tones. 
+We also found that both groups were able to find a set of randomly distribute set of direction targets with similar levels of accuracy.
+However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
+We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
+Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.
+higher time-to-target).
+These results, together with a a Fitts's Law analysis that confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
+\tofix{I reworded a few bits, check if still correct}
 
-The next steps for the project is to implement this interface into a guidance system and test the complete system's performance. 
-Implementing an auto-adaptive interface scheme can also now be considered.
+% The next steps for the project is to implement this interface into a guidance system and test the complete system's performance. 
+% Implementing an auto-adaptive interface scheme can also now be considered.
+\tofix{A little more effort in your (hypothetical) plans for future work.
+You could expand more the user-adaptation concept -- e.g.
+adapt to different users, or to the performance variations of the same user over time (like the ``progressive co-adaptation'' of~\cite{gallina2015progressive}).
+Also, what about adding extra modalities, like voice instructions or device vibrations?}
 

### 2019-11-07 paper.tex
Added conclusion, minor change to abstract, added references to previolusly-used figures

@@
 \begin{abstract}
-  Sound perception is a fundamentally important skill for many people with severe sight impairments.
+  Sound perception is a fundamental skill for many people with severe sight impairments.
   The research presented in this paper is part of the ActiVis project, the aim of which is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
-  This system requires an effective non-visual interface and therefore uses bone-conduction headphones to transmit audio instructions to the user.
+  This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
   It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
-  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments.
-We analyse pros and cons of our design choices, and found that a Fitts's Law metric can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
-\tofix{Reworded, check if OK}
+  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
+  In addition to producing state-of-the-art results, we found that Fitts's Law can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
 \end{abstract}
@@
   \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
-  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right).
-\tofix{Update this figures to differ from AEIT)}}
+  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right)~\citep{lock2019bone}.}
 \end{figure}
@@
   \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
-Note the logarithmic scale of the frequency axis.
-\tofix{Update this figure (e.g.
-use colors) to differ from AEIT)}}
+Note the logarithmic scale of the frequency axis~\citep{lock2019bone}.}
 \end{figure}
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines.
-$F$ indicates a feedback signal and $P$ a pose signal.
-\tofix{Update this figure (e.g.
-use colors) to differ from AEIT)}}\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}.}\label{fig:pipeline}
 \end{figure}
@@
 We found that the blindfolded participants and those with severe sight impairments performed similarly in localising sound sources and differentiating between tones. 
-We also found that both groups were able to find a set of randomly distribute set of direction targets with similar levels of accuracy.
+We also found that both groups were able to find a randomly distributed set of virtual targets with similar levels of accuracy.
 However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
 We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
-Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.
-higher time-to-target).
-These results, together with a a Fitts's Law analysis that confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
-\tofix{I reworded a few bits, check if still correct}
+Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.\ more time to reach the target).
+These results, together with an analysis done with Fitts's Law confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
 
-% The next steps for the project is to implement this interface into a guidance system and test the complete system's performance. 
-% Implementing an auto-adaptive interface scheme can also now be considered.
-\tofix{A little more effort in your (hypothetical) plans for future work.
-You could expand more the user-adaptation concept -- e.g.
-adapt to different users, or to the performance variations of the same user over time (like the ``progressive co-adaptation'' of~\cite{gallina2015progressive}).
-Also, what about adding extra modalities, like voice instructions or device vibrations?}
+This work identified a number of uncertainties that can be the focus of future work.
+These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias within the participants' minds, or whether there is a more complex underlying reason for the behaviour.
+Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.
+For example, the pitch gradient can be automatically adjusted over time by the device to provide a better match between the human and computer and increase overall target-finding performance.
+Indeed, the work by~\cite{gallina2015progressive} may serve as a good guideline for such a system.
+Additional feedback modes may also be added to allow for clearer guidance experience for the user, e.g.\ vibration signals to inform them when they point to the target or adjusting the volume to expand the system to three dimensions.
+With this kind of audio interface now better understood, it is ready to be implemented into a fully packaged guidance system for people with visual impairments.
 

### 2019-11-08 paper.tex
Fixed figures to make them different from previous submissions

@@
 
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango} and \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
+The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
 It also provides access to Android's full range of interface tools and I/O options. 
@@
   \centering
-  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
+  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.6\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
 ~
-  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
-~
-  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
-  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right)~\citep{lock2019bone}.}
+  \subfloat[]{\label{fig:participant}\includegraphics[width=0.3\columnwidth]{figures/vi_participant.pdf}}
+  \caption{Pictures of the former Tango tablet and the bone-conduction headphones used in this work (left), and a participant with visual impairments during an experiment (right)~\citep{lock2019bone}.}
 \end{figure}
@@
   \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
-\hfil
+~
   \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
   \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
-Note the logarithmic scale of the frequency axis~\citep{lock2019bone}.}
+Note the logarithmic scale of the frequency axis.
+}
 \end{figure}
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}.}\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
 \end{figure}

### 2019-11-11 paper.tex
Proofreading, improved layout. Pushing for review

@@
 \usepackage[natbibapa,nodoi]{apacite}
-
-% \usepackage{soul}
-% \DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}
-\usepackage{color}
-\newcommand{\tofix}[1]{\textcolor{red}{\bf{[#1]}}}
+\usepackage{todonotes}
 
@@
   We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
-  In addition to producing state-of-the-art results, we found that Fitts's Law can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
+  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
 \end{abstract}
@@
 The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
-Improvements to computer vision and machine learning techniques, as well as mobile commuting hardware improvements are exploited to make this system possible.
+Improvements to computer vision and machine learning techniques, as well as mobile computing hardware improvements are exploited to make this system possible.
 In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
-  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.6\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
+  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
 ~
-  \subfloat[]{\label{fig:participant}\includegraphics[width=0.3\columnwidth]{figures/vi_participant.pdf}}
-  \caption{Pictures of the former Tango tablet and the bone-conduction headphones used in this work (left), and a participant with visual impairments during an experiment (right)~\citep{lock2019bone}.}
+  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
+  \caption{Pictures of the former Tango tablet and the bone-conduction headphones used in this work (left), and a participant with visual impairments during an experiment (right).}
 \end{figure}
 
-Humans are able to determine the 3D position of a sound source and by exploiting this natural ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
+Humans are naturally able to determine the 3D position of a sound source and by exploiting this ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
 A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals sued with expensive closed-cup headphones~\citep{lock2019bone,macdonald2006spatial} and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones~\citep{lock2019bone,macdonald2006spatial} and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
@@
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still relies on sound to detect, for example, oncoming vehicles and people~\citep{lichtenstein2012headphone}.
+This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\citep{lichtenstein2012headphone}.
 Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
-The AfterShockz headphones (\Cref{fig:tango-headphone}) were ultimately selected since they do not interfere on other sounds and are also more discreet than the larger over-ear headphones.
+The AfterShockz headphones (\Cref{fig:tango-headphone}) were ultimately selected for the aforementioned reasons of non-interference and increased discretion when compared to larger over-ear headphones.
 
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
@@
 
-The pitch is changed as a linear function of the elevation angle and the gradient is determined by setting the angle and pitch limits.
+The pitch is changed as a linear function of the elevation angle (see \Cref{fig:pitch-gain}) and the gradient is determined by setting the angle and pitch limits.
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
@@
 After practical tests with the interface, we set the neutral pitch to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
-We set the pitch limits to two octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
-The linear function is visualised in \Cref{fig:pitch-gain}.
+%We set the pitch limits to two octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
 
@@
 
-\subsubsection{Sound Localisation} \label{sec:sound_localisation}
+\subsubsection{Sound Localisation}\label{sec:sound_localisation}
 
@@
 Here we determined a participant's ability to differentiate the pitches of two different tones, i.e.\ how well they can tell if a tone is high or low pitched.
-We played two tones to the participants, in succession, with the second tone being higher or lower-pitched than the first.
+We played two tones to the participants in succession, with the second tone being higher or lower-pitched than the first.
 The participants were then asked to select which tone was higher or lower.
@@
 To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
-
 The participants were given a Tango device running an app that implements the experimental setup in~\Cref{fig:pipeline}.
-The app generates a set of virtual targets and presents them to each participants through the audio interface, one at a time.
+The app generates a set of virtual targets and presents them to each participant through the audio interface, one at a time.
 The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
@@
 
-As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\Cref{fig:pitch-gain}, affected target acquisition performance, e.g.\ does a steeper pitch gain function as a function of the elevation angle improve accuracy or decrease the search time?
-Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings, respectively.
+As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\Cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
+Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively, giving pitch intervals of
+
+\begin{gather*}
+  f_{lo}\in[\SI{256}{\hertz}, \SI{1024}{\hertz}]\\
+  f_{med}\in[\SI{128}{\hertz}, \SI{2048}{\hertz}]\\
+  f_{hi}\in[\SI{64}{\hertz}, \SI{4096}{\hertz}].
+\end{gather*}
 
@@
 The accuracy is given as the difference between the Tango's orientation at the time the participant confirmed they were on target, and the target's actual orientation.
-We separate the results of the tilt and pan dimensions in order to see how the different pitch gradients affect a participant's pointing accuracy.
+We separate the results of the elevation and pan dimensions in order to see how the different pitch gradients affect a participant's pointing accuracy.
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group~\textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 8 people with severe visual impairments (18--55 years old; 36 female, 14 male).
+Group~\textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18--55 years old; 36 female, 16 male).
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/pitch_discrimination.png}
+  \includegraphics[width=0.8\textwidth]{figures/pitch_discrimination.png}
   \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds.png}
+  \includegraphics[width=0.8\textwidth]{figures/pitch_thresholds.png}
   \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/pitch_thresholds_limits.png}
+  \includegraphics[width=0.8\textwidth]{figures/pitch_thresholds_limits.png}
   \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/target_errors.png}
+  \includegraphics[width=0.8\textwidth]{figures/target_errors.png}
   \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-errors}
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_median_error.png}
+  \includegraphics[width=0.8\textwidth]{figures/boxplot_target_search_median_error.png}
   \caption{Box-plots of the median pan and elevation errors for each audio setting. }\label{fig:target-boxplot-error}
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
+  \includegraphics[width=0.8\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
   \caption{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-boxplot-absolute-errors}
@@
 Regarding the errors in the elevation dimension in \Cref{fig:target-boxplot-error}, we observe in Group~\textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings, respectively, and a median gradually approaching \SI{0}{\radian}.
-A similar trent is observed for Group~\textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group~\textit{G1}.
+A similar trend is observed for Group~\textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group~\textit{G1}.
 \Cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the three settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
@@
 This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}.
-Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may be caused by the relatively small sample size for each setting.
+Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
 %while Group~\textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
-We also noted that there is a significant negative error bias in the elevation for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
+We also noted that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
 Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset.
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/fitts_fit.png}
+  \includegraphics[width=0.8\textwidth]{figures/fitts_fit.png}
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-results}
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/fitts_ips.png}
+  \includegraphics[width=0.8\textwidth]{figures/fitts_ips.png}
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
@@
 Since the Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
-However, the Fitts's model does not account for different stimuli.
+However, the Fitts's model does not account for changing stimuli and different strategies.
 We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
@@
 Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.\ more time to reach the target).
-These results, together with an analysis done with Fitts's Law confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
+These results, together with an analysis done with Fitts's Law that confirms its applicability to this type of audio interface, provide a useful baseline to improve and refine the latter in future applications, prioritising speed or accuracy to produce the desired output.
 
 This work identified a number of uncertainties that can be the focus of future work.
-These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias within the participants' minds, or whether there is a more complex underlying reason for the behaviour.
+These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
 Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.

### 2019-11-26 paper.tex
Added figures, fixed Iain's name

@@
 \author{%
-  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchirst\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
+  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchrist\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
   \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
@@
 That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
-However, this trend is almost wholly reversed in the time-to-target results from the Fitts's model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
-Since the Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
-However, the Fitts's model does not account for changing stimuli and different strategies.
+However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
+Since Fitts's' model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
+However, the Fitts model does not account for changing stimuli and different strategies.
 We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
 This seems to indicate a speed/accuracy trade-off in finding the targets.
-With the Fitts's model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
+With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
 

### 2019-12-11 frontpage.tex
Modifying template for submission, greg's revisions

\documentclass{hcij_article}

\begin{document}

\articletitle{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}

\authorlist{%
  Jacobus C. Lock\textsuperscript{1}, Iain D. Gilchrist\textsuperscript{2}, Grzegorz Cielniak\textsuperscript{1} and Nicola Bellotto\textsuperscript{1}%
}

\affiliationlist{\textsuperscript{1}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{2}University of Bristol, Bristol, BS8 1TH, UK%
}

\titleauthorminibios

\miniauthorbio{Jacobus C. Lock}{jaycee.lock@gmail.com}{jclock.co.uk}{is a research assistant and PhD student at the University of Lincoln. His research interests are on intelligent systems and mobile computing.}

\miniauthorbio{Iain D. Gilchrist}{i.d.gilchrist@bristol.ac.uk}{}{is a professor at the University of Bristol's School of Psychological Science. His major academic focus is on how humans gather information about their visual environment, in particular how and why our eyes move to sample the world.}

\miniauthorbio{Grzegorz Cielniak}{gcielniak@lincoln.ac.uk}{}{is an associated professor at the University of Lincoln's School of Computer Science. His research interests include mobile robotics, machine perception, AI and in particular applications in agricultural robotics and food technology.}

\miniauthorbio{Nicola Bellotto}{nbellotto@lincoln.ac.uk}{}{is an associated professor at the University of Lincoln's School of Computer Science. His research focus is on machine perception of humans for robotics and intelligent systems, from low-level detection and tracking, to high-level behaviour understanding and reasoning.}

\titlenotes

%\titlebackground{This article is based on...}
\titlefunding{This project is partly funded and supported by the Google Winter Award (2016).}
%\titlesupplementarydata{Supplemental data can be found...}

\titlehcieditorialrecord{First received on \emph{date}. Revisions received on \emph{date}, \emph{date}, and \emph{date}. Accepted by \emph{action-editor-name}. Final manuscript received on \emph{date}.}

\end{document}

### 2019-12-11 paper.tex
Modifying template for submission, greg's revisions

@@
-\documentclass[]{interact}
+\documentclass{hcij_article}
 
@@
 \usepackage{multirow}
-\usepackage[natbibapa,nodoi]{apacite}
-\usepackage{todonotes}
-
-\setlength\bibhang{12pt}
-\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}
+\usepackage{array}
+\usepackage{natbib}
 
@@
 
-\articletype{Review Draft}
+\articletitle{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
 
-\title{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
-
-\author{%
-  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchrist\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
-  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
-}
-
-\maketitle
-
-\begin{abstract}
+\articleabstract{
   Sound perception is a fundamental skill for many people with severe sight impairments.
@@
   We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
-  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
-\end{abstract}
+  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
+}
 
-\begin{keywords}
-  Visual impairment; active vision; guidance system; audio interface; Fitts Law
-\end{keywords}
+\newpage
+
+\thickhrrule
+
+\tableofcontents
+
+\thickhrrule
+
+%\begin{keywords}
+%  Visual impairment; active vision; guidance system; audio interface; Fitts Law
+%\end{keywords}
+
+\articlebodystart
 
@@
 The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
-Improvements to computer vision and machine learning techniques, as well as mobile computing hardware improvements are exploited to make this system possible.
+Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
 In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
-However, in literature, these techniques are typically limited to electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
-In previous work we implemented a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to humans as well~\citep{lock2019active}.
+However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
+In previous work we developed a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to direct humans' attention as well.%~\citep{lock2019active}.
 
@@
 It also provides access to Android's full range of interface tools and I/O options. 
-Furthermore, a set of bone-conduction headphones (pictured in \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
+Furthermore, a set of bone-conduction headphones (see \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
 
@@
   \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
-  \caption{Pictures of the former Tango tablet and the bone-conduction headphones used in this work (left), and a participant with visual impairments during an experiment (right).}
+  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
 \end{figure}
@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones~\citep{lock2019bone,macdonald2006spatial} and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.% ~\citep{lock2019bone,macdonald2006spatial}
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
@@
 The main contributions of this paper are two-fold: 
-
 \begin{itemize}
-  \item we provide more comprehensive experimental results on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with bone-conducting headsets; 
+  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with a bone-conducting headset;
   \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
@@
 
-The rest of the paper starts by discussing previous relevant works and research in \Cref{sec:prev-work}, followed by a discussion on the design and implementation of our interface in \Cref{sec:system-description}.
+The rest of the paper starts by discussing previous relevant works and research in \Cref{sec:prev-work}, followed by a presentation of the design and implementation of our interface in \Cref{sec:system-description}.
 This is followed by a description of the experiments that were conducted and a discussion of their results in \Cref{sec:experiments} and \Cref{sec:results}.
-Finally, the paper concludes with a summary and a short discussion on future research prospects in \Cref{sec:conclusion}.
+Finally, the paper concludes with a summary and discussions on future research prospects in \Cref{sec:conclusion}.
 
@@
 ~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
-We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
+We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area.%~\citep{lock2019bone}.
 We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
 
-Researchers have previously used Fitts's Law~\citep{fitts1954information}, and more recently MacKenzie's modified version of it~\citep{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
+Fitts's Law~\citep{fitts1954information} is a predictive model of human movement and is particularly useful to evaluate human-computer interactions.
+Indeed, researchers have previously used Fitts's Law, and more recently MacKenzie's modified version of it~\citep{mackenzie1992fitts}, as a metric to evaluate the performance of a spatial audio HMI\@.
 Fitts's Law was originally proposed for visual target search tasks, but has since been applied in non-visual target search tasks as well.
@@
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
-To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
+To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localise itself in real-time.
+%To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
 This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
@@
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\citep{lichtenstein2012headphone}.
+This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\cite{lichtenstein2012headphone}.
 Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
@@
 Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
-However, given the complicated process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.
+However, given the complex process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.
 
@@
 The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
-For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume.
+For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume compared to the left ear.
 
@@
 The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
-After practical tests with the interface, we set the neutral pitch to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
-%We set the pitch limits to two octaves away from the neutral pitch, giving frequency limits of [\SI{128}{\hertz}, \SI{2048}{\hertz}].
 
@@
 We performed a set of experiments with the audio interface to determine how effective it is at directing a user to adjust the pan and elevation angles of a camera for point it to a target.
-Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics.
+Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics in order to determine their perception limits in the respective audio dimensions.
 The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
@@
   \centering
-  \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
+  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
   \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
@@
   \centering
-  \includegraphics[width=1.0\textwidth]{figures/sound_localisation.png}
+  \includegraphics[width=0.8\columnwidth]{figures/sound_localisation.png}
   \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }\label{fig:sound-localisation}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/pitch_discrimination.png}
+  \includegraphics[width=0.8\columnwidth]{figures/pitch_discrimination.png}
   \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/pitch_thresholds.png}
+  \includegraphics[width=0.8\columnwidth]{figures/pitch_thresholds.png}
   \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/pitch_thresholds_limits.png}
+  \includegraphics[width=0.8\columnwidth]{figures/pitch_thresholds_limits.png}
   \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/boxplot_target_search_median_error.png}
+  \includegraphics[width=0.6\textwidth]{figures/boxplot_target_search_median_error.png}
   \caption{Box-plots of the median pan and elevation errors for each audio setting. }\label{fig:target-boxplot-error}
@@
   \caption{The average target acquisition error in the pan and elevation dimensions for each participant group. }\label{tab:target-results}
-  \begin{tabular}{p{0.5cm}p{1.5cm}p{1.5cm}p{3.0cm}p{3.0cm}p{3.0cm}}
+	\begin{tabular}%
+	{>{\centering\arraybackslash}p{0.5cm}%
+	 >{\centering\arraybackslash}p{1.5cm}%
+	 >{\centering\arraybackslash}p{1.1cm}%
+ 	 >{\raggedleft\arraybackslash}p{2.6cm}%
+ 	 >{\raggedleft\arraybackslash}p{3.0cm}%
+	 >{\raggedleft\arraybackslash}p{3.0cm}}
     \toprule
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
+  \includegraphics[width=0.6\textwidth]{figures/boxplot_target_search_absolute_median_error.png}
   \caption{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-boxplot-absolute-errors}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{figures/fitts_ips.png}
+  \includegraphics[width=0.6\textwidth]{figures/fitts_ips.png}
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
@@
 However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
-Since Fitts's' model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
+Since Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
 However, the Fitts model does not account for changing stimuli and different strategies.
@@
 
-\section*{Acknowledgements}
+\articlebodyend
 
-This project is partly funded and supported by the Google Winter Award (2016).
-
+\begingroup
+\raggedright
+\titleformat*{\section}{\bfseries\Large\centering\MakeUppercase}
 \bibliographystyle{apacite}
 \bibliography{bib}
+\endgroup
 

### 2019-12-11 paper.tex
Review and submitted!

@@
 
-\articletitle{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
+\articletitle{Experimental Analysis of a Spatialized Audio Interface for People with Visual Impairments}
 
@@
   Sound perception is a fundamental skill for many people with severe sight impairments.
-  The research presented in this paper is part of the ActiVis project, the aim of which is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
+  The research presented in this paper is part of an ongoing project, the aim of which is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
   This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
-  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
-  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
+  It has been implemented and tested with spatialized audio cues, which convey the direction of a predefined target in 3D space.
+  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyze the pros and cons of our design choices.
   In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
@@
 
-The ActiVis\footnote{https://lcas.github.io/ActiVis/} project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
+This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
 Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
-In particular, techniques from the active vision field are being used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
+In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
 However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
@@
 
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
+The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a color camera and provides access to powerful real-time localization (through IMU measurements and landmark tracking) and image-processing facilities.
 It also provides access to Android's full range of interface tools and I/O options. 
@@
 Humans are naturally able to determine the 3D position of a sound source and by exploiting this ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
-A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
+A sound source can be spatialized by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
 In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.% ~\citep{lock2019bone,macdonald2006spatial}
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialized signals used with expensive closed-cup headphones and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behavior of the pitch affects target acquisition performance in terms of time and angular error.% ~\citep{lock2019bone,macdonald2006spatial}
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
@@
 Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
+Following this, researchers have investigated using audio signals that are spatialized with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+The authors generally report favorable results for this guidance approach when used with standard over-ear headphones or speakers. 
 However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+Cheaper headphones and bone-conduction headphones generally report unfavorable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
 This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favorable results. 
 We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area.%~\citep{lock2019bone}.
-We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
+We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behavior can impact that performance.
 
@@
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
-To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localise itself in real-time.
+To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
 %To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
@@
 
-Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
+Humans localize a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
 Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
-When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
+When the modified audio signal enters the inner ear canal, the human brain is able to analyze the frequency response and accurately determine the position of the sound source on the median plane. 
 The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.
@@
 The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \Cref{fig:cam-coords}.
-Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
-However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
+Spatialized audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
+However, given the previously discussed limitations of bone-conduction and spatialized audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
 The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
@@
 
-The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
+The human audition system uses binaural comparison cues, such as ITD and ILD, to localize a sound source on the horizontal plane~\citep{blauert1969sound}.
 The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
@@
 In this work, a pure sinusoidal wave was used. 
-People typically have trouble localising a pure tone without a sufficiently rich spectral signature.
+People typically have trouble localizing a pure tone without a sufficiently rich spectral signature.
 However, the ITD and ILD are independent of the tone's spectral make-up, while the elevation angle is given through a different mechanism.
 Therefore, a pure sine wave is suitable to convey the target's pan angle.
-To transform and spatialise the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
+To transform and spatialize the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
 
@@
 Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics in order to determine their perception limits in the respective audio dimensions.
-The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
-We also tested the system with a group of severely sight impaired participants and compared their data to the blindfolded dataset.
-The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
+The participants were given time before the experiments commenced to familiarize themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
+We also tested the system with a group of participants with severe sight impairments and compared their data to the blindfolded participant dataset.
+The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimize the behavior of the feedback modes in our portable navigation aid.
 
@@
 
-\subsection{Participant Characterisation}\label{sec:participant_characterisation}
+\subsection{Participant Characterization}\label{sec:participant_characterisation}
 
-A preliminary set of experiments were conducted to characterise the participants' hearing characteristics.
-The measured characteristics were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
+A preliminary set of experiments were conducted to characterize the participants' hearing characteristics.
+The measured characteristics were each participant's audio localization ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
 These results will be used to provide context to the following target search experiment and provide additional insight on any possible biases or limitations.
 
-\subsubsection{Sound Localisation}\label{sec:sound_localisation}
+\subsubsection{Sound Localization}\label{sec:sound_localisation}
 
 In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
-To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
+To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialize and place its source to the participant's left or right.
 The participant then had to select the direction the sound came from.
-The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly harder to localise.
+The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly harder to localize.
 
@@
 For example, the experiment will terminate when one sequence is set to \SI{11.25}{\degree} and the other is between \SI{2.8}{\degree} or \SI{45}{\degree} for three consecutive guesses.
-This gives a distance band where the participant is capable of localising the sound source.
+This gives a distance band where the participant is capable of localizing the sound source.
 Each participant performed this experiment three times.
@@
 The tone difference depends on how well the participant can tell the tones apart.
-Like the sound localisation experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
+Like the sound localization experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
 Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
@@
 When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
-The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
+The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localization API.\
 A total of 28 targets were generated per participant.
 
-As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\Cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
+As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualized in~\Cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
 Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively, giving pitch intervals of
@@
 
-Here we briefly summarise the equations and quantities involved in our metric.
+Here we briefly summarize the equations and quantities involved in our metric.
 Fitts's Law is given by
@@
 \noindent
-Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\citep{welford1968fundamentals}, given by
+Here $\theta$ is the angular distance between subsequent target centers and $w_e$ is the targets' effective angular width~\citep{welford1968fundamentals}, given by
 
@@
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
-Each participant performed three sets of experiments each, with the two characterisation experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
-Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
-Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
+Each participant performed three sets of experiments each, with the two characterization experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
+Both groups were given some time before the target-search experiment to familiarize themselves with the system, the audio signal's behavior and the \SI{512}{\hertz} on-level tone. 
+Furthermore, to minimize any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
 
@@
 
-\subsection{Characterisation of Sound Localisation}
+\subsection{Characterization of Sound Localization}
 
-\Cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from. 
-%
+\Cref{fig:sound-localisation} shows the results captured from the sound localization experiment where the participants had to select the direction (left or right) that the tone was being played from. 
 It can be seen that the vast majority of guesses for both groups were correct.
-For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
+For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behavior.
 This indicates that the participants in \textit{G1} consistently progressed through the distance intervals and we can therefore conclude they had little difficulty determining sound direction.
@@
 These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy.
-These results are in line previous literature, confirming that humans are very adept at localising a sound source, particularly in the pan dimension.
+These results are in line previous literature, confirming that humans are very adept at localizing a sound source, particularly in the pan dimension.
 
-\subsection{Characterisation of Pitch Discrimination}
+\subsection{Characterization of Pitch Discrimination}
 
@@
 A set of box-plots of the angle errors are also given in \Cref{fig:target-boxplot-error} for each audio setting.
-The results are summarised in \Cref{tab:target-results}.
+The results are summarized in \Cref{tab:target-results}.
 
@@
 
-Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \Cref{tab:inter-group-results}).
+Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarized in \Cref{tab:inter-group-results}).
 This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
@@
 These results allows us to calculate and plot in \Cref{fig:fitts-ips} an index of performance, as given by \Cref{eq:fitts-performance}, for each audio setting.
-The results are summarised in \Cref{tab:fitts-results}.
+The results are summarized in \Cref{tab:fitts-results}.
 For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
@@
 However, the Fitts model does not account for changing stimuli and different strategies.
-We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
+We therefore hypothesize that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
 This seems to indicate a speed/accuracy trade-off in finding the targets.
-With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
+With the Fitts model discussed here, we can modify the interface to prioritize different metrics and produce the correct output.
 
@@
 
-In this paper we investigated the use of spatialised audio interface with varying pitch to guide a visually impaired user in a target pointing task.
-We found that the blindfolded participants and those with severe sight impairments performed similarly in localising sound sources and differentiating between tones. 
+In this paper we investigated the use of spatialized audio interface with varying pitch to guide a user with visual impairments in a target pointing task.
+We found that the blindfolded participants and those with severe sight impairments performed similarly in localizing sound sources and differentiating between tones. 
 We also found that both groups were able to find a randomly distributed set of virtual targets with similar levels of accuracy.
 However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
-We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
+We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialized cues, is independent of such settings.
 Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.\ more time to reach the target).
@@
 This work identified a number of uncertainties that can be the focus of future work.
-These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
+These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behavior.
 Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.

### 2020-01-02 paper.tex
Update figures
Editing to ACM format

@@
-\documentclass{hcij_article}
+\documentclass[acmsmall]{acmart}
 
@@
 
+\citestyle{acmauthoryear}
+
 \begin{document}
 
-\articletitle{Experimental Analysis of a Spatialized Audio Interface for People with Visual Impairments}
+\title{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
 
-\articleabstract{
+\author{Jacobus C. Lock}
+\authornote{Contact Author}
+\email{jaycee.lock@gmail.com}
+\affiliation{%
+  \institution{University of Lincoln}
+  \streetaddress{Brayford Pool}
+  \city{Lincoln}
+  \country{UK}
+  \postcode{LN6 7TS}
+}
+
+\author{Iain D. Gilchrist}
+\affiliation{%
+  \institution{University of Bristol}
+  \city{Bristol}
+  \country{UK}
+}
+
+\author{Grzegorz Cielniak}
+\affiliation{%
+  \institution{University of Lincoln}
+  \city{Lincoln}
+  \country{UK}
+}
+
+\author{Nicola Bellotto}
+\affiliation{%
+  \institution{University of Lincoln}
+  \city{Lincoln}
+  \country{UK}
+}
+
+\begin{abstract}
   Sound perception is a fundamental skill for many people with severe sight impairments.
@@
   This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
-  It has been implemented and tested with spatialized audio cues, which convey the direction of a predefined target in 3D space.
-  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyze the pros and cons of our design choices.
+  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
+  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
   In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
+\end{abstract}
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10003120.10011738.10011773</concept_id>
+<concept_desc>Human-centered computing~Empirical studies in accessibility</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10003120.10003121.10003126</concept_id>
+<concept_desc>Human-centered computing~HCI theory, concepts and models</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10003120.10011738.10011775</concept_id>
+<concept_desc>Human-centered computing~Accessibility technologies</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Human-centered computing~Empirical studies in accessibility}
+\ccsdesc[300]{Human-centered computing~HCI theory, concepts and models}
+\ccsdesc[300]{Human-centered computing~Accessibility technologies}
+
+\keywords{%
+  Visual impairment; active vision; guidance system; audio interface; Fitts Law
 }
 
-\newpage
-
-\thickhrrule
-
-\tableofcontents
-
-\thickhrrule
-
-%\begin{keywords}
-%  Visual impairment; active vision; guidance system; audio interface; Fitts Law
-%\end{keywords}
-
-\articlebodystart
+\maketitle
 
@@
 However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
-In previous work we developed a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to direct humans' attention as well.%~\citep{lock2019active}.
+In previous work we developed a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to direct humans' attention as well\citep{lock2019active}.
 
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a color camera and provides access to powerful real-time localization (through IMU measurements and landmark tracking) and image-processing facilities.
+The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localization (through IMU measurements and landmark tracking) and image-processing facilities.
 It also provides access to Android's full range of interface tools and I/O options. 
@@
 Humans are naturally able to determine the 3D position of a sound source and by exploiting this ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
-A sound source can be spatialized by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
+A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
 In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialized signals used with expensive closed-cup headphones and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behavior of the pitch affects target acquisition performance in terms of time and angular error.% ~\citep{lock2019bone,macdonald2006spatial}
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error~\citep{lock2019bone,macdonald2006spatial}.
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.
@@
 Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-Following this, researchers have investigated using audio signals that are spatialized with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-The authors generally report favorable results for this guidance approach when used with standard over-ear headphones or speakers. 
+Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
 However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-Cheaper headphones and bone-conduction headphones generally report unfavorable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
 This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favorable results. 
-We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area.%~\citep{lock2019bone}.
-We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behavior can impact that performance.
+~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
+We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
 
@@
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
-To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
-%To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
+%To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
+To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
 This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
@@
 Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
-When the modified audio signal enters the inner ear canal, the human brain is able to analyze the frequency response and accurately determine the position of the sound source on the median plane. 
+When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
 The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.
@@
 The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \Cref{fig:cam-coords}.
-Spatialized audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
-However, given the previously discussed limitations of bone-conduction and spatialized audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
+Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
+However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
 The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
@@
 Therefore, a pure sine wave is suitable to convey the target's pan angle.
-To transform and spatialize the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
+To transform and spatialise the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
 
@@
 We also tested the system with a group of participants with severe sight impairments and compared their data to the blindfolded participant dataset.
-The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimize the behavior of the feedback modes in our portable navigation aid.
+The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimize the behaviour of the feedback modes in our portable navigation aid.
 
@@
 When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
-The audio generator then produces a tone based on the difference between the device and the target's positions. The tone is sent to the audio output channel, which plays it back to the user.
+The audio generator then produces a tone based on the difference between the device and the target's positions.
+The tone is sent to the audio output channel, which plays it back to the user.
 A WiFi recording module is constantly monitoring the different values of the device's parameters and of the target's position, as well as the system's output, recording everything in a remotely stored datafile.
@@
 In this experiment, we evaluated a participant's ability to determine the lateral direction a sound is coming from.
-To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialize and place its source to the participant's left or right.
+To do this, we played a continuous \SI{512}{\hertz} sinusoidal tone to the participant through the headphones and applied an HRTF to spatialise and place its source to the participant's left or right.
 The participant then had to select the direction the sound came from.
@@
 \noindent
-Here $\theta$ is the angular distance between subsequent target centers and $w_e$ is the targets' effective angular width~\citep{welford1968fundamentals}, given by
+Here $\theta$ is the angular distance between subsequent target centres and $w_e$ is the targets' effective angular width~\citep{welford1968fundamentals}, given by
 
@@
 
-% \noindent
-% where $IP = \frac{1}{t}$ when $\sigma=0$.% When sigma=0, then ID=log2(0/we + 1) = log2(1) = 0
-
 \subsection{Procedure}
@@
 Each participant performed three sets of experiments each, with the two characterization experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
-Both groups were given some time before the target-search experiment to familiarize themselves with the system, the audio signal's behavior and the \SI{512}{\hertz} on-level tone. 
+Both groups were given some time before the target-search experiment to familiarize themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
 Furthermore, to minimize any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
@@
 It can be seen that the vast majority of guesses for both groups were correct.
-For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behavior.
+For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
 This indicates that the participants in \textit{G1} consistently progressed through the distance intervals and we can therefore conclude they had little difficulty determining sound direction.
@@
 
-In this paper we investigated the use of spatialized audio interface with varying pitch to guide a user with visual impairments in a target pointing task.
+In this paper we investigated the use of spatialised audio interface with varying pitch to guide a user with visual impairments in a target pointing task.
 We found that the blindfolded participants and those with severe sight impairments performed similarly in localizing sound sources and differentiating between tones. 
@@
 However, the blindfolded group outperformed the one with severe sight impairments in terms of time-to-target. 
-We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialized cues, is independent of such settings.
+We further tested different pitch settings and found that the user performance in the pan dimension, based on spatialised cues, is independent of such settings.
 Moreover, we noticed a speed/accuracy trade-off between the settings, where a higher pitch setting produces a smaller angular error, but at the cost of reducing the time performance (i.e.\ more time to reach the target).
@@
 This work identified a number of uncertainties that can be the focus of future work.
-These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behavior.
+These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
 Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.
@@
 
-\articlebodyend
-
-\begingroup
-\raggedright
-\titleformat*{\section}{\bfseries\Large\centering\MakeUppercase}
-\bibliographystyle{apacite}
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{bib}
-\endgroup
 

### 2020-01-02 paper.tex
Added description

@@
   \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
+  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
 \end{figure}
@@
 }
+  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle.
+Note the logarithmic scale of the frequency axis.
+}
 \end{figure}
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
+  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
 \end{figure}
@@
   \caption{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }\label{fig:sound-localisation}
+  \Description{Histograms of the participants' guesses of the tone locations that show the correct and incorrect guesses for each bin. }
 \end{figure}
@@
   \caption{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }\label{fig:pitch-discrimination}
+  \Description{Histograms of the participants' guesses of which tone was higher pitched that show the correct and incorrect guesses for each bin. }
 \end{figure}
@@
   \caption{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }\label{fig:pitch-thresholds}
+  \Description{Distributions of the median cut-off frequency thresholds along with the median 75\% cut-off thresholds. }
 \end{figure}
@@
   \caption{Histogram distributions of the participants' 75\% cut-off thresholds. }\label{fig:pitch-thresholds-hist}
+  \Description{Histogram distributions of the participants' 75\% cut-off thresholds. }
 \end{figure}
@@
   \caption{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-errors}
+  \Description{Distributions of the angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
 \end{figure}
@@
   \caption{Box-plots of the median pan and elevation errors for each audio setting. }\label{fig:target-boxplot-error}
+  \Description{Box-plots of the median pan and elevation errors for each audio setting. }
 \end{figure}
@@
   \caption{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }\label{fig:target-boxplot-absolute-errors}
+  \Description{Distributions of the absolute angular errors in the pan and elevation dimensions for the 3 different pitch gradient settings. }
 \end{figure}
@@
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-results}
+  \Description{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
 \end{figure}
@@
   \caption{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }\label{fig:fitts-ips}
+  \Description{Plots showing the Fitts relationship between the time it took the participants to find a target and the target's index of difficulty. }
 \end{figure}

### 2020-01-03 paper.tex
Fixed American spelling, added CSS classes:

@@
 <concept>
-<concept_id>10003120.10011738.10011773</concept_id>
-<concept_desc>Human-centered computing~Empirical studies in accessibility</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
 <concept_id>10003120.10003121.10003126</concept_id>
@@
 <concept>
-<concept_id>10003120.10011738.10011775</concept_id>
-<concept_desc>Human-centered computing~Accessibility technologies</concept_desc>
+<concept_id>10003120.10003121.10003122.10011749</concept_id>
+<concept_desc>Human-centered computing~Laboratory experiments</concept_desc>
 <concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10003120.10003121.10003125.10010597</concept_id>
+<concept_desc>Human-centered computing~Sound-based input / output</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10003120.10003121.10003125.10010873</concept_id>
+<concept_desc>Human-centered computing~Pointing devices</concept_desc>
+<concept_significance>100</concept_significance>
+</concept>
+<concept>
+<concept_id>10003120.10011738.10011773</concept_id>
+<concept_desc>Human-centered computing~Empirical studies in accessibility</concept_desc>
+<concept_significance>500</concept_significance>
 </concept>
@@
 
+\ccsdesc[100]{Human-centered computing~HCI theory, concepts and models}
+\ccsdesc[300]{Human-centered computing~Laboratory experiments}
+\ccsdesc[500]{Human-centered computing~Sound-based input / output}
+\ccsdesc[100]{Human-centered computing~Pointing devices}
 \ccsdesc[500]{Human-centered computing~Empirical studies in accessibility}
-\ccsdesc[300]{Human-centered computing~HCI theory, concepts and models}
-\ccsdesc[300]{Human-centered computing~Accessibility technologies}
 
@@
 ~
-  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
+  \subfloat[]{\label{fig:participant}\includegraphics[width=0.25\columnwidth]{figures/vi_participant.pdf}}
   \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
@@
 
-Humans localize a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
+Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
@@
 
-The human audition system uses binaural comparison cues, such as ITD and ILD, to localize a sound source on the horizontal plane~\citep{blauert1969sound}.
+The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
 The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
@@
 Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics in order to determine their perception limits in the respective audio dimensions.
-The participants were given time before the experiments commenced to familiarize themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
+The participants were given time before the experiments commenced to familiarise themselves with the device and the tones it emits, as well as what the `on-target' tone sounds like.
 We also tested the system with a group of participants with severe sight impairments and compared their data to the blindfolded participant dataset.
-The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimize the behaviour of the feedback modes in our portable navigation aid.
+The results from the experiments we performed allow us to better understand how the users respond to different settings for the spatial audio feedback stimulus and use them to improve and optimise the behaviour of the feedback modes in our portable navigation aid.
 
@@
 
-A preliminary set of experiments were conducted to characterize the participants' hearing characteristics.
+A preliminary set of experiments were conducted to characterise the participants' hearing characteristics.
 The measured characteristics were each participant's audio localization ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
@@
 The participant then had to select the direction the sound came from.
-The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly harder to localize.
+The longer the experiment lasts and the more correct guesses the participant makes, the closer the source moves to the centre-front of the participant, making it increasingly harder to localise.
 
@@
 
-As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualized in~\Cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
+As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\Cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
 Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively, giving pitch intervals of
@@
 
-Here we briefly summarize the equations and quantities involved in our metric.
+Here we briefly summarise the equations and quantities involved in our metric.
 Fitts's Law is given by
@@
 Each participant performed three sets of experiments each, with the two characterization experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
-Both groups were given some time before the target-search experiment to familiarize themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
-Furthermore, to minimize any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
+Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
+Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
 
@@
 A set of box-plots of the angle errors are also given in \Cref{fig:target-boxplot-error} for each audio setting.
-The results are summarized in \Cref{tab:target-results}.
+The results are summarised in \Cref{tab:target-results}.
 
@@
 
-Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarized in \Cref{tab:inter-group-results}).
+Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \Cref{tab:inter-group-results}).
 This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
@@
 These results allows us to calculate and plot in \Cref{fig:fitts-ips} an index of performance, as given by \Cref{eq:fitts-performance}, for each audio setting.
-The results are summarized in \Cref{tab:fitts-results}.
+The results are summarised in \Cref{tab:fitts-results}.
 For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
@@
 This seems to indicate a speed/accuracy trade-off in finding the targets.
-With the Fitts model discussed here, we can modify the interface to prioritize different metrics and produce the correct output.
+With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
 

### 2020-01-03 paper.tex
Added compliance sentence to intro

@@
 ~
-  \subfloat[]{\label{fig:participant}\includegraphics[width=0.25\columnwidth]{figures/vi_participant.pdf}}
+  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
   \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
@@
 However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
-In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones and we expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error~\citep{lock2019bone,macdonald2006spatial}.
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
+These results were presented at the 9th International Workshop on Assistive Engineering~\cite{lock2019bone}.
+We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
 The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

### 2020-01-17 paper.tex
Updated intro

@@
 
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localization (through IMU measurements and landmark tracking) and image-processing facilities.
+The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
 It also provides access to Android's full range of interface tools and I/O options. 
@@
   \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
-  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
+  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right)~\citep{lock2019bone}.}
   \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
@@
 
-Humans are naturally able to determine the 3D position of a sound source and by exploiting this ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
-A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
-In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
-However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
+This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load tot he user, given humans' natural ability to determine a sound source 3D positions.
+By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
+In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
+However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted, since they are placed on the user's cheekbones and bypass the ears outer structure.
+We bypass this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
 In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
-These results were presented at the 9th International Workshop on Assistive Engineering~\cite{lock2019bone}.
+These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
 We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
@@
 This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+~\citet{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
 We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
@@
 %To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
-To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
+To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
 This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
 
-A set of bone-conduction headphones is used as the audio transmission medium.
+A set of bone-conduction headphones is used as the audio transmission medium~\citep{lock2019bone}.
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\cite{lichtenstein2012headphone}.
+This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\citep{lichtenstein2012headphone}.
 Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
@@
 
-Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
+Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound,lock2019bone}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
@@
   \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
-Note the logarithmic scale of the frequency axis.
+Note the logarithmic scale of the frequency axis~\citep{lock2019bone}.
 }
@@
 
-The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
+The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound,lock2019bone}.
 The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
@@
 
-A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison}.
+A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison,lock2019bone}.
 To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
-  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}. }\label{fig:pipeline}
+  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
 \end{figure}
 
-\subsection{Participant Characterization}\label{sec:participant_characterisation}
+\subsection{Participant Characterisation}\label{sec:participant_characterisation}
 
 A preliminary set of experiments were conducted to characterise the participants' hearing characteristics.
-The measured characteristics were each participant's audio localization ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
+The measured characteristics were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
 These results will be used to provide context to the following target search experiment and provide additional insight on any possible biases or limitations.
 
-\subsubsection{Sound Localization}\label{sec:sound_localisation}
+\subsubsection{Sound Localisation}\label{sec:sound_localisation}
 
@@
 The tone difference depends on how well the participant can tell the tones apart.
-Like the sound localization experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
+Like the sound localisation experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
 Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
@@
 When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
-The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localization API.\
+The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
 A total of 28 targets were generated per participant.
@@
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
-Each participant performed three sets of experiments each, with the two characterization experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
+Each participant performed three sets of experiments each, with the two characterisation experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
 Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
@@
 
-\subsection{Characterization of Sound Localization}
+\subsection{Characterisation of Sound Localisation}
 
-\Cref{fig:sound-localisation} shows the results captured from the sound localization experiment where the participants had to select the direction (left or right) that the tone was being played from. 
+\Cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from. 
 It can be seen that the vast majority of guesses for both groups were correct.
@@
 
-\subsection{Characterization of Pitch Discrimination}
+\subsection{Characterisation of Pitch Discrimination}
 
@@
 For example, the pitch gradient can be automatically adjusted over time by the device to provide a better match between the human and computer and increase overall target-finding performance.
-Indeed, the work by~\cite{gallina2015progressive} may serve as a good guideline for such a system.
+Indeed, the work by~\citet{gallina2015progressive} may serve as a good guideline for such a system.
 Additional feedback modes may also be added to allow for clearer guidance experience for the user, e.g.\ vibration signals to inform them when they point to the target or adjusting the volume to expand the system to three dimensions.

### 2020-01-17 paper.tex
More minor changes to reduce plagiarism

@@
 \usepackage{natbib}
+\usepackage{todonotes}
 
@@
 
+\todo{edit start}
 This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load tot he user, given humans' natural ability to determine a sound source 3D positions.
@@
 In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
-However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted, since they are placed on the user's cheekbones and bypass the ears outer structure.
-We bypass this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
+However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
+We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
+\todo{edit stop}
 In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
@@
 
+\todo{edit start}
 Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
@@
 Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
+\todo{edit stop}
 
@@
 However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
-The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}.
+This interface was implemented and evaluated in previous work~\citep{lock2019bone}.
 
@@
 
+\subsection{Participant Feedback}
+
+\todo{include subjective feedback?}
+
 \subsection{Discussion}

### 2020-01-20 paper.tex
Rewrote some sections to avoid plagiarism

@@
   Sound perception is a fundamental skill for many people with severe sight impairments.
-  The research presented in this paper is part of an ongoing project, the aim of which is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
+  The research presented in this paper is part of an ongoing project, the aim of which is to build a mobile guidance aid to assist people with vision impairments find objects within an unknown indoor environment.
   This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
@@
 
-This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the last leg of their journey (the so-called `last 10-yard problem').
+This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the final part of their journey, addressing the so-called `last 10-yard problem'.
 Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
@@
 However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
-In previous work we developed a prototype system that uses active vision and machine learning models to gather information and help a person find objects in an unknown environment, showing that these techniques can indeed successfully be applied to direct humans' attention as well\citep{lock2019active}.
+In previous work we developed a prototype system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention as well\citep{lock2019active}.
 
-The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
-It also provides access to Android's full range of interface tools and I/O options. 
-Furthermore, a set of bone-conduction headphones (see \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
+\todo{edit start}
+The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones.
+Both these devices are shown in \cref{fig:tango-headphone}.
+This a Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
+It also gives access to Android's full range of interface and I/O options.
+Bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
+These headphones have the benefit of not interfering with a user's normal hearing function.
+\todo{edit end}
+
+%The prototype is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
+%It also provides access to Android's full range of interface tools and I/O options. 
+%Furthermore, a set of bone-conduction headphones (see \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
 
@@
 \todo{edit start}
-This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load tot he user, given humans' natural ability to determine a sound source 3D positions.
+This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source 3D positions.
 By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
@@
 
-The rest of the paper starts by discussing previous relevant works and research in \Cref{sec:prev-work}, followed by a presentation of the design and implementation of our interface in \Cref{sec:system-description}.
-This is followed by a description of the experiments that were conducted and a discussion of their results in \Cref{sec:experiments} and \Cref{sec:results}.
-Finally, the paper concludes with a summary and discussions on future research prospects in \Cref{sec:conclusion}.
+The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a presentation of the design and implementation of our interface in \cref{sec:system-description}.
+This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiments} and \cref{sec:results}.
+Finally, the paper concludes with a summary and discussions on future research prospects in \cref{sec:conclusion}.
 
@@
 
-\todo{edit start}
-Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
-The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
-In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
-However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
-Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
+Over multiple years, both commercial and academic parties have devices new and innovative mobile navigation and travel aids for people with visual impairments.
+Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
+Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
+However, from an ergonomic perspective, haptic feedback is a weak performer and require significant additional external hardware to transmit guidance instructions with significant resolution.
+Furthermore, both haptic and vocal feedback can present a significant cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
 Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
-Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
-\todo{edit stop}
+As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
+However, such tones can potentially fatigue a user if the tone is too unpleasant.
+Researchers started using cameras and object detectors to determine what a user is looking at and using them together with simple audio tones and vocal feedback signals to indicate to the user where to find an object.
+They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
 
-Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
-However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
-This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-~\citet{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
-We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
-We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
+%\todo{edit start}
+%Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
+%The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
+%In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
+%However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
+%Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
+%Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
+%Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
+%\todo{edit stop}
+
+Work has been done in an attempt to add complexity to these tones by spatialising them with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
+The authors generally report favourable results when using snormal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+However, the audio transmission device used has a significant effect on performance.
+Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization}.
+However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
+Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as the work by~\citet{durette2008visuo}.
+We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}.
+We found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions comparable to those of more expensive and over-ear headphones.
+
+%Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
+%Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+%The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
+%However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
+%Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
+%This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
+%~\citet{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
+%We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
+%We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
 
@@
 
-A set of bone-conduction headphones is used as the audio transmission medium~\citep{lock2019bone}.
+A set of bone-conduction headphones is used as the audio transmission medium.
 These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
@@
 Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
-The AfterShockz headphones (\Cref{fig:tango-headphone}) were ultimately selected for the aforementioned reasons of non-interference and increased discretion when compared to larger over-ear headphones.
+The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected for the aforementioned reasons of non-interference and increased discretion when compared to larger over-ear headphones.
 
@@
 
-The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \Cref{fig:cam-coords}.
+The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
 Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
@@
 
-The pitch is changed as a linear function of the elevation angle (see \Cref{fig:pitch-gain}) and the gradient is determined by setting the angle and pitch limits.
+The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}) and the gradient is determined by setting the angle and pitch limits.
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
@@
 
-A diagram of the experimental system pipeline is shown in~\Cref{fig:pipeline}, where the arrows indicate the direction of the information flow.
+A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of information flow.
+The system implementation used here is similar to the one used by~\citet{lock2019bone}.
 When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
@@
 
-To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
-The participants were given a Tango device running an app that implements the experimental setup in~\Cref{fig:pipeline}.
+A set of experiments were conducted to determine the interface's guidance effectiveness for a pointing task.
+These experiments captured the difference between the targets' actual directions and the directions the participants perceived them to be located. 
+The participants were given a Tango tablet running an app implementing the experimental setup in \cref{fig:pipeline}.
+This app generates a set of virtual targets, one at a time, and presents their directions to the participants with audio guidance signals.
+These targets are generated at a constant distance from the participants with pan and elevation angles that are uniformly distributed across the four quadrants to avoid clustering.
+Each target's relative angular position is communicated to the participants in real-time as the device is moved around via the bone-conducting headphones.
+Every time a participant was confident that they were pointing at a target, i.e.\ hearing a signal that is placed at their front at a frequency of \SI{512}{\hertz}, they tapped the device's screen, marking the location and generating a new target.
+The target's are all positioned relative to the device's camera coordinate system, which is tracked by the Tango hardware and localisation API.\
+Each participant was tasked with finding 28 targets each.
+
+%To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
+%The participants were given a Tango device running an app that implements the experimental setup in \cref{fig:pipeline}.
 The app generates a set of virtual targets and presents them to each participant through the audio interface, one at a time.
-The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
-Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
-When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
-The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
-A total of 28 targets were generated per participant.
+%The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
+%Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
+%When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
+%The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
+%A total of 28 targets were generated per participant.
 
-As part of this experiment, we wanted to see how changing the gradient of the pitch function, visualised in~\Cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
+This experimental setup was used in~\cite{lock2019bone}.
+However, in these experiments we also want to see how changing the gradient of the pitch function, visualised in \cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
 Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively, giving pitch intervals of
@@
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
-Each participant performed three sets of experiments each, with the two characterisation experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}.
+Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}.
 Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
@@
 
-\Cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from. 
+\cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from. 
 It can be seen that the vast majority of guesses for both groups were correct.
@@
 However, it also shows more errors in other distance intervals and a more even progression towards the centre.
-This could indicate that, instead of terminating the experiment as described in \Cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals.
+This could indicate that, instead of terminating the experiment as described in \cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals.
 
@@
 
-The results of the pitch discrimination experiment are shown in \Cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
+The results of the pitch discrimination experiment are shown in \cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
 For Group~\textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.
@@
 It can also be used to improve the interface's frequency profile and performance. 
-\Cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
-\Cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
+\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
+\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
 %The median is used for each grouping given the skewed plot and
@@
 
-The results from the target search experiment shown on the 2D histograms in \Cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other. 
-A set of box-plots of the angle errors are also given in \Cref{fig:target-boxplot-error} for each audio setting.
-The results are summarised in \Cref{tab:target-results}.
+The results from the target search experiment shown on the 2D histograms in \cref{fig:target-errors}, where the angular errors in the pan and elevation dimensions are plotted against each other. 
+A set of box-plots of the angle errors are also given in \cref{fig:target-boxplot-error} for each audio setting.
+The results are summarised in \cref{tab:target-results}.
 
@@
 Therefore, the Pearson test is used to investigate the correlation between the actual target location and participants' pointing location.
-These results are included in \Cref{tab:target-results}.
+These results are included in \cref{tab:target-results}.
 The Pearson correlation scores for Group~\text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.
@@
 The medians of these data groupings are then used as individual samples that represent an individual participant's performance for each setting.
-\Cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots, while \Cref{fig:target-boxplot-absolute-errors} shows the collection of absolute errors.
+\cref{fig:target-boxplot-error} shows these median data collected from each participant as a set of box-plots, while \cref{fig:target-boxplot-absolute-errors} shows the collection of absolute errors.
 
@@
 
-The box-plots in \Cref{fig:target-boxplot-error} show that the error in the pan dimension is approximately centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
+The box-plots in \cref{fig:target-boxplot-error} show that the error in the pan dimension is approximately centred around \SI{0}{\radian} for both groups, with some divergence between the groups for the different settings.
 However, using the Friedman test for repeated measures on the medians of absolute errors, these divergences are found to be not significant ($p_{G1} = 0.17,~p_{G2} = 0.09$), showing that spatial perception and accuracy are not affected by changes in the tone's pitch.
-This is further demonstrated in the box-plots in \Cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all three settings.
+This is further demonstrated in the box-plots in \cref{fig:target-boxplot-absolute-errors}, which demonstrates relatively consistent error levels in the pan dimension for both groups and across all three settings.
 
-Regarding the errors in the elevation dimension in \Cref{fig:target-boxplot-error}, we observe in Group~\textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings, respectively, and a median gradually approaching \SI{0}{\radian}.
+Regarding the errors in the elevation dimension in \cref{fig:target-boxplot-error}, we observe in Group~\textit{G1} a narrowing distribution between the \textit{lo}, \textit{med} and \textit{hi} settings, respectively, and a median gradually approaching \SI{0}{\radian}.
 A similar trend is observed for Group~\textit{G2}, but the improvement across the settings is more subtle and not as linear as for Group~\textit{G1}.
-\Cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the three settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
+\cref{fig:target-boxplot-absolute-errors} shows a clearer improvement, i.e.\ approaching \SI{0}{\radian}, for the elevation data between the three settings in both groups, with the \textit{hi} setting producing the smallest error in both cases.
 Further analysis of the medians of the absolute elevation error with the Friedman test reveals that the results for the different settings are significantly different from each other only for Group~\textit{G1} ($p_{G1} = 0.002,~p_{G2} = 0.32$).
@@
 
-Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \Cref{tab:inter-group-results}).
+Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
 This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
@@
 
-To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty, as defined by \Cref{eq:fitts-base}.
-The data is binned in intervals of the effective target width~($w_e$), given by \Cref{eq:fitts-we}, and are plotted for each pitch gradient setting. 
-A logarithmic line is fitted through the bins' median values by regression and all the results are presented in \Cref{fig:fitts-results}.
+To investigate if the interface generates a Fitts-like response from the participants, we plot the time to find the target as a function of the targets' indices of difficulty, as defined by \cref{eq:fitts-base}.
+The data is binned in intervals of the effective target width~($w_e$), given by \cref{eq:fitts-we}, and are plotted for each pitch gradient setting. 
+A logarithmic line is fitted through the bins' median values by regression and all the results are presented in \cref{fig:fitts-results}.
 
@@
 
-These results allows us to calculate and plot in \Cref{fig:fitts-ips} an index of performance, as given by \Cref{eq:fitts-performance}, for each audio setting.
-The results are summarised in \Cref{tab:fitts-results}.
+These results allows us to calculate and plot in \cref{fig:fitts-ips} an index of performance, as given by \cref{eq:fitts-performance}, for each audio setting.
+The results are summarised in \cref{tab:fitts-results}.
 For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
@@
 The \textit{med} and \textit{hi}, instead, are not significantly different from each other ($p_{med-hi} = 0.85$).
-The results for Group~\textit{G2} show generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \Cref{fig:fitts-results}.
+The results for Group~\textit{G2} show generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
 Again, from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin, compared to the \textit{med} setting, with the Wilcoxon test and Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results, respectively.
@@
 
-\Cref{fig:fitts-ips} shows a significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
+\cref{fig:fitts-ips} shows a significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
 This is further supported by the Kruskal-Wallis test, revealing that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001,~p_{med} < 0.001,~p_{hi} < 0.001$).
@@
 
-Regarding target acquisition, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings (see \Cref{tab:target-results}) seems to indicate that simply increasing the pitch gradient leads to better target-pointing performance.
-However, \Cref{fig:pitch-thresholds-hist} shows that the frequency difference between the ``on-target'' tone and the selected one with the \textit{hi} setting approaches the cut-off frequency of Group~\textit{G1}, indicating an inflection point where increasing the gradient reduces the final performance.
+Regarding target acquisition, the progressive improvement from the \textit{lo}, \textit{med} and \textit{hi} settings (see \cref{tab:target-results}) seems to indicate that simply increasing the pitch gradient leads to better target-pointing performance.
+However, \cref{fig:pitch-thresholds-hist} shows that the frequency difference between the ``on-target'' tone and the selected one with the \textit{hi} setting approaches the cut-off frequency of Group~\textit{G1}, indicating an inflection point where increasing the gradient reduces the final performance.
 Indeed, the participants from Group~\textit{G2} seem to go beyond this threshold and reach a saturation point where they can no longer reliably distinguish different tones.
@@
 This work identified a number of uncertainties that can be the focus of future work.
-These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
+These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
 Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.

### 2020-01-20 paper.tex
Spelling fixes, etc.

@@
 
-\todo{edit start}
 The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones.
-Both these devices are shown in \cref{fig:tango-headphone}.
-This a Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
+Both of these devices are shown in \cref{fig:tango-headphone}.
+This Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
 It also gives access to Android's full range of interface and I/O options.
@@
 These headphones have the benefit of not interfering with a user's normal hearing function.
-\todo{edit end}
 
@@
 
-\todo{edit start}
-This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source 3D positions.
+This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
 By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
-In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
+In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
 However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
-We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
-\todo{edit stop}
+We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
 In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
@@
 
-Over multiple years, both commercial and academic parties have devices new and innovative mobile navigation and travel aids for people with visual impairments.
+Over the years, commercial and academic parties have devised new and innovative mobile navigation and travel aids for people with visual impairments.
 Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
 Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
-However, from an ergonomic perspective, haptic feedback is a weak performer and require significant additional external hardware to transmit guidance instructions with significant resolution.
+However, from an ergonomic perspective, haptic feedback is a weak performer and require significant additional external hardware to transmit guidance instructions with sufficient resolution.
 Furthermore, both haptic and vocal feedback can present a significant cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
-Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
+Indeed, participants report that they prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
 As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
-However, such tones can potentially fatigue a user if the tone is too unpleasant.
-Researchers started using cameras and object detectors to determine what a user is looking at and using them together with simple audio tones and vocal feedback signals to indicate to the user where to find an object.
+However, such tones can potentially fatigue a user if there are too unpleasant.
+Researchers started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
 They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
@@
 Work has been done in an attempt to add complexity to these tones by spatialising them with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
-The authors generally report favourable results when using snormal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
 However, the audio transmission device used has a significant effect on performance.
@@
 However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as the work by~\citet{durette2008visuo}.
+Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
 We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}.
-We found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions comparable to those of more expensive and over-ear headphones.
+We found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions comparable to those of more expensive over-ear headphones.
 
@@
 
-\subsection{Participant Feedback}
+%\subsection{Participant Feedback}
 
-\todo{include subjective feedback?}
+%\todo{include subjective feedback?}
 

### 2020-01-22 paper.tex
More minor fixes

@@
 
-The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones.
-Both of these devices are shown in \cref{fig:tango-headphone}.
+The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:tango-headphone}).
 This Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
 It also gives access to Android's full range of interface and I/O options.
-Bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
+Unlike normal headphones, bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
 These headphones have the benefit of not interfering with a user's normal hearing function.
@@
   \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
-  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right)~\citep{lock2019bone}.}
+  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).
+Adapted from~\citet{lock2019bone}.}
   \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
@@
 
-Over the years, commercial and academic parties have devised new and innovative mobile navigation and travel aids for people with visual impairments.
+Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments.
 Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
 Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
-However, from an ergonomic perspective, haptic feedback is a weak performer and require significant additional external hardware to transmit guidance instructions with sufficient resolution.
-Furthermore, both haptic and vocal feedback can present a significant cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
+However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
+Furthermore, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
 Indeed, participants report that they prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
@@
 However, such tones can potentially fatigue a user if there are too unpleasant.
-Researchers started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
+Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
 They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
@@
 
-Work has been done in an attempt to add complexity to these tones by spatialising them with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
+Work has been done in an attempt to spatialise these tones with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
 The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
@@
 Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
-We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}.
-We found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions comparable to those of more expensive over-ear headphones.
+We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}, and found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions.
+The measured performance is comparable to those of more expensive and over-ear headphones.
 

### 2020-01-23 paper.tex
Added adaptation notes to figures
More edits

@@
   Sound perception is a fundamental skill for many people with severe sight impairments.
-  The research presented in this paper is part of an ongoing project, the aim of which is to build a mobile guidance aid to assist people with vision impairments find objects within an unknown indoor environment.
+  The research presented in this paper is part of an ongoing project with the aim to create a mobile guidance aid to help people with vision impairments find objects within an unknown indoor environment.
   This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
@@
 The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:tango-headphone}).
-This Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
+This Tango device uses a set of embedded RGB-D cameras and other hardware and software components to provide accurate real-time localisation estimates and has powerful image-processing capabilities.
 It also gives access to Android's full range of interface and I/O options.
@@
 These headphones have the benefit of not interfering with a user's normal hearing function.
-
-%The prototype is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities.
-%It also provides access to Android's full range of interface tools and I/O options. 
-%Furthermore, a set of bone-conduction headphones (see \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.
 
@@
   \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
-  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).
+  \caption{A Tango tablet and bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).
 Adapted from~\citet{lock2019bone}.}
@@
 
-This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
+The system generates guidance instructions that can be interpreted in real-time with minimal additional cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
 By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
@@
 
-The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a presentation of the design and implementation of our interface in \cref{sec:system-description}.
-This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiments} and \cref{sec:results}.
-Finally, the paper concludes with a summary and discussions on future research prospects in \cref{sec:conclusion}.
+The rest of the paper starts by discussing relevant works and previous research in \cref{sec:prev-work}.
+This is followed by a discussion on the design and implementation of our interface in \cref{sec:system-description}.
+The experiments that were conducted are discussed in \cref{sec:experiments}, while their results are presented and discussed in \cref{sec:results}.
+The paper concludes with a summary of the work and discussions on future research prospects in \cref{sec:conclusion}.
 
@@
 Furthermore, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
-Indeed, participants report that they prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
+
+Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
 As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
@@
 They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-
-%\todo{edit start}
-%Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
-%The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
-%In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
-%However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
-%Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
-%Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
-%Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
-%\todo{edit stop}
 
@@
 The measured performance is comparable to those of more expensive and over-ear headphones.
-
-%Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
-%Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
-%The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
-%However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
-%Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.
-%This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
-%~\citet{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
-%We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
-%We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.
 
@@
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
-%To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
 To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
@@
 
-Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound,lock2019bone}.
+Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
 The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
@@
 The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}.
-This interface was implemented and evaluated in previous work~\citep{lock2019bone}.
+This interface was implemented and evaluated by~\citet{lock2019bone}.
 
@@
   \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
-Note the logarithmic scale of the frequency axis~\citep{lock2019bone}.
+Note the logarithmic scale of the frequency axis.
+Adapted from~\citet{lock2019bone}.
 }
@@
 
-The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound,lock2019bone}.
+The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
 The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
@@
 
-A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison,lock2019bone}.
+A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison}.
 To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
@@
 The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
+In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\cite{lock2019bone}.
 
@@
 A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of information flow.
-The system implementation used here is similar to the one used by~\citet{lock2019bone}.
+The system implementation used here is similar to the setup used by~\citet{lock2019bone}.
 When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
@@
   \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
-  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}. }\label{fig:pipeline}
+  \caption{A diagram of the individual system components and their communication pipelines.
+$F$ indicates a feedback signal and $P$ a pose signal.
+Adapted from~\citet{lock2019bone}.
+}\label{fig:pipeline}
   \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
@@
 
-%To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
-%The participants were given a Tango device running an app that implements the experimental setup in \cref{fig:pipeline}.
-The app generates a set of virtual targets and presents them to each participant through the audio interface, one at a time.
-%The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
-%Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
-%When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
-%The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
-%A total of 28 targets were generated per participant.
-
-This experimental setup was used in~\cite{lock2019bone}.
+A similar experimental setup was used in~\cite{lock2019bone}.
 However, in these experiments we also want to see how changing the gradient of the pitch function, visualised in \cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
@@
 \cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
-%The median is used for each grouping given the skewed plot and
 
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-%while Group~\textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
 We also noted that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
@@
 
-%\subsection{Participant Feedback}
-
-%\todo{include subjective feedback?}
-
 \subsection{Discussion}

### 2020-04-29 review/reviews.tex
Added reviewer summaries

\documentclass{article}

\begin{document}

\section{Reviewer 1}

The reviewer seemed mostly content with the submission, suggesting some additional references, typo corrections and some specific suggestions for rephrasing some parts to improve the paper's accuracy. 
Furthermore, they suggest to reframe the paper in the micro-navigation context to make it more appealing to researchers who wish to know the accuracy of bone-conduction guidance cues.
Finally, they also suggest that the variance in the partially sighted group need to be better explained, by adding their demographics for example.

\section{Reviewer 2}

\section{Reviewer 3}

\end{document}

### 2020-04-29 paper.tex
R1 typo fixes

@@
 Every time a participant was confident that they were pointing at a target, i.e.\ hearing a signal that is placed at their front at a frequency of \SI{512}{\hertz}, they tapped the device's screen, marking the location and generating a new target.
-The target's are all positioned relative to the device's camera coordinate system, which is tracked by the Tango hardware and localisation API.\
+The targets are all positioned relative to the device's camera coordinate system, which is tracked by the Tango hardware and localisation API.\
 Each participant was tasked with finding 28 targets each.
@@
 These results are included in \cref{tab:target-results}.
-The Pearson correlation scores for Group~\text{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.
+The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.
 However, the correlation scores for Group~\textit{G2} are significantly weaker, with a pan angle correlation $r_{pan} \in [0.1, 0.21],~p < 0.03$.
@@
 Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
-This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
+This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
 Consequently, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.
@@
 This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}.
-Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{med} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).
+Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{hi} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).
 

### 2020-04-29 paper.tex
R1: framed system as micro-navigation, improving system description

@@
 
-Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments.
-Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
-Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
+Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
+The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings.
+Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
+The interface for this work is used to provide instructions to a stationary user to guide them to point a camera at a target location and we therefore are mainly concerned with micro-navigation tools.
+In this context, respondents with visual impairments typically prefer haptic and vocal feedback over an audio tone~\citep{arditi2013user,golledge2004stated}.
 However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
-Furthermore, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
-
-Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
+Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
+This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.
+%Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
 As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
@@
 
-A set of bone-conduction headphones is used as the audio transmission medium.
-These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
-This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\citep{lichtenstein2012headphone}.
-Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
-The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected for the aforementioned reasons of non-interference and increased discretion when compared to larger over-ear headphones.
+People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since this can have severe effects~\citep{lichtenstein2012headphone}.
+We there use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities.
+Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
+The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected.
+These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.
 

### 2020-04-30 paper.tex
R1: added participant ages, added similarity test

@@
 
-People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since this can have severe effects~\citep{lichtenstein2012headphone}.
-We there use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities.
+People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
+We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities.
 Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
@@
 
-\subsection{Audio Interface}
+%\subsection{Audio Interface}
 
-Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
-The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
-Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
-When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
-The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.
+Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
+These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences , ITD and ILD respectively) and monaural cues, where a cue is extracted directly from each ear's audio signal (e.g.\ the spectral profile, audio intensity).
+The ITD and ILD extracted from binaural cues allow a user to localise a sound on the horizontal plane (e.g.\ a sound from the right will hit the right ear before left one), while monaural cues indicate a sound's distance (e.g.
+louder sounds appear closer than softer ones) and its position on the vertical plane (e.g.\ the spectral profile generated from the signal hitting the user's body).
+Prior to transmitting an audio signal to the user, it can be adjusted by an HRTF to mimic a natural sound source and make a user believe it is located at some arbitrary 3D location. 
+An HRTF is a mathematical function that simulates a human head and ear's response to an external sound and is derived by capturing key characteristics that affect the monaural and binaural responses at the user's ear, such as the hearing level and anatomy.
+An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.
 
-When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, making the brain believe a sound is located at some arbitrary position.
-An HRTF is a mathematical function that simulates the response signal of a human head and is derived by capturing key characteristics that affect the monaural and binaural responses, such as the user's hearing levels and head size.
-Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
-However, given the complex process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.
+The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
+Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}.
+However, we propose a linear adjustment to the signal's pitch as a function of the elevation angle to overcome the limitations of bone-conduction headphones and spatialised audio stated previously.
+The pan angle can still be conveyed with a spatialised audio signal generated by an HRTF.
+Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
+This interface was implemented and evaluated in~\citet{lock2019bone}.
 
-The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
-Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
-However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
-The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}.
-This interface was implemented and evaluated by~\citet{lock2019bone}.
+%Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
+%The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
+%Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
+%When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
+%The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.
+
+%When an audio signal is transmitted via a set of speakers or headphones, it can be transformed with an HRTF to mimic the characteristics of a natural sound source before it is transmitted, making the brain believe a sound is located at some arbitrary position.
+%An HRTF is a mathematical function that simulates the response signal of a human head and is derived by capturing key characteristics that affect the monaural and binaural responses, such as the user's hearing levels and head size.
+%Since hearing responses are unique amongst different users, the best results would be observed if each user had their own customised HRTF.\
+%However, given the complex process involved to capture the required user characteristics, making unique HRTFs is often an untenable solution and using average values (e.g.\ head measurements, height, etc.) have shown to produce acceptable results~\citep{gardner1995hrtf}.
+
+%The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
+%Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
+%However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
+%The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}.
+%This interface was implemented and evaluated by~\citet{lock2019bone}.
 
@@
 
-\subsubsection{Pan Dimension}
+\subsection{Pan Dimension}
 
-The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
-The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
-For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume compared to the left ear.
+To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
+For example, a sound placed at a person's right will hit their right ear first with a slightly higher volume compared to the left ear.
+Since the binaural cues are largely independent if the signal's spectral profile, it would be convenient to use a simple audio wave to transmit guidance instructions to the user.
+Therefore, in this work a pure sine wave was used, but can easily be replaced with a richer tone once the system's characteristics are better understood. 
+The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.
+%which uses the person and targets' positions as input, and outputs a transformed audio signal.
 
-In this work, a pure sinusoidal wave was used. 
-People typically have trouble localizing a pure tone without a sufficiently rich spectral signature.
-However, the ITD and ILD are independent of the tone's spectral make-up, while the elevation angle is given through a different mechanism.
-Therefore, a pure sine wave is suitable to convey the target's pan angle.
-To transform and spatialise the audio signal, we used OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}, which uses the person and targets' positions as input, and outputs a transformed audio signal.
+\subsection{Elevation Dimension}
 
-\subsubsection{Elevation Dimension}
+To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
+When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
+This high/low scheme was selected based on humans' natural association of high-pitched sounds with elevated objects and vice-versa for low-lying objects~\citep{pratt1930spatial,blauert1997spatial}.
+The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}.
 
-A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison}.
-To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
-When the camera vector is at the correct elevation, the tone pitch is set to neutral.
-When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
-This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\citep{pratt1930spatial,blauert1997spatial}.
-An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\citep{shepard1964circularity}.
-The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.
-
-The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}) and the gradient is determined by setting the angle and pitch limits.
+The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
+These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
+This tone is heuristically set to \SI{512}{\hertz} following practical tests, which is comfortably audible for a large number of octaves changes.
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
-After practical tests with the interface, we set the neutral, on-target pitch the HMI emits to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
-The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
-In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\cite{lock2019bone}.
+In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.
 
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group~\textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18--55 years old; 36 female, 16 male).
+Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
+Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $73\pm20$).
+Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception.
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-We also noted that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
+Furthermore, the significant variance in the error results for group \textit{G2} could possibly be because of the higher mean age compared to group \textit{G1} and their general inexperience with mobile phones.
+However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
+The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test ($p > 0.05$ for both groups and all three test conditions).\todo{include these p-values in the table?}
+This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
+Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
+We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
 Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
-
-Comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
-This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar, and that groups from a different population can reasonably be expected to produce similar errors, under similar experimental conditions.
-Consequently, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.
+Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.
 
@@
   \centering
-  \caption{A summary of the $p$-values comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions. }\label{tab:inter-group-results}
+  \caption{A summary of the $p$-values from the Kruskal-Wallis test comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions.
+}\label{tab:inter-group-results}
   \begin{tabular}{lll}
@@
 However, the Fitts model does not account for changing stimuli and different strategies.
-We therefore hypothesize that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
+We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
 This seems to indicate a speed/accuracy trade-off in finding the targets.

### 2020-04-30 paper.tex
R3: Typos, explain difference in scale in fig5+6, need to reply to him to motivate reason for not using real objects and why the largest number of guesses are placed in the centre intervals

@@
 \cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
+Note that the cut-off thresholds in \cref{fig:pitch-thresholds-hist} are transformed from the logarithmic semitone scale in \cref{fig:pitch-thresholds} to a linear Hertz-based scale for visualisation purposes to make the separation between the settings more clearly visible.
 
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-Furthermore, the significant variance in the error results for group \textit{G2} could possibly be because of the higher mean age compared to group \textit{G1} and their general inexperience with mobile phones.
+Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
 However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
@@
 This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.76,~p_{lo} = 0.045;~r_{med} = 0.96,~p_{med}<0.001;~r_{hi} = 0.86,~p_{hi} = 0.013$).
-Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data plot, indicating less consistency in the time-to-target results for participants with severe sight impairments.
-This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}.
+Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data interval, indicating less consistency in the time-to-target results for participants with severe sight impairments.
+This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}, as well as the mean age and general level expertise with mobile devices of this particular group.
 Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{hi} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).

### 2020-05-04 paper.tex
Updated Fitts calculations

@@
 
-This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the final part of their journey, addressing the so-called `last 10-yard problem'.
+The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
 Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
@@
 However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
-In previous work we developed a prototype system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention as well\citep{lock2019active}.
+The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the advantages and limitations of its main user.
+In previous work we developed a prototype guidance system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention~\citep{lock2019active}.
+However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that will possibly benefit the user experience and boost long-term navigation performance.
+
+%This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the final part of their journey, addressing the so-called `last 10-yard problem'.
+%Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
+%In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
+%However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
 
@@
 \begin{itemize}
-  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's tilt angle when using a mobile device with a bone-conducting headset;
+  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's elevation angle when using a mobile device with a bone-conducting headset;
   \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
@@
 These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\citep{wu2010fitts}.
-However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's tilt angle, as demonstrated in this paper.
+However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's elevation angle, as demonstrated in this paper.
 
@@
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
-Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty (the ratio between the distance to the target and its width).
-It also provides a so-called `index of performance' that we can use as a metric to compare the results between the three configurations.
+Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
+It also provides a so-called `index of performance' ($IP$), which can be used to compare the results between the three different configurations used in the experiments.
+Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.
 
-Here we briefly summarise the equations and quantities involved in our metric.
+\todo{mention limitations of Fitts, i.e. zero-width and not playing second tone to confirm target found}
+
+%that we can use as a metric to compare the results between the three configurations.
+
+Here we briefly summarise the equations and quantities involved in this metric.
 Fitts's Law is given by
@@
 \noindent
-where $\sigma$ is the standard deviation of the error data, taken as the angle between the participant's target selection and target's actual angular position.
+where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with
+
+\begin{equation}
+  \sigma = \sqrt{\frac{\sum_{i=1}^{N}\left(\sqrt{(x_i-\bar{x})^2 + (y_i - \bar{y})^2}\right)^2}{N-1}}
+\end{equation}
+
+\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
 Fitts's index of performance, $IP$, can then be calculated using
@@
 Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
-Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $73\pm20$).
+Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
 Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception.
@@
 For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
-This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.76,~p_{lo} = 0.045;~r_{med} = 0.96,~p_{med}<0.001;~r_{hi} = 0.86,~p_{hi} = 0.013$).
+This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
 Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data interval, indicating less consistency in the time-to-target results for participants with severe sight impairments.
-This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}, as well as the mean age and general level expertise with mobile devices of this particular group.
-Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{hi} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).
+This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}, as well as the mean age and general level of expertise with mobile devices of this particular group.
+Nevertheless, all three settings exhibit strong Pearson correlation scores ($r_{lo}=0.71,~p=0.005;r_{med}=0.85,~p_{med}<0.001;~r_{hi}=0.84,~p_{hi}<0.001$).
 

### 2020-05-07 review/response/response.tex
Adding review response tex

\documentclass{article}

\begin{document}

\noindent Dear associate editors and reviewers,

I would first like to sincerely thank you for your honest and helpful feedback on our work.
We have taken some time to go over and implement your suggestions and we believe that we can resubmit to you an improved version of the paper. 
Please find below our responses to your comments and suggestions, where we point out how we addressed them.

\section*{Reviewer 1}

\begin{itemize}
  \item \textit{In particular, the claim that "...both haptic and vocal feedback can present a cognitive burden and overwhelm a user’s input bandwidth, particularly when high-resolution guidance is required." needs to be clarified.
      In essence, as suggested in [kammoun2012navigation,petrie1997mobic], there are two synergic classes of information to be conveyed: directions (or macro-navigation), which is commonly conveyed through turn-by-turn instructions (e.g., [sato2019navcog3]), and space-related information (or micro-navigation), which is better conveyed through spatialized audio.
      Indeed, Arditi and Tian refer to the task of "request information about environmental objects", which is a micro-navigation task, and for which the participants preferred on-demand information rather than continuous feedback.
In this frame, the proposed analysis of the performance in localizing spatialized sound for micro navigation tasks using bone-conducting headphones is useful since many works already use bone conducting headphones for guidance, but their accuracy still needs to be validated.
}
  \item[] \noindent To address these concerns, we have added additional information to the introduction section that frames this as a micro-navigation task.
    We have also added an additional reference at the line in question to support our argument for not using constant vocal or haptic feedback such a micro-navigation task context.
    We also added a number of the works the reviewer kindly provided in the previous work section and throughout the rest of the paper.

  \item \textit{While the amount of novel content seems to be appropriate for a journal extension of the paper, the system description is copied verbatim from the previous paper, and Figures 1b, 2 and 3 are essentially identical. Content provided elsewhere should be summarized and readapted and not copied.}
  \item []We have completely rewritten the system description section and further modified the figures in question.

  \item \textit{However, there is one critical issue. The paper states: "..differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation... This results confirm that the performance of the blindfolded participants and those with severe sight impairments are statistically similar...".
    This statement is not valid. Difference testing detects difference, but the absence of statistically significant difference does not imply similarity. For that equivalence testing is needed.}
  \item[] This is addressed in section 5.3, where we confirm the statistical similarity with a Kolmogorov-Smirnov 2-sample test.

  \item \textit{Another important consideration that should be discussed is the high variance in the results of the participants with visual impairments. As the authors suggest, this might be an artifact due to a lower number of participants. However, there is also an alternative interpretation: prior literature on spatial understanding in people with visual impairments suggests that visual impairment onset age, prior experience with spatialized information and other characteristics impact spatial performance capabilities [millar1994understanding, pring2008psychological]. Thus, it may be that the high variance in data for visually impaired participants is due to the high variance in participants' characteristics. As the number of visually impaired participants is low, I suggest adding a table presenting participants' demographic characteristics (age, impairment, onset, navigation expertise....)}
  \item[] This is a valid point. In Section 4.4 we have added additional information regarding the distributions of the participants' age, sex, age of impairment onset and level of impairment.
\end{itemize}

\section*{Reviewer 2}

\begin{itemize}

  \item \textit{While I have reservations about using Fitts's Law in this paper, probably the single best citation for the justification for using We is:
Zhai, S., Kong, J., \& Ren, X. (2004). Speed–accuracy tradeoff in Fitts' law tasks—on the equivalency of actual and nominal pointing precision. International journal of human-computer studies, 61(6), 823-856.
      Also not all that critical given my reservations, but JFYI. In two-dimensional directed pointing, the calculation of We is better calculated as described in:
    Jacob O. Wobbrock, Kristen Shinohara, and Alex Jansen. 2011. The effects of task dimensionality, endpoint deviation, throughput calculation, and experiment design on pointing measures and models. In Proceedings of the SIGCHI Conference on Human Factors in Computing Systems (CHI '11). Association for Computing Machinery, New York, NY, USA, 1639–1648.}
  \item[] These are indeed helpful references. We have integrated both into the paper, and the latter suggested method of calculating $w_e$ was used to generate the updated figure 11 and 12. This seemed to have generated a better fitting model, which led to improved correlation scores in section 5.4 and indices of performance in table 3.

  \item \textit{First, while it is good that the authors included visually impaired individuals in the study, it is hard to know what to make of the differences in performance (and patterns of performance) between the two groups. Since the whole point of the study is to inform a system intended to be used by visually impaired individuals, how should we interpret this? The two groups are VERY different in performance, N, and (I assume, though details are not provided) demography. While having a group of young blind-folded participants is fine as a baseline for a project like this, the apparent variability and small N in the VI group is problematic. This isn’t really a fatal flaw, but it makes the study much less robust. At a minimum, we need to know more detail about the demographic details of the two groups. Currently, the paper lumps the age range and gender together for the two groups. Because the behavior of the two groups is so different, these really need to be separated.}
  \item We acknowledge that the small sample size is not ideal.
    However, we attempted to alleviate concerns and make the results more robust by adding the statistical difference and similarity tests between the 2 groups.
    These confirm that, at least statistically, the 2 groups performed similarly.
    Our intention is that this is interpreted that if we repeat the experiment with another group of participants with visual impairments (perhaps a younger group with more experience with mobile devices and electronic navigation aids), we may collect results that fall closer to that of the blindfolded group.
    The reviewer is correct in pointing out that the demographics for each group need to be separated and this was done in Section 4.4.
    We also added observations in the Discussion section to hypothesise on the difference in mean demographics between the 2 groups may also have influenced the performance we recorded.

  \item \textit{Because the targets in this task are point targets, there is no W, so the authors used the spread of hits around the target to manufacture an effective width We. The problem with this is that the whole concept of We (from Crossman and then later Welford) *assumes that participants have some level of W that they are targeting*. Without this, there is no external feedback as to whether a user has actually hit the target or not—it’s just their own subjective sense. That is, “accuracy” in this case is essentially determined by the average subjective impression of individual participants (i.e., “this seems right to me… click!”). And, as seen in Fig 8, there are huge differences in the distribution of “error” between the two groups (G1 \& G2), and I suspect there may be even larger differences between users: different thresholds of “good enough” for different users. It’s also not clear to me if We is calculated for each level of Distance, or is it calculated across multiple amplitude of movements?
    So my skepticism of the whole exercise of using Fitts’s Law for comparing these conditions is that it feels weird to me to reconstitute some form of W (We) from the spread of hits around a point target when there’s no objective feedback for hitting it (i.e., no W). Since they mostly just use this to make comparisons between different elevation stimuli, it’s not clear that they NEED to do this anyway. I think they could probably just use speed \& distance and be done with it, especially since there is no change in W. I guess if We were actually changing with different conditions (D or elevation), there might be some justification for this (though We in that case will be highly correlated with D, which would violate at least the spirit of the law), but this experiment seems way too small to detect this (and this detail isn’t reported anyway). Why go to all the trouble of doing the Fitt’s analysis when the only thing you’re varying is distance? Indeed, for the final take-aways that the authors provide, this seems like enormous overkill.}
  \item[] We understand the reviewer's concerns regarding the use of Fitts's Law with an experiment where the targets have no physical width and have to rely on their own subjective senses to determine where the target was placed. 
    Indeed, as the reviewer points out, every participant will have their own opinion on where the target is truly located.
    The primary goal of this work is precisely to measure this difference, i.e. given some spatialised audio signal, how well does it convey a target location to a new user?
    For this reason, we could not provide the participants with any more information to more objectively give the target's location (e.g. a second audio tone).
    Since we did not do this in our experiments, Fitts's Law does not seem an appropriate model here. 
    However, we respectfully disagree with this assertion for 2 reasons.
    Firstly, we did not specify this in the text, but the app was coded such that it played back the 512Hz on-target tone when a participant was within 10cm of the target centre, effectively giving it a width (this information has been added in section 4.3).
    This search is then similar to the work on the Prince method by~\cite{kabbash1995prince}, who showed that searching for a point-target with an oversized cursor (a 10cm radius 'searchlight' cursor in our case) is comparable to a normal Fitts-task with a target of known width being searched for with a point-cursor.
    We refrained from using this 10cm radius as a target, given the subjective nature of the participants' estimates and opted to use the more conservative $w_e$ we calculated instead, which we found to be approximately 10\% higher for each participant.
    We calculated the $w_e$ for each participant and setting to generate the plots in fig 11 and used the medians across the participants to generate the IPs for each setting.
    For full transparency, we included the $w_e$ we calculated in the text.
    Secondly, despite the experiment's apparent non-conformance to Fitts's requirements, it still provides a fairly robust fit for the movement data we recorded for both groups, which in and of itself is interesting given the significant performance differences between the two groups.
    This latter point leads to the reviewer's other major concern, which is that using Fitts's Law for this work 'seems like enormous overkill'.
    From the surface, tend to agree, but provided more context, we believe the reviewer will agree that there is logical reasoning for using Fitts here beyond the additional keywords.
    This work forms part of a larger project where we initially looked into ways to create an interface for a guidance system that can autonomously adapt its own internal parameters to better match the user's limitations and capabilities, thereby boost overall guidance and target finding performance.
  For this optimisation process, we needed a metric we can use to measure performance for different parameter settings to determine the effectiveness of a parameter adjustment.
  This is why Fitts's Law came to mind: it provided a robust unifying metric between search time and accuracy.
  At the time of writing, it was unclear whether Fitts is applicable to our interface and for this reason we sought to determine whether there such a relationship does indeed manifest itself.
  Furthermore, any data we can collect on the expected perception limitations and abilities of the general population will enable us to select a good 'default' setting to start the optimisation from, as well as keep the parameters bounded to some effective range.
  The characterisation experiments we conducted was to address the latter point.
  These results provide us a) with a good metric to judge whether adjustments to the interface parameters increase performance and b) provide us with a 'good' starting point to start the optimisation process for a new user.
  We opted to not include these details, since it is not directly pertinent to this work and did not wish to bog down the reader in details of work that is still in progress.
  However, we agree that some additional detail will make the reasoning a bit clearer and alleviate some confusion on why we even bothered with Fitts's Law.
  These details were added to the Introduction section and we also modified the terminology to not imply that we found an adherence to Fitts's Law, but rather an observation of a Fitts-like relationship.
  We sincerely hope that these clarifications and modifications to the text address the reviewers concerns about us using Fitts's Law for these experiments.

  \item \textit{To my mind, the paper is a bit of an “LPU” (least-publishable-unit), for a larger, more interesting project (which I would love to see!). The specific contribution here is in the use of a pitch gradient for conveying elevation information for spatialized 3D audio as well as a user study evaluating its effectiveness and some of the design space (three different pitch gradients). I’m not sure that I would consider this an adequate contribution for a shorter conference paper (such as ASSETS); for TACCESS, this seems weak. That is, I would say the contribution is not commensurate with the length of the paper.}
  \item[] On this front, we again have to respectfully disagree with the reviewer's opinion.
    We pointed out in the previous work section that researchers have implemented different combinations of spatialised sound, frequency adjustments and headphones in their navigation systems for people with visual impairment with different levels of success.
    However, to our knowledge, very little work has been done in quantifying these spatialised audio signals with varying pitch gains with a significant number of participants with or without visual impairments, as well as bone-conduction headphones.
    Indeed, we believe that the experiment design, analysis and scale is a fairly novel contribution to other researchers that wish to know what level of perception they can expect from audio signals played back via bone-conduction headphones.
    It is not our intention to minimise the work to an 'LPU' and indeed, this paper represents a phase of work that was completed for a larger overall project.
    However, in our opinion it would be detrimental to the message we'd like to publish to the scientific community if we include too much detail on the overall project and bog the reader down in details that are not pertinent to this publication.

\end{itemize}

\section*{Reviewer 3}

%\begin{itemize}
%\end{itemize}

\end{document}

### 2020-05-07 paper.tex
Adding review response tex

@@
 \usepackage{natbib}
+\usepackage{xcolor}
+\usepackage[most]{tcolorbox}
 \usepackage{todonotes}
+
+\newcommand\hl[1]{\colorbox{yellow}{\textcolor{black}{#1}}}
+\newcommand\hlbreakable[1]{\textcolor{red}{#1}}
+\newtcolorbox{highlighted}{colback=yellow,coltext=black,breakable}
 
@@
 
-The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
+\begin{highlighted}The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
 Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
@@
 However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that will possibly benefit the user experience and boost long-term navigation performance.
+\end{highlighted}
 
@@
 
+\begin{highlighted}
 Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
@@
 This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.
+\end{highlighted}
 %Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
@@
 
+\begin{highlighted}
 Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
@@
 These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance. 
+\end{highlighted}
 
@@
 
+\begin{highlighted}
 Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
@@
 This interface was implemented and evaluated in~\citet{lock2019bone}.
+\end{highlighted}
 
@@
 
+\begin{highlighted}
 To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
@@
 The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.
-%which uses the person and targets' positions as input, and outputs a transformed audio signal.
+%which uses the person and targets' positions as input, and outputs a transformed audio signal.}
+\end{highlighted}
 
@@
 
+\begin{highlighted}
 To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
@@
 In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.
+\end{highlighted}
 
@@
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
+\begin{highlighted}
 Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
@@
 Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.
+\end{highlighted}
 
@@
 
-\noindent
-where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with
+\noindent \hlbreakable{where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with}
 
@@
 \noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
+\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre}, but the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
+Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
+Previous authors have found this to capture the true performance metrics fairly well~\citep{zhai2004speed}.}
 Fitts's index of performance, $IP$, can then be calculated using
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
+\hlbreakable{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
 Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
-Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception.
+Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception and none reported any significant prior experience with electronic navigation aids.
+}
 None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
@@
 \cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
-Note that the cut-off thresholds in \cref{fig:pitch-thresholds-hist} are transformed from the logarithmic semitone scale in \cref{fig:pitch-thresholds} to a linear Hertz-based scale for visualisation purposes to make the separation between the settings more clearly visible.
+\hlbreakable{Note that the cut-off thresholds in \cref{fig:pitch-thresholds-hist} are transformed from the logarithmic semitone scale in \cref{fig:pitch-thresholds} to a linear Hertz-based scale for visualisation purposes to make the separation between the settings more clearly visible.}
 
@@
 These results are included in \cref{tab:target-results}.
-The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.
+\hlbreakable{The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.}
 However, the correlation scores for Group~\textit{G2} are significantly weaker, with a pan angle correlation $r_{pan} \in [0.1, 0.21],~p < 0.03$.
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
-However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
+\hlbreakable{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
+However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
 The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test ($p > 0.05$ for both groups and all three test conditions).\todo{include these p-values in the table?}
-This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
+\hlbreakable{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
 Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
@@
 Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.
+}
 
@@
 For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
-This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
+\hlbreakable{This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
 Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data interval, indicating less consistency in the time-to-target results for participants with severe sight impairments.
 This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}, as well as the mean age and general level of expertise with mobile devices of this particular group.
-Nevertheless, all three settings exhibit strong Pearson correlation scores ($r_{lo}=0.71,~p=0.005;r_{med}=0.85,~p_{med}<0.001;~r_{hi}=0.84,~p_{hi}<0.001$).
+Nevertheless, all three settings exhibit strong Pearson correlation scores ($r_{lo}=0.71,~p=0.005;r_{med}=0.85,~p_{med}<0.001;~r_{hi}=0.84,~p_{hi}<0.001$).}
 
@@
 For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
-This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001,~p_{lo-hi} < 0.001$).
-The \textit{med} and \textit{hi}, instead, are not significantly different from each other ($p_{med-hi} = 0.85$).
+\hlbreakable{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001,~p_{lo-hi} < 0.001$).
+The \textit{med} and \textit{hi}, instead, are not significantly different from each other ($p_{med-hi} = 0.85$).}
 The results for Group~\textit{G2} show generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.

### 2020-05-07 review/response/response.tex
Edits to reviews

@@
-\documentclass{article}
+\documentclass{scrartcl}
 
@@
 
+\title{Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments}
+\subtitle{Rebuttal to Reviewers}
+
+\author{JC Lock; G. Cielniak; ID Gilchrist; N Bellotto}
+
+\maketitle
+
 \noindent Dear associate editors and reviewers,
 
-I would first like to sincerely thank you for your honest and helpful feedback on our work.
+We would first like to sincerely thank you for your honest and helpful feedback on our work.
 We have taken some time to go over and implement your suggestions and we believe that we can resubmit to you an improved version of the paper. 
@@
 
-%\begin{itemize}
-%\end{itemize}
+\begin{itemize}
+  \item \textit{The contents in Fig.
+6 and Fig.
+7 are confusing.
+They both show the median cut-off.
+Since they have different units (one is semitone and the other is Hz), is the median cut-off the same?
+Explain this threshold more clearly.}
+
+  \item[] We used a linear scale in Figure 7 to highlight the separation between the 3 settings, which was not as clearly evident with the logarithmic semitone scale.
+    This has been clarified in section 5.2.
+
+  \item \textit{The contents in Fig 5 and Fig.
+6 are confusing.
+Fig.
+5 shows that the number of wrong guesses is much bigger than that of correct guesses.
+Does it mean that the pitch is hard to be distinguished?
+It also shows that the number of wrong guesses mostly locates in the area where the pitch difference is almost 0.
+Intuitively, with the increase of pitch difference, the correct guesses should be increased as well.
+But in Fig.
+6, it shows that most of the samples (75\% the correct guesses) are in the area with smaller pitch threshold e.g 0 to 0.5, rather than in the areas with larger pitch threshold e.g.
+1.0-2.0.}
+  \item[] Given the progressive difficulty process we used, the tones became increasingly more difficult to distinguish from one another, i.e.
+small frequency difference represented by a small semitone and Hz difference.
+    In Fig 6, it shows the threshold where 75\% of the correct guesses lie to the right, i.e. the larger semitone differences that are easier to distinguish.
+
+  \item \textit{Before equation (3), the authors claim the targets have no width.
+So does it mean that the virtual objects are actually a virtual point randomly created in the Tango’s screen?
+Since the Tango has an RGB-D camera to measure both direction and distance, a more practical experiment design should use the real daily objects.}
+  \item[] This is correct, we use virtual targets generated by the Tango.
+    We opted for this setup over physical targets, since piratically it was advantageous and allowed us to easily place many targets at a variety of random locations while still knowing precisely where the targets are generated, since they are all located relative to the Tango's frame of reference.
+    For these pointing experiments, it was sufficient, but in a larger-scale experiment with a real object search system, real objects would indeed make more sense than virtual ones.
+
+  \item \textit{Improve the resolution of Fig. 8 to make it more clear.}
+  \item[] Fig 8 has been updated with this change. 
+\end{itemize}
+
+\bibliography{bib}
+\bibliographystyle{ieeetr}
 

### 2020-05-07 paper.tex
Edits to reviews

@@
 \usepackage{siunitx}
-\usepackage{cleveref}
+\usepackage[capitalise]{cleveref}
 \usepackage{booktabs}
@@
   \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's elevation angle when using a mobile device with a bone-conducting headset;
-  \item we show that this sound-based human-machine interface conforms to Fitts's Law and can provide a useful metric of performance for similar mobile user interfaces.
+  \item we show that this sound-based human-machine interface exhibits a response that is well-modelled by Fitts's Law which can provide a useful metric of performance for similar mobile user interfaces.
 \end{itemize}
@@
 \noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
-\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre}, but the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
+\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, the on-target tone was emitted.
+This is similar to the work by~\citet{kabbash1995prince}, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
+However, the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
 Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
@@
 \cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group.
-\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
-\hlbreakable{Note that the cut-off thresholds in \cref{fig:pitch-thresholds-hist} are transformed from the logarithmic semitone scale in \cref{fig:pitch-thresholds} to a linear Hertz-based scale for visualisation purposes to make the separation between the settings more clearly visible.}
+
+\begin{highlighted}
+For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
+Each participant's median tone error for each setting was then plotted alongside the groups' median thresholds and plotted in \cref{fig:pitch-thresholds-hist}.
+These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.
+\end{highlighted}
 
@@
 	{>{\centering\arraybackslash}p{0.5cm}%
-	 >{\centering\arraybackslash}p{1.5cm}%
-	 >{\centering\arraybackslash}p{1.1cm}%
- 	 >{\raggedleft\arraybackslash}p{2.6cm}%
- 	 >{\raggedleft\arraybackslash}p{3.0cm}%
-	 >{\raggedleft\arraybackslash}p{3.0cm}}
+	 >{\centering\arraybackslash}p{1.2cm}%
+	 >{\centering\arraybackslash}p{0.9cm}%
+ 	 >{\raggedleft\arraybackslash}p{2.2cm}%
+ 	 >{\raggedright\arraybackslash}p{2.6cm}%
+	 >{\raggedright\arraybackslash}p{2.6cm}}
     \toprule

### 2020-05-12 paper.tex
Updated stats, figures. Modified discussion

@@
 \hlbreakable{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
+Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
 However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
-The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test ($p > 0.05$ for both groups and all three test conditions).\todo{include these p-values in the table?}
+The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test, where none of the $p$-values are significant.
+The $p$-values for this test are also listed in~\cref{tab:inter-group-results}.
 \hlbreakable{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
@@
   \centering
-  \caption{A summary of the $p$-values from the Kruskal-Wallis test comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions.
+  \caption{A summary of the $p$-values from the Kruskal-Wallis and Kolmogorov-Smirnov tests comparing the distributions of the different settings' error data for each group in both the pan and elevation dimensions.
 }\label{tab:inter-group-results}
-  \begin{tabular}{lll}
+  \begin{tabular}{lcccc}
     \toprule
-                   & Pan      & Elevation \\ \midrule
-      \textit{lo}  & $p=0.18$ & $p=0.90$  \\
-      \textit{med} & $p=0.86$ & $p=0.34$  \\
-      \textit{hi}  & $p=0.28$ & $p=0.38$  \\
+		   & \multicolumn{2}{c}{Kruskal-Wallis} & \multicolumn{2}{c}{Kolmogorov-Smirnov} \\
+		   & Pan      & Elevation & Pan      & Elevation \\ \midrule
+      \textit{lo}  & $p=0.18$ & $p=0.90$  & $p=0.07$ & $p=0.91$  \\
+      \textit{med} & $p=0.86$ & $p=0.34$  & $p=0.90$ & $p=0.36$  \\
+      \textit{hi}  & $p=0.28$ & $p=0.38$  & $p=0.61$ & $p=0.31$  \\
     \bottomrule
@@
 The results are summarised in \cref{tab:fitts-results}.
-For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{lo} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
-\hlbreakable{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{lo} setting is significantly different to the \textit{med} and \textit{hi} settings ($p_{lo-med} < 0.001,~p_{lo-hi} < 0.001$).
-The \textit{med} and \textit{hi}, instead, are not significantly different from each other ($p_{med-hi} = 0.85$).}
-The results for Group~\textit{G2} show generally lower and inconsistent indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
-Again, from the Friedman test ($p < 0.001$), the \textit{lo} setting produces the highest performance by a large margin, compared to the \textit{med} setting, with the Wilcoxon test and Holm-Bonferronni corrections ($p_{lo-med}=0.01$), followed by the \textit{hi} and \textit{med} settings' results, respectively.
-This seems to indicate that, for both groups, the \textit{lo} setting produces the highest level of performance, followed by the \textit{hi} setting.
+For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{med} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
+\hlbreakable{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{med} setting is significantly different to the \textit{lo} and \textit{hi} settings ($p_{med-lo} < 0.001,~p_{med-hi} < 0.001$).
+The \textit{lo} and \textit{hi} settings, instead, are not significantly different from each other ($p_{lo-hi} = 0.11$).
+The results for Group~\textit{G2} show generally lower indices of performance for each setting, which is expected given the increased times to target observed in \cref{fig:fitts-results}.
+%However, the \emph{hi} setting's result is an exception here and has a far smaller gap between it and its counterpart in Group \emph{G1}.
+Following visual inspection of the distribution and significant results from the Friedman test ($p < 0.001$), it is clear that the \textit{hi} setting produces the highest performance by a large margin, compared to the \textit{lo} and \textit{med} settings.
+This is supported by Wilcoxon tests ($p_{lo-hi}=0.01$, $p_{med-hi}=0.01$), which also show that the results for the \textit{lo} and \textit{med} settings are not different ($p_{lo-med}=0.09$).}
+
+%This seems to indicate that, for both groups, the \textit{lo} setting produces the highest level of performance, followed by the \textit{hi} setting.
 
@@
                 & Setting      & Mean Index of Performance \\ \midrule
-    & \textit{lo}  & $0.056\pm0.005$ \\
-    \textit{G1} & \textit{med} & $0.053\pm0.008$ \\
-		& \textit{hi}  & $0.051\pm0.007$ \\ \cline{2-3}
-    & \textit{lo}  & $0.034\pm0.009$ \\
-    \textit{G2} & \textit{med} & $0.014\pm0.002$ \\
-    & \textit{hi}  & $0.022\pm0.006$ \\
+                & \textit{lo}  & $0.054\pm0.005$ \\
+    \textit{G1} & \textit{med} & $0.057\pm0.006$ \\
+		& \textit{hi}  & $0.054\pm0.007$ \\ \cline{2-3}
+                & \textit{lo}  & $0.039\pm0.007$ \\
+    \textit{G2} & \textit{med} & $0.038\pm0.007$ \\
+                & \textit{hi}  & $0.048\pm0.008$ \\
     \bottomrule
@@
 \cref{fig:fitts-ips} shows a significant difference between the IPs for each group's respective settings, with \textit{G2} producing significantly lower indices of performance.
-This is further supported by the Kruskal-Wallis test, revealing that each setting's distribution is indeed significantly different from its counterpart in the other group ($p_{lo} < 0.001,~p_{med} < 0.001,~p_{hi} < 0.001$).
+This is further supported by a Kruskal-Wallis tests that reveals that each setting's distribution is indeed significantly different from its counterpart in the other group.
 The significant difference between the blindfolded group and the group of participants with visual impairments seems to indicate that the latter require significantly more time to find the target. 
@@
 
-The results for the accuracy and time performance with the proposed audio interface shows an interesting contrast.
-That is, the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
-However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
-Since Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
-However, the Fitts model does not account for changing stimuli and different strategies.
-We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
-This seems to indicate a speed/accuracy trade-off in finding the targets.
-With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
+\begin{highlighted}
+Since Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
+Indeed, this seems to be the case, with the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
+This trend continues in the time-to-target results obtained with the Fitts model analysis, where the \textit{med} setting gave the marginally highest level of performance in Group \textit{G1} and \textit{hi} for Group \textit{G2}.
+However, the improvement of the latter settings are far clearer in Group \textit{G2} than for \textit{G1}.
+Indeed, Group \textit{G2} seems to respond better to the increased movement resolution that the \textit{hi} affords the use, allowing for finer adjustments to be made to the device's orientation to get closer to the target.
+With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. 
+\end{highlighted}
+%However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
+%Since Fitts's model takes the angular error into account, one might reasonably expect that the results for both experiments follow a similar trend. 
+%However, the Fitts model does not account for changing stimuli and different strategies.
+%We therefore hypothesise that the reason for this divergence in performance is due to the increased resolution of the \textit{hi} setting, which allows for finer adjustments of the device's orientation, getting it closer to the correct target, but at the cost of a higher average time-to-target.
+%This seems to indicate a speed/accuracy trade-off in finding the targets.
+%With the Fitts model discussed here, we can modify the interface to prioritise different metrics and produce the correct output.
 

### 2020-05-13 review/response/response.tex
Edits to review rebuttal

@@
 \begin{itemize}
-  \item \textit{In particular, the claim that "...both haptic and vocal feedback can present a cognitive burden and overwhelm a user’s input bandwidth, particularly when high-resolution guidance is required." needs to be clarified.
+  \item R1.1 \textit{However, the paper should be thoroughly proofread as there are a number of typos}
+  \item[] Thank you for pointing these out. We have proofread the paper and amended all typos.
+
+  \item R1.2 \textit{The references are generally appropriate.
+However, additional details on the problem and literature references would be useful (a number of seminal, updated and novel works are below).
+In particular, the claim that "...both haptic and vocal feedback can present a cognitive burden and overwhelm a user’s input bandwidth, particularly when high-resolution guidance is required." needs to be clarified.
       In essence, as suggested in [kammoun2012navigation,petrie1997mobic], there are two synergic classes of information to be conveyed: directions (or macro-navigation), which is commonly conveyed through turn-by-turn instructions (e.g., [sato2019navcog3]), and space-related information (or micro-navigation), which is better conveyed through spatialized audio.
@@
 }
-  \item[] \noindent To address these concerns, we have added additional information to the introduction section that frames this as a micro-navigation task.
+  \item[] Thank you for the suggestions.
+    To address these concerns, we have added additional information to the Introduction (Section 1) that frames this as a micro-navigation task.
     We have also added an additional reference at the line in question to support our argument for not using constant vocal or haptic feedback such a micro-navigation task context.
-    We also added a number of the works the reviewer kindly provided in the previous work section and throughout the rest of the paper.
+    We also added the works the reviewer kindly provided in the Previous Work (Section 2).
 
-  \item \textit{While the amount of novel content seems to be appropriate for a journal extension of the paper, the system description is copied verbatim from the previous paper, and Figures 1b, 2 and 3 are essentially identical.
+  \item R1.3 \textit{The authors published an initial paper on the system.
+With respect to that paper, here the experiments are extended, including also an analysis of the time-to-target fitting with respect to Fitts's Law.
+    While the amount of novel content seems to be appropriate for a journal extension of the paper, the system description is copied verbatim from the previous paper, and Figures 1b, 2 and 3 are essentially identical.
 Content provided elsewhere should be summarized and readapted and not copied.}
-  \item []We have completely rewritten the system description section and further modified the figures in question.
+  \item[] Thank you for pointing this out.
+    To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question.
 
-  \item \textit{However, there is one critical issue.
+  \item R1.4 \textit{The work is generally technically sound.
+However, there is one critical issue.
 The paper states: "..differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation...
@@
     This statement is not valid. Difference testing detects difference, but the absence of statistically significant difference does not imply similarity. For that equivalence testing is needed.}
-  \item[] This is addressed in section 5.3, where we confirm the statistical similarity with a Kolmogorov-Smirnov 2-sample test.
+  \item[] Thank you for pointing out this error.
+    This is addressed in Section 5.3, where we confirm the statistical similarity between the 2 groups with a 2-sample Kolmogorov-Smirnov test. 
+    These results are listed in Table 2.
 
-  \item \textit{Another important consideration that should be discussed is the high variance in the results of the participants with visual impairments.
+  \item R1.5 \textit{Another important consideration that should be discussed is the high variance in the results of the participants with visual impairments.
 As the authors suggest, this might be an artifact due to a lower number of participants.
@@
 As the number of visually impaired participants is low, I suggest adding a table presenting participants' demographic characteristics (age, impairment, onset, navigation expertise....)}
-  \item[] This is a valid point. In Section 4.4 we have added additional information regarding the distributions of the participants' age, sex, age of impairment onset and level of impairment.
+  \item[] We thank the reviewer for this helpful suggestion.
+    To address this, we added in Section 4.4 additional demographic information regarding the distributions of the participants' age, sex, age of impairment onset and level of impairment.
+    This is summarised in Table meme
+
+  \item R1.6 \textit{The main result of the work is quite original and the contribution is timely as a lot of the work in the field is currently being done}
+  \item[] We'd thank the reviewer for this kind comment.
+
 \end{itemize}
@@
 
-  \item \textit{While I have reservations about using Fitts's Law in this paper, probably the single best citation for the justification for using We is:
-Zhai, S., Kong, J., \& Ren, X.
-(2004).
-Speed–accuracy tradeoff in Fitts' law tasks—on the equivalency of actual and nominal pointing precision.
-International journal of human-computer studies, 61(6), 823-856.
-      Also not all that critical given my reservations, but JFYI. In two-dimensional directed pointing, the calculation of We is better calculated as described in:
-    Jacob O.
-Wobbrock, Kristen Shinohara, and Alex Jansen.
-2011.
-The effects of task dimensionality, endpoint deviation, throughput calculation, and experiment design on pointing measures and models.
-In Proceedings of the SIGCHI Conference on Human Factors in Computing Systems (CHI '11).
-Association for Computing Machinery, New York, NY, USA, 1639–1648.}
-  \item[] These are indeed helpful references.
-We have integrated both into the paper, and the latter suggested method of calculating $w_e$ was used to generate the updated figure 11 and 12.
-This seemed to have generated a better fitting model, which led to improved correlation scores in section 5.4 and indices of performance in table 3.
+  \item R2.1 \textit{The authors might make mention of the Microsoft Soundscape system.
+While this system does not provide information about elevation, it is an example of a commercially available navigation aid that uses spatialized audio.
+https://www.microsoft.com/en-us/research/product/soundscape/.
+While I have reservations about using Fitts’s Law in this paper, probably the single best citation for the justification for using We is [zhai2004].
+Also not all that critical given my reservations, but JFYI.
+In two-dimensional directed pointing, the calculation of We is better calculated as described in [wobbrock2011]}
+  \item[] We'd like to thank the reviewer for these helpful references. 
+    We have added the reference from~\cite{zhai2004speed}, as well as a paper by~\cite{kabbash1995prince}, in Section 4.3 to support our use of $w_e$ in this work.
+    We have also revised the way we calculate $w_e$ based on the recommendations from the reviewer and~\cite{wobbrock2011effects} recommendations and made mention of this in Section 4.3. 
+    These changes have led to modifications to Fig. 11 and 12 and have improved the overall model fit.
+    The updated results are discussed in Sections 5.4 and 5.5. and Table 3.
 
-  \item \textit{First, while it is good that the authors included visually impaired individuals in the study, it is hard to know what to make of the differences in performance (and patterns of performance) between the two groups.
+  \item R2.2 \textit{First, while it is good that the authors included visually impaired individuals in the study, it is hard to know what to make of the differences in performance (and patterns of performance) between the two groups.
 Since the whole point of the study is to inform a system intended to be used by visually impaired individuals, how should we interpret this?
@@
 Because the behavior of the two groups is so different, these really need to be separated.}
-  \item We acknowledge that the small sample size is not ideal.
-    However, we attempted to alleviate concerns and make the results more robust by adding the statistical difference and similarity tests between the 2 groups.
-    These confirm that, at least statistically, the 2 groups performed similarly.
-    Our intention is that this is interpreted that if we repeat the experiment with another group of participants with visual impairments (perhaps a younger group with more experience with mobile devices and electronic navigation aids), we may collect results that fall closer to that of the blindfolded group.
-    The reviewer is correct in pointing out that the demographics for each group need to be separated and this was done in Section 4.4.
-    We also added observations in the Discussion section to hypothesise on the difference in mean demographics between the 2 groups may also have influenced the performance we recorded.
+  \item[] We'd like to thank the reviewer for pointing this out. 
+    We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table meme. 
+    We have also added comments in Section 5.3 to point out that these underlying demographic differences may be the cause of the divergences between the groups.  
+    Furthermore, we added an additional Kolmogorov-Smirnov test in Section 5.3 to show the statistical similarity between the groups' results, which we hope alleviates concerns about robustness.
 
-  \item \textit{Because the targets in this task are point targets, there is no W, so the authors used the spread of hits around the target to manufacture an effective width We.
+  \item R2.3 \textit{[...]Because the targets in this task are point targets, there is no W, so the authors used the spread of hits around the target to manufacture an effective width We.
 The problem with this is that the whole concept of We (from Crossman and then later Welford) *assumes that participants have some level of W that they are targeting*.
 Without this, there is no external feedback as to whether a user has actually hit the target or not—it’s just their own subjective sense.
-That is, “accuracy” in this case is essentially determined by the average subjective impression of individual participants (i.e., “this seems right to me… click!”).
-And, as seen in Fig 8, there are huge differences in the distribution of “error” between the two groups (G1 \& G2), and I suspect there may be even larger differences between users: different thresholds of “good enough” for different users.
-It’s also not clear to me if We is calculated for each level of Distance, or is it calculated across multiple amplitude of movements?
-    So my skepticism of the whole exercise of using Fitts’s Law for comparing these conditions is that it feels weird to me to reconstitute some form of W (We) from the spread of hits around a point target when there’s no objective feedback for hitting it (i.e., no W).
+That is, ``accuracy'' in this case is essentially determined by the average subjective impression of individual participants (i.e., ``this seems right to me...click!'').
+}
+  \item[] Thank you for their insight.
+    Firstly, we neglected to mention this in the text, but the targets were coded to have a 10cm radius, i.e.
+the 512Hz tone was emitted when the camera was within 10cm of the target centre (we have added this detail in Section 4.3).
+    The frequency response plot in in Fig 2b has been adjusted to reflect this pseudo target width.
+    This made the search process somewhat similar to the work by~\cite{kabbash1995prince}, who showed that searching for a point-target with an oversized cursor (analogous to the 10cm radius `searchlight' cursor in our case) is comparable to a normal Fitts-task with a target of known width being searched for with a point-cursor.
+    Furthermore, we were not able to explicitly inform a user when they were within 10cm, because the goal of these experiments is mainly to determine the subjective impressions (as the reviewer put it) we can expect from a participant given some audio parameters.
+    We have added text in Section 4.3 to point this out more explicitly and also point out that these experiments are at least conceptually similar to those that have been shown to be Fitts's Law-compliant by citing relevant litature.
+
+  \item R2.4 \textit{And, as seen in Fig 8, there are huge differences in the distribution of ``error'' between the two groups (G1 \& G2), and I suspect there may be even larger differences between users: different thresholds of ``good enough'' for different users.
+It’s also not clear to me if We is calculated for each level of Distance, or is it calculated across multiple amplitude of movements?}
+  \item[] As mentioned in R2.3, the thresholds of `good enough' is this experiment's measurement.
+    However, to address the reviewer's concerns and clarify our method, we have added additional details in Section 4.3 of how we determined $w_e$ and use it to determine a setting's expected performance.
+    In summary, we calculated a $w_e$ for each participant's experiment run and used the median of all the participants to fit the curves in Fig 11 and generate the $IP$ in Fig 12.
+
+  \item R2.5 \textit{So my skepticism of the whole exercise of using Fitts’s Law for comparing these conditions is that it feels weird to me to reconstitute some form of W (We) from the spread of hits around a point target when there’s no objective feedback for hitting it (i.e., no W).
 Since they mostly just use this to make comparisons between different elevation stimuli, it’s not clear that they NEED to do this anyway.
@@
 Indeed, for the final take-aways that the authors provide, this seems like enormous overkill.}
-  \item[] We understand the reviewer's concerns regarding the use of Fitts's Law with an experiment where the targets have no physical width and have to rely on their own subjective senses to determine where the target was placed.
-    Indeed, as the reviewer points out, every participant will have their own opinion on where the target is truly located.
-    The primary goal of this work is precisely to measure this difference, i.e. given some spatialised audio signal, how well does it convey a target location to a new user?
-    For this reason, we could not provide the participants with any more information to more objectively give the target's location (e.g. a second audio tone).
-    Since we did not do this in our experiments, Fitts's Law does not seem an appropriate model here. 
-    However, we respectfully disagree with this assertion for 2 reasons.
-    Firstly, we did not specify this in the text, but the app was coded such that it played back the 512Hz on-target tone when a participant was within 10cm of the target centre, effectively giving it a width (this information has been added in section 4.3).
-    This search is then similar to the work on the Prince method by~\cite{kabbash1995prince}, who showed that searching for a point-target with an oversized cursor (a 10cm radius 'searchlight' cursor in our case) is comparable to a normal Fitts-task with a target of known width being searched for with a point-cursor.
-    We refrained from using this 10cm radius as a target, given the subjective nature of the participants' estimates and opted to use the more conservative $w_e$ we calculated instead, which we found to be approximately 10\% higher for each participant.
-    We calculated the $w_e$ for each participant and setting to generate the plots in fig 11 and used the medians across the participants to generate the IPs for each setting.
-    For full transparency, we included the $w_e$ we calculated in the text.
-    Secondly, despite the experiment's apparent non-conformance to Fitts's requirements, it still provides a fairly robust fit for the movement data we recorded for both groups, which in and of itself is interesting given the significant performance differences between the two groups.
-    This latter point leads to the reviewer's other major concern, which is that using Fitts's Law for this work 'seems like enormous overkill'.
-    From the surface, tend to agree, but provided more context, we believe the reviewer will agree that there is logical reasoning for using Fitts here beyond the additional keywords.
-    This work forms part of a larger project where we initially looked into ways to create an interface for a guidance system that can autonomously adapt its own internal parameters to better match the user's limitations and capabilities, thereby boost overall guidance and target finding performance.
-  For this optimisation process, we needed a metric we can use to measure performance for different parameter settings to determine the effectiveness of a parameter adjustment.
-  This is why Fitts's Law came to mind: it provided a robust unifying metric between search time and accuracy.
-  At the time of writing, it was unclear whether Fitts is applicable to our interface and for this reason we sought to determine whether there such a relationship does indeed manifest itself.
-  Furthermore, any data we can collect on the expected perception limitations and abilities of the general population will enable us to select a good 'default' setting to start the optimisation from, as well as keep the parameters bounded to some effective range.
-  The characterisation experiments we conducted was to address the latter point.
-  These results provide us a) with a good metric to judge whether adjustments to the interface parameters increase performance and b) provide us with a 'good' starting point to start the optimisation process for a new user.
-  We opted to not include these details, since it is not directly pertinent to this work and did not wish to bog down the reader in details of work that is still in progress.
-  However, we agree that some additional detail will make the reasoning a bit clearer and alleviate some confusion on why we even bothered with Fitts's Law.
-  These details were added to the Introduction section and we also modified the terminology to not imply that we found an adherence to Fitts's Law, but rather an observation of a Fitts-like relationship.
-  We sincerely hope that these clarifications and modifications to the text address the reviewers concerns about us using Fitts's Law for these experiments.
+  \item[] We'd like to thank the reviewer for this feedback.
+    To address these concerns, we have added text in Section 1, where additional context behind the reason for these experiments and how their results will be used is provided. 
+    In summary, for this project we were looking into ways to automate an optimisation process where an audio interface changes its own audio parameters to boost the user's target-finding performance.
+    For this, we required a robust model that can provide a quantifiable measure of performance (Fitts Index of Performance).
+    At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
+    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface 'exhibits a response that is well-modelled by Fitts’s Law'n instead of 'conforms to Fitts' Law'.
 
-  \item \textit{To my mind, the paper is a bit of an “LPU” (least-publishable-unit), for a larger, more interesting project (which I would love to see!).
+  \item R2.6 \textit{I suspect that the authors want to engage in this whole Fitts’s exercise in order to tie the work more closely to the wider HCI pointing literature.
+However, if the authors really wanted to use Fitts’s Law for this task, there is certainly precedent in the Marentakis \& Brewster, 2006 paper that they cite.
+Here, researchers used a second audio signal to indicate that a target was acquired.
+    All the above notwithstanding, I’m not certain that this is *wrong* for the purposes they use here, it’s just very non-standard and violates much of the basic theory behind Fitts’s Law.
+So I don’t see this as a completely fatal flaw, but the authors would definitely need to modify the manuscript to address these issues if they want to engage with the Fitts’s Law discourse.}
+  \item We appreciate this feedback.
+    As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target postilion estimation error.
+    However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system.
+    Regarding Fitts's Law not being used correctly in this work, we hope that the points in R2.3-2.4 sufficiently address the reviewer's concerns.
+
+  \item R2.7 \textit{To my mind, the paper is a bit of an ``LPU'' (least-publishable-unit), for a larger, more interesting project (which I would love to see!).
 The specific contribution here is in the use of a pitch gradient for conveying elevation information for spatialized 3D audio as well as a user study evaluating its effectiveness and some of the design space (three different pitch gradients).
@@
 That is, I would say the contribution is not commensurate with the length of the paper.}
-  \item[] On this front, we again have to respectfully disagree with the reviewer's opinion.
-    We pointed out in the previous work section that researchers have implemented different combinations of spatialised sound, frequency adjustments and headphones in their navigation systems for people with visual impairment with different levels of success.
-    However, to our knowledge, very little work has been done in quantifying these spatialised audio signals with varying pitch gains with a significant number of participants with or without visual impairments, as well as bone-conduction headphones.
-    Indeed, we believe that the experiment design, analysis and scale is a fairly novel contribution to other researchers that wish to know what level of perception they can expect from audio signals played back via bone-conduction headphones.
-    It is not our intention to minimise the work to an 'LPU' and indeed, this paper represents a phase of work that was completed for a larger overall project.
-    However, in our opinion it would be detrimental to the message we'd like to publish to the scientific community if we include too much detail on the overall project and bog the reader down in details that are not pertinent to this publication.
+  \item[] Thank you for this helpful feedback.
+    We recognise and respect the reviewer's opinion on this point.
+    However, we think that the paper contains enough contributory work to justify its publication for a couple of reasons.
+    Firstly, the experiments with a sizable sample of both partially-sighted blindfolded individuals provides compelling results on the expected accuracy of a modified spatialised audio signal played via bone-conduction headphones.
+    Indeed, it adds to a relatively sparse body of knowledge on the matter.
+    Furthermore, while not necessarily strictly proving conformance to Fitts's Law, we do show a consistent and reasonably strong fit for a non-visual search task with an audio interface with both partially-sighted and blindfolded individuals that, in our opinion, is interesting and merits further exploration.
 
@@
 \begin{itemize}
-  \item \textit{The contents in Fig.
+  \item R3.1 \textit{The experimental design and study are new and reasonable.
+The paper can be improved by addressing the following concerns.
+The contents in Fig.
 6 and Fig.
@@
 Explain this threshold more clearly.}
+  \item[] Thank you for this suggestion.
+    We added text in Section 5.2 that explains that we used a linear scale in Figure 7 to highlight the separation between the 3 settings, which was not as clearly evident with the logarithmic semitone scale.
+    We also added text that explains that the median cut-offs in both figures are the same.
 
-  \item[] We used a linear scale in Figure 7 to highlight the separation between the 3 settings, which was not as clearly evident with the logarithmic semitone scale.
-    This has been clarified in section 5.2.
-
-  \item \textit{The contents in Fig 5 and Fig.
+  \item R3.2 \textit{The contents in Fig 5 and Fig.
 6 are confusing.
@@
 1.0-2.0.}
-  \item[] Given the progressive difficulty process we used, the tones became increasingly more difficult to distinguish from one another, i.e.
-small frequency difference represented by a small semitone and Hz difference.
-    In Fig 6, it shows the threshold where 75\% of the correct guesses lie to the right, i.e. the larger semitone differences that are easier to distinguish.
+  \item[] Thank you for indicating this point.
+    To clarify confusion, we added text in Section 5.2 where we indicate that the progressive difficulty process does indeed make the pitches more difficult to distinguish as the participant progresses towards the centre, which would increase the proportion of incorrect guesses as they progress towards the centre.
+    We also clarified in the text that the threshold in Fig.
+6 contains 75\% is set conservatively such that it contains the easiest to distinguish tones first, i.e.\ moving from the largest semitone differences to the lowest.
+    Therefore, the threshold will likely be located closer to the 0.0-0.5 range than the 1.0-2.0.
 
-  \item \textit{Before equation (3), the authors claim the targets have no width.
+  \item R3.3 \textit{Before equation (3), the authors claim the targets have no width.
 So does it mean that the virtual objects are actually a virtual point randomly created in the Tango’s screen?
 Since the Tango has an RGB-D camera to measure both direction and distance, a more practical experiment design should use the real daily objects.}
-  \item[] This is correct, we use virtual targets generated by the Tango.
-    We opted for this setup over physical targets, since piratically it was advantageous and allowed us to easily place many targets at a variety of random locations while still knowing precisely where the targets are generated, since they are all located relative to the Tango's frame of reference.
-    For these pointing experiments, it was sufficient, but in a larger-scale experiment with a real object search system, real objects would indeed make more sense than virtual ones.
+  \item[] Thank you for pointing this out.
+    In Section 4.1, we now explain that virtual targets were convenient for these experiments, given that we didn't need to move any physical targets ourselves.
+    We also add that in an experiment with a real navigation system, the virtual targets will be replaced with real objects and targets.
 
-  \item \textit{Improve the resolution of Fig. 8 to make it more clear.}
+  \item R3.4 \textit{Improve the resolution of Fig. 8 to make it more clear.}
   \item[] Fig 8 has been updated with this change. 

### 2020-05-13 paper.tex
Edits to review rebuttal

@@
 
+Even though the Tango is able to detect distances to object, we opted to use virtual targets given the added ability to place targets at any random location without physical manipulation while without losing the ability to determine its exact position relative to the device.
+When this interface is used with a real navigation system, it will be extended to work with real targets.
+
 \begin{figure}
@@
 \noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
-\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, the on-target tone was emitted.
+\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
 This is similar to the work by~\citet{kabbash1995prince}, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
@@
 The results of the pitch discrimination experiment are shown in \cref{fig:pitch-discrimination}, where bar plots are used to show the proportion of correct to incorrect guesses of which tone was higher pitched for different tone difference intervals.
-For Group~\textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and, as expected, the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.
+For Group~\textit{G1}, we see that their guesses are normally spread around the 0 semitone-difference interval and the highest proportion of incorrect guesses occurs in the $[-0.25, 0.25]$ semitone-difference interval.
 The guesses from Group~\textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.
+\hl{The concentration of incorrect guesses around the centre is expected, given the experiment process's progressive increase in difficulty.}
 
 Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
-We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
+We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses starting from the easiest to distinguish tones with large frequency differences, to the hardest to distinguish with the smallest differences.
 The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
 It can also be used to improve the interface's frequency profile and performance. 
-\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group.
+\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be 0.29 for Group \textit{G1} and 0.35 for Group \textit{G2}.
 
@@
 However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
-The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test, where none of the $p$-values are significant.
+The similarity between the distributions is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test, where none of the $p$-values are significant.
 The $p$-values for this test are also listed in~\cref{tab:inter-group-results}.

### 2020-05-13 review/response/response.tex
Added extra references

@@
     Furthermore, we were not able to explicitly inform a user when they were within 10cm, because the goal of these experiments is mainly to determine the subjective impressions (as the reviewer put it) we can expect from a participant given some audio parameters.
-    We have added text in Section 4.3 to point this out more explicitly and also point out that these experiments are at least conceptually similar to those that have been shown to be Fitts's Law-compliant by citing relevant litature.
+    We have added text in Section 4.3 to point this out more explicitly and also point out that these experiments are at least conceptually similar to those that have been shown to be Fitts's Law-compliant by citing relevant literature.
 
@@
   \item We appreciate this feedback.
-    As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target postilion estimation error.
+    As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target position estimation error.
     However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system.

### 2020-05-13 paper.tex
Added extra references

@@
 \usepackage[most]{tcolorbox}
+%\usepackage{soul}
+%\usepackage{color}
 \usepackage{todonotes}
 
-\newcommand\hl[1]{\colorbox{yellow}{\textcolor{black}{#1}}}
-\newcommand\hlbreakable[1]{\textcolor{red}{#1}}
+%\newcommand\hl[1]{\colorbox{yellow}{\textcolor{black}{#1}}}
+\newcommand\hl[1]{\textcolor{red}{#1}}
+%\newcommand\hl[1]{{\sethlcolor{yellow}\hl{#1}}}
 \newtcolorbox{highlighted}{colback=yellow,coltext=black,breakable}
-
+%\newcommand\hl[1]{%
+  %\bgroup
+  %\hskip0pt\color{yellow!80!black}%
+  %#1%
+  %\egroup
+%}
+%\sethlcolor{yellow}
 \citestyle{acmauthoryear}
@@
   We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
-  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
+  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law (a predictive model for human movement) can be used to generate a metric to improve and refine the quality of the audio interface in future mobile navigation aids.
 \end{abstract}
@@
 
-\begin{highlighted}The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
-Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
+\hl{The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
+Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance, are exploited to make this system possible.
 In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
-However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
-The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the advantages and limitations of its main user.
+However, in the literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a target location.
+The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the user's strengths and limitations.
 In previous work we developed a prototype guidance system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention~\citep{lock2019active}.
-However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that will possibly benefit the user experience and boost long-term navigation performance.
-\end{highlighted}
-
-%This project aims to build an indoor mobile navigation aid for people with vision impairments that can guide them to their destination in the final part of their journey, addressing the so-called `last 10-yard problem'.
-%Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance increases are exploited to make this system possible.
-%In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
-%However, in literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a certain point.
+However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that could benefit the user experience and boost long-term navigation performance.}
 
@@
 The system generates guidance instructions that can be interpreted in real-time with minimal additional cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
-By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
+By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from any arbitrary location.
 In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
@@
 We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
-In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
+In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a level of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
 These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
@@
 
-\begin{highlighted}
-Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
-The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings.
+\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
+  The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}.
 Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
@@
 Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
-This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.
-\end{highlighted}
+This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.}
 %Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
@@
 Work has been done in an attempt to spatialise these tones with a head-related transfer function (HRTF) that simulates a sound source being placed at some arbitrary 3D position.
-The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
+The authors generally report favourable results when using normal over-ear headphones or speakers~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized,presti2019watchout,crispien1994guib}.
 However, the audio transmission device used has a significant effect on performance.
-Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization}.
-However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
+Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization,voong2019auditory,mascetti2016sonification}.
+However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization,pec2008individual}.
 Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
@@
 
-\begin{highlighted}
-Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
+\hl{Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
 To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
-This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
+This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.}
 
-People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
+\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
 We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities.
@@
 The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected.
-These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance. 
-\end{highlighted}
+These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}
 
@@
 
-\begin{highlighted}
-Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
+\hl{Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
 These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences , ITD and ILD respectively) and monaural cues, where a cue is extracted directly from each ear's audio signal (e.g.\ the spectral profile, audio intensity).
@@
 An HRTF is a mathematical function that simulates a human head and ear's response to an external sound and is derived by capturing key characteristics that affect the monaural and binaural responses at the user's ear, such as the hearing level and anatomy.
-An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.
+An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.}
 
-The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
+\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
 Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}.
@@
 Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
-This interface was implemented and evaluated in~\citet{lock2019bone}.
-\end{highlighted}
+This interface was implemented and evaluated in~\citet{lock2019bone}.}
 
@@
 
-\begin{highlighted}
-To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
+\hl{To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
 For example, a sound placed at a person's right will hit their right ear first with a slightly higher volume compared to the left ear.
@@
 Therefore, in this work a pure sine wave was used, but can easily be replaced with a richer tone once the system's characteristics are better understood. 
-The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.
-%which uses the person and targets' positions as input, and outputs a transformed audio signal.}
-\end{highlighted}
+The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.} %which uses the person and targets' positions as input, and outputs a transformed audio signal.}
 
@@
 
-\begin{highlighted}
-To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
+\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
 When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
@@
 The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}.
+}
 
-The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
+\hl{The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
 These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
@@
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
-In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.
-\end{highlighted}
+In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.}
 
@@
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
-\begin{highlighted}
-Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
+\hl{Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
 It also provides a so-called `index of performance' ($IP$), which can be used to compare the results between the three different configurations used in the experiments.
-Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.
-\end{highlighted}
-
-\todo{mention limitations of Fitts, i.e. zero-width and not playing second tone to confirm target found}
-
-%that we can use as a metric to compare the results between the three configurations.
+Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.}
 
@@
 
-\noindent \hlbreakable{where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with}
+\noindent \hl{where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with}
 
@@
 \noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
-\hlbreakable{The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
-This is similar to the work by~\citet{kabbash1995prince}, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
+\hl{The virtual targets have a programmed radius of approximately} \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
+\hl{This is similar to the work by}~\citet{kabbash1995prince}\hl{, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
 However, the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
 Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
-Previous authors have found this to capture the true performance metrics fairly well~\citep{zhai2004speed}.}
+Previous authors have found this to capture the true performance metrics fairly well}~\citep{zhai2004speed}.
 Fitts's index of performance, $IP$, can then be calculated using
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-\hlbreakable{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
+\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
 Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
@@
 This could indicate that, instead of terminating the experiment as described in \cref{sec:sound_localisation}, there was more switching back and forth between the three central intervals. 
-
-These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy.
-These results are in line previous literature, confirming that humans are very adept at localizing a sound source, particularly in the pan dimension.
+These results show that both participant groups are capable of determining a sound source's location with a reasonable level of consistency and accuracy and are in line previous literature, confirming that humans are very adept at localising a sound source, particularly in the pan dimension~\cite{wersenyi2003localization}.
 
@@
 
-\begin{highlighted}
-For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
+\hl{For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
 Each participant's median tone error for each setting was then plotted alongside the groups' median thresholds and plotted in \cref{fig:pitch-thresholds-hist}.
-These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.
-\end{highlighted}
+These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.}{}
 
@@
 These results are included in \cref{tab:target-results}.
-\hlbreakable{The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.}
+\hl{The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.}
 However, the correlation scores for Group~\textit{G2} are significantly weaker, with a pan angle correlation $r_{pan} \in [0.1, 0.21],~p < 0.03$.
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-\hlbreakable{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
+\hl{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
 Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
@@
 The $p$-values for this test are also listed in~\cref{tab:inter-group-results}.
-\hlbreakable{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
+\hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
 Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
@@
 For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
-\hlbreakable{This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
+\hl{This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
 Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data interval, indicating less consistency in the time-to-target results for participants with severe sight impairments.
@@
 For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{med} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
-\hlbreakable{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{med} setting is significantly different to the \textit{lo} and \textit{hi} settings ($p_{med-lo} < 0.001,~p_{med-hi} < 0.001$).
+\hl{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{med} setting is significantly different to the \textit{lo} and \textit{hi} settings ($p_{med-lo} < 0.001,~p_{med-hi} < 0.001$).
 The \textit{lo} and \textit{hi} settings, instead, are not significantly different from each other ($p_{lo-hi} = 0.11$).
@@
 
-\begin{highlighted}
-Since Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
+\hl{Since Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
 Indeed, this seems to be the case, with the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
@@
 Indeed, Group \textit{G2} seems to respond better to the increased movement resolution that the \textit{hi} affords the use, allowing for finer adjustments to be made to the device's orientation to get closer to the target.
-With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. 
-\end{highlighted}
+With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. }
 %However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.

### 2020-05-15 review/response/response.tex
Updated response, added participant table, adapted figures

@@
 
-\author{JC Lock; G. Cielniak; ID Gilchrist; N Bellotto}
+\author{JC Lock; ID Gilchrist; G. Cielniak; N Bellotto}
 
@@
     This is addressed in Section 5.3, where we confirm the statistical similarity between the 2 groups with a 2-sample Kolmogorov-Smirnov test. 
-    These results are listed in Table 2.
+    These results are listed in Table 3.
 
@@
     To address this, we added in Section 4.4 additional demographic information regarding the distributions of the participants' age, sex, age of impairment onset and level of impairment.
-    This is summarised in Table meme
+    This is summarised in Table 1.
 
@@
     These changes have led to modifications to Fig. 11 and 12 and have improved the overall model fit.
-    The updated results are discussed in Sections 5.4 and 5.5. and Table 3.
+    The updated results are discussed in Sections 5.4 and 5.5. and listed in Table 4.
 
@@
   \item[] We'd like to thank the reviewer for pointing this out. 
-    We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table meme. 
+    We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table 1. 
     We have also added comments in Section 5.3 to point out that these underlying demographic differences may be the cause of the divergences between the groups.  
@@
     For this, we required a robust model that can provide a quantifiable measure of performance (Fitts Index of Performance).
-    At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
-    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface 'exhibits a response that is well-modelled by Fitts’s Law'n instead of 'conforms to Fitts' Law'.
+    %At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
+    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts' Law'.
 
@@
 So I don’t see this as a completely fatal flaw, but the authors would definitely need to modify the manuscript to address these issues if they want to engage with the Fitts’s Law discourse.}
-  \item We appreciate this feedback.
+  \item[] We appreciate this feedback.
     As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target position estimation error.
-    However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system.
+    However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system and we make mention of this in the concluding lines.
     Regarding Fitts's Law not being used correctly in this work, we hope that the points in R2.3-2.4 sufficiently address the reviewer's concerns.
@@
     Indeed, it adds to a relatively sparse body of knowledge on the matter.
-    Furthermore, while not necessarily strictly proving conformance to Fitts's Law, we do show a consistent and reasonably strong fit for a non-visual search task with an audio interface with both partially-sighted and blindfolded individuals that, in our opinion, is interesting and merits further exploration.
+    Furthermore, while not necessarily strictly proving conformance to Fitts's Law, we do show a consistent and reasonably strong fit for a non-visual search task with an audio interface with both partially-sighted and blindfolded individuals that, in our opinion, is interesting and merits publication.
 

### 2020-05-15 paper.tex
Updated response, added participant table, adapted figures

@@
 
-The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:tango-headphone}).
+The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:participant}).
 This Tango device uses a set of embedded RGB-D cameras and other hardware and software components to provide accurate real-time localisation estimates and has powerful image-processing capabilities.
@@
   \centering
-  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
-~
-  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
-  \caption{A Tango tablet and bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).
-Adapted from~\citet{lock2019bone}.}
+  %\subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
+%~
+  %\subfloat[]{\label{fig:participant}\includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}}
+  \includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}
+  \caption{The Tango tablet and bone-conduction headphones in use during an experiment.
+The angle reference system that the guidance instructions are based on is also included , showing the camera vector, $C$, and the pan and elevation angles to the target.
+Adapted from~\citet{lock2019bone}.}\label{fig:participant}
   \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
@@
 Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
-The AfterShockz headphones (\cref{fig:tango-headphone}) were ultimately selected.
+The AfterShockz headphones (\cref{fig:participant}) were ultimately selected.
 These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}
@@
 
-\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:cam-coords}).
+\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:participant}).
 Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}.
@@
   \centering
-  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
-~
-  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
-  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right).
+  %\subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
+%~
+  %\subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
+  \includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}
+  \caption{A plot depicting the pitch gain function used to convey the target's elevation angle.
 Note the logarithmic scale of the frequency axis.
 Adapted from~\citet{lock2019bone}.
-}
+}\label{fig:pitch-gain}
   \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle.
@@
 
-\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:cam-coords}.
+\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:pitch-gain}.
 When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
@@
 
-\hl{The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}), the gradient of which is determined by setting the angle and pitch limits.
+\hl{The pitch is changed as a linear function of the elevation angle, the gradient of which is determined by setting the angle and pitch limits.
 These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
@@
 \begin{equation}
-  \label{eq:fitts-we}
-  w_e = \sqrt{2\pi e}~\sigma = 4.133~\sigma,
+  \label{eq:fitts-we} w_e = \sqrt{2\pi e}~\sigma = 4.133~\sigma,
 \end{equation}
@@
 Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
-Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life and 3 had limited light perception and none reported any significant prior experience with electronic navigation aids.
-}
-None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
+Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life.
+Of these, 3 participants still have limited light perception with no ability to reliably discern shapes and objects. 
+Nevertheless, they were asked to close their eyes during the experiment to. 
+None of the participants reported any significant prior experience with electronic navigation aids and none had any hearing or other disabilities that could have influenced their performance in the experiments.
+These demographics are summarised in \cref{tab:demographics}.}
 Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}.
@@
 Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.
+
+\begin{table}
+  \centering
+  \caption{}\label{tab:demographics}
+  \begin{tabular}{p{2.7cm}p{1.8cm}p{6cm}}
+    \toprule
+                                 & Group \textit{G1} & Group \textit{G2} \\\midrule
+    Gender [M/F]                 & 10/32    & 7/3 \\
+    Age [years]                  & $20\pm2$ & $61\pm17$ \\
+    Degrees of Vision Impairment & N/A      & 3 totally blind, 7 severely sight impaired (3 with very limited light perception) \\
+    Experience with ETAs         & None     & None \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
-The similarity between the distributions is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test, where none of the $p$-values are significant.
-The $p$-values for this test are also listed in~\cref{tab:inter-group-results}.
+The similarity between the distributions is further highlighted by a two-sample Kolmogorov-Smirnov test (the $p$-values are listed in~\cref{tab:inter-group-results}).
 \hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
@@
 Indeed, the work by~\citet{gallina2015progressive} may serve as a good guideline for such a system.
-Additional feedback modes may also be added to allow for clearer guidance experience for the user, e.g.\ vibration signals to inform them when they point to the target or adjusting the volume to expand the system to three dimensions.
-With this kind of audio interface now better understood, it is ready to be implemented into a fully packaged guidance system for people with visual impairments.
+Additional feedback modes may also be added to allow for a clearer guidance experience for the user, e.g.\ vibration signals or another tone~\citep{marentakis2006effects}, to explicitly inform them when they are pointing to the target or by adjusting the volume to expand the system to three dimensions.
+With this kind of audio interface now better understood, it is ready to be implemented into a fully implemented guidance system for people with visual impairments.
 

### 2020-05-15 review/response/response.tex
Updated response, added participant table, adapted figures
Minor changes to figure 1

@@
 
-\author{JC Lock; ID Gilchrist; G. Cielniak; N Bellotto}
+\author{J.C. Lock; I.D. Gilchrist; G. Cielniak; N. Bellotto}
 
@@
 
-We would first like to sincerely thank you for your honest and helpful feedback on our work.
+We would first like to sincerely thank you all for taking the time for reviewing our work and for your honest and helpful feedback.
 We have taken some time to go over and implement your suggestions and we believe that we can resubmit to you an improved version of the paper. 
@@
   \item[] Thank you for pointing this out.
-    To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question.
+    To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question (see Fig. 1).
 

### 2020-05-15 review/response/response.tex
Fixed American spelling, checked spelling elsewhere

@@
     These changes have led to modifications to Fig. 11 and 12 and have improved the overall model fit.
-    The updated results are discussed in Sections 5.4 and 5.5. and listed in Table 4.
+    The updated results are discussed in Sections 5.4 and 5.5 and listed in Table 4.
 
@@
     %At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
-    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts' Law'.
+    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts's Law'.
 

### 2020-05-15 paper.tex
Updated response, added participant table, adapted figures
Minor changes to figure 1
Fixed American spelling, checked spelling elsewhere

@@
   %\subfloat[]{\label{fig:participant}\includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}}
-  \includegraphics[width=0.8\columnwidth]{figures/vi_participant_e.png}
+  \includegraphics[width=0.65\columnwidth]{figures/vi_participant_e.png}
   \caption{The Tango tablet and bone-conduction headphones in use during an experiment.
@@
 
-\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments to address macro- and micro-navigation issues.
+\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and electronic travel aids (ETA) for people with visual impairments to address macro- and micro-navigation issues.
   The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}.
@@
 For example, the experiment will terminate when one sequence is set to \SI{11.25}{\degree} and the other is between \SI{2.8}{\degree} or \SI{45}{\degree} for three consecutive guesses.
-This gives a distance band where the participant is capable of localizing the sound source.
+This gives a distance band where the participant is capable of localising the sound source.
 Each participant performed this experiment three times.
@@
 In this paper we investigated the use of spatialised audio interface with varying pitch to guide a user with visual impairments in a target pointing task.
-We found that the blindfolded participants and those with severe sight impairments performed similarly in localizing sound sources and differentiating between tones. 
+We found that the blindfolded participants and those with severe sight impairments performed similarly in localising sound sources and differentiating between tones. 
 We also found that both groups were able to find a randomly distributed set of virtual targets with similar levels of accuracy.

### 2020-05-21 paper.tex
Proofreading paper

@@
   We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
-  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law (a predictive model for human movement) can be used to generate a metric to improve and refine the quality of the audio interface in future mobile navigation aids.
+  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law (a predictive model for human movement) provides a suitable a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids.
 \end{abstract}
@@
 In particular, techniques from the active vision field are used to enable a mobile device to gather information on the surrounding environment and use it to generate guidance instructions for a user with limited or no vision.
-However, in the literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if the same techniques can also be used to direct a user's attention to a target location.
-The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the user's strengths and limitations.
+However, in the literature, these techniques are typically limited to directing electro-mechanical servos~\citep{bajcsy2018revisiting} and in this project, we attempt to find out if similar techniques can be used to direct a user's attention to a target location.
+The proposed system was introduced by~\citet{lock2017portable}, who describe the aforementioned autonomous guidance system paired with a co-adaptive human-machine interface that changes its own parameters over time to better match the user's perception strengths and limitations.
 In previous work we developed a prototype guidance system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention~\citep{lock2019active}.
@@
 
-The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:participant}).
+The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conduction headphones (both are shown in \cref{fig:participant}).
 This Tango device uses a set of embedded RGB-D cameras and other hardware and software components to provide accurate real-time localisation estimates and has powerful image-processing capabilities.
 It also gives access to Android's full range of interface and I/O options.
-Unlike normal headphones, bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
+Unlike normal headphones, bone-conduction headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canals.
 These headphones have the benefit of not interfering with a user's normal hearing function.
@@
 \begin{itemize}
-  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's elevation angle when using a mobile device with a bone-conducting headset;
+  \item we provide comprehensive experimental results, with two groups of participants with healthy and limited eyesight, on how well a tone with varying pitch can convey a target's elevation angle when using a mobile device with a bone-conduction headset;
   \item we show that this sound-based human-machine interface exhibits a response that is well-modelled by Fitts's Law which can provide a useful metric of performance for similar mobile user interfaces.
@@
 \hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and electronic travel aids (ETA) for people with visual impairments to address macro- and micro-navigation issues.
-  The latter refer to the scale that navigation takes place on, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}.
+The latter refers to the scale in which navigation takes place, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}.
 Many of the proposed systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation,sato2019navcog}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,kammoun2012navigation} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with macro- and/or micro-guidance instructions, each of which has its own set of features and limitations.
@@
 Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
-This this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the user experience~\citep{klatzky2006cognitive}.}
+In this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the overall user experience~\citep{klatzky2006cognitive}.}
 %Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
 As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
-However, such tones can potentially fatigue a user if there are too unpleasant.
+However, such tones can potentially fatigue a user if they are too unpleasant.
 Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
@@
 However, the audio transmission device used has a significant effect on performance.
-Indeed, research has shown that cheaper headphones and bone-conducting headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization,voong2019auditory,mascetti2016sonification}.
+Indeed, research has shown that cheaper headphones and bone-conduction headphones have diminished performance in location perception with HRTFs when compared to over-ear or other expensive headphones~\citep{stanley2006lateralization,voong2019auditory,mascetti2016sonification}.
 However, this performance degradation seems limited to the elevation dimension, which is drastically improved when the HRTFs are adjusted for the bone-conduction pathway~\citep{stanley2006lateralization,pec2008individual}.
 Another way around the performance issue in the elevation dimension is to transmit the elevation angle by adjusting the audio tone's pitch, such as in the work by~\citet{durette2008visuo}.
-We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}, and found that participants are able to adequately determine a target's elevation with this approach with performance in both pan and elevation dimensions.
+We expanded upon the latter's work and investigated using spatialised audio and a varying pitch for guidance in an initial study~\cite{lock2019bone}, and found that participants are able to adequately determine a target's elevation.
 The measured performance is comparable to those of more expensive and over-ear headphones.
@@
 These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\citep{wu2010fitts}.
-However, Fitts's Law has not yet been shown to apply to a spatial tone that uses varying pitch to convey the target's elevation angle, as demonstrated in this paper.
+\hl{However, it is not clear whether Fitts's Law applies to a spatial tone that uses varying pitch to convey the target's elevation angle, as demonstrated in this paper.}
 
@@
 
-\hl{Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
+\hl{Existing electronic navigation aids have typically struggled to gain significant market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
@@
 
-\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing to can have severe undesirable effects~\citep{lichtenstein2012headphone}.
-We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and therefore does not impede the user's ambient sound perception abilities.
+\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing so can have severe and undesirable effects~\citep{lichtenstein2012headphone}.
+We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and does therefore does not impede the user's ambient sound perception abilities.
 Alternative, open-back headphones were also considered, but it was found that they still interfere with hearing and were therefore disregarded.
-The AfterShockz headphones (\cref{fig:participant}) were ultimately selected.
+The AfterShockz headphones (shown in \cref{fig:participant}) were ultimately selected.
 These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}
@@
 
-\hl{Humans are able to localise sounds in three dimensions by extracting different cues from the audio signal~\citep{blauert1969sound,blauert1997spatial}.
-These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences , ITD and ILD respectively) and monaural cues, where a cue is extracted directly from each ear's audio signal (e.g.\ the spectral profile, audio intensity).
-The ITD and ILD extracted from binaural cues allow a user to localise a sound on the horizontal plane (e.g.\ a sound from the right will hit the right ear before left one), while monaural cues indicate a sound's distance (e.g.
+\hl{Humans are able to localise sounds in three dimensions by extracting different cues from audio signals~\citep{blauert1969sound,blauert1997spatial}.
+These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences), and monaural cues, where a cue is extracted from the signal received at each ear (e.g.\ the spectral profile, audio intensity).
+%Binaural cues allow a user to localise a sound on the horizontal plane (e.g.\ a sound from the right will hit the right ear before left one), while monaural cues indicate a sound's distance (e.g.
 louder sounds appear closer than softer ones) and its position on the vertical plane (e.g.\ the spectral profile generated from the signal hitting the user's body).
@@
 \hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:participant}).
-Spatialised audio is well-suited to this micro-navigation task, displaying accuracy levels comparable to vocal feedback, but with less cognitive load at the high resolution of this task~\citep{klatzky2006cognitive}.
+Spatialised audio is well-suited to this micro-navigation task, displaying accuracy comparable to vocal feedback, but with less cognitive load when used in a high-resolution search task such as this~\citep{klatzky2006cognitive}.
 However, we propose a linear adjustment to the signal's pitch as a function of the elevation angle to overcome the limitations of bone-conduction headphones and spatialised audio stated previously.
@@
 Therefore, in this work a pure sine wave was used, but can easily be replaced with a richer tone once the system's characteristics are better understood. 
-The since was was spatialised using OpenAL's default HRTF , based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.} %which uses the person and targets' positions as input, and outputs a transformed audio signal.}
+The since was was spatialised using OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.} %which uses the person and targets' positions as input, and outputs a transformed audio signal.}
 
@@
 
-\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a linear function of the target's elevation angle, as shown in \cref{fig:pitch-gain}.
+\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a log-linear function of the target's elevation angle, as shown in \cref{fig:pitch-gain}.
 When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
@@
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
-In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\citep{lock2019bone}.}
+In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a signal fully spatialised in the pan and elevation dimensions~\citep{lock2019bone}.}
 
@@
 
-We performed a set of experiments with the audio interface to determine how effective it is at directing a user to adjust the pan and elevation angles of a camera for point it to a target.
+We performed a set of experiments with the audio interface to determine how effective it is at directing a user to adjust the pan and elevation angles of a camera to point it to a target.
 Furthermore, we also carried out a set of pre-screening experiments to determine each participant's hearing characteristics in order to determine their perception limits in the respective audio dimensions.
@@
 
-Even though the Tango is able to detect distances to object, we opted to use virtual targets given the added ability to place targets at any random location without physical manipulation while without losing the ability to determine its exact position relative to the device.
-When this interface is used with a real navigation system, it will be extended to work with real targets.
+\hl{Even though the Tango is able to detect distances to object, we opted to use virtual targets given the added ability to place targets at any random location without physical manipulation without losing the ability to determine its exact position relative to the device.
+When this interface is used with a real navigation system, it will be extended to work with real targets and objects.}
 
@@
 These targets are generated at a constant distance from the participants with pan and elevation angles that are uniformly distributed across the four quadrants to avoid clustering.
-Each target's relative angular position is communicated to the participants in real-time as the device is moved around via the bone-conducting headphones.
+Each target's relative angular position is communicated to the participants in real-time as the device is moved around via the bone-conduction headphones.
 Every time a participant was confident that they were pointing at a target, i.e.\ hearing a signal that is placed at their front at a frequency of \SI{512}{\hertz}, they tapped the device's screen, marking the location and generating a new target.
@@
 It also provides a so-called `index of performance' ($IP$), which can be used to compare the results between the three different configurations used in the experiments.
-Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\cite{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.}
+Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\citet{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.}
 
@@
 
-\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
-\hl{The virtual targets have a programmed radius of approximately} \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
-\hl{This is similar to the work by}~\citet{kabbash1995prince}\hl{, where they had participants search for a point-target with an oversized cursor and found that this was similar to a Fitts-like response.
-However, the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
+\noindent \hl{as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
+The virtual targets have a programmed radius of approximately} \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
+\hl{This is similar to the work by}~\citet{kabbash1995prince}\hl{, where they had participants search for a point-target with an oversized cursor and elicited a Fitts-like response.
+However, in this case the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
 Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$).
-Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$).
+\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$ years).
+Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$ years).
 Of the latter group, 3 are congenitally blind, while the rest were classified as severely sight impaired later in life.
-Of these, 3 participants still have limited light perception with no ability to reliably discern shapes and objects. 
-Nevertheless, they were asked to close their eyes during the experiment to. 
+Of these, 3 participants still have limited light perception with no ability to reliably discern shapes and objects (the rest had no light perception). 
+Nevertheless, they were asked to close their eyes during the experiment. 
 None of the participants reported any significant prior experience with electronic navigation aids and none had any hearing or other disabilities that could have influenced their performance in the experiments.
 These demographics are summarised in \cref{tab:demographics}.}
+
 Each participant performed three sets of experiments each, with the two characterisation experiments in \cref{sec:participant_characterisation} preceding the final target-search experiment in \cref{sec:target_search}.
@@
   \caption{}\label{tab:demographics}
-  \begin{tabular}{p{2.7cm}p{1.8cm}p{6cm}}
+  \begin{tabular}{p{4.5cm}p{1.8cm}p{4cm}}
     \toprule
@@
     Age [years]                  & $20\pm2$ & $61\pm17$ \\
-    Degrees of Vision Impairment & N/A      & 3 totally blind, 7 severely sight impaired (3 with very limited light perception) \\
+    Degree of Vision Impairment  & N/A      & 7 totally blind, 3 with very limited light perception \\
     Experience with ETAs         & None     & None \\
@@
 \hl{For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
-Each participant's median tone error for each setting was then plotted alongside the groups' median thresholds and plotted in \cref{fig:pitch-thresholds-hist}.
+Each participant's median tone error for each setting was then plotted alongside the groups' median thresholds in \cref{fig:pitch-thresholds-hist}.
 These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.}{}
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-\hl{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
+\hl{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile devices.
 Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
@@
 The similarity between the distributions is further highlighted by a two-sample Kolmogorov-Smirnov test (the $p$-values are listed in~\cref{tab:inter-group-results}).
-\hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
+\hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in performance.
 Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
@@
 
-\hl{Since Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
-Indeed, this seems to be the case, with the \textit{hi} pitch setting produces the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
+\hl{Since the Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
+Indeed, this seems to be the case, with the \textit{hi} pitch setting producing the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
 This trend continues in the time-to-target results obtained with the Fitts model analysis, where the \textit{med} setting gave the marginally highest level of performance in Group \textit{G1} and \textit{hi} for Group \textit{G2}.
 However, the improvement of the latter settings are far clearer in Group \textit{G2} than for \textit{G1}.
-Indeed, Group \textit{G2} seems to respond better to the increased movement resolution that the \textit{hi} affords the use, allowing for finer adjustments to be made to the device's orientation to get closer to the target.
+Indeed, Group \textit{G2} seems to respond better to the increased movement resolution that the \textit{hi} affords the user, allowing for finer adjustments to be made to the device's orientation to get closer to the target.
 With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. }

### 2020-05-21 review/response/response.tex
Proofread response

@@
 \documentclass{scrartcl}
+
+\usepackage{hyperref}
 
@@
 }
-  \item[] Thank you for the suggestions.
-    To address these concerns, we have added additional information to the Introduction (Section 1) that frames this as a micro-navigation task.
+  \item[] To address these concerns, we have added additional information to the Introduction (Section 1) that frames this as a micro-navigation task.
     We have also added an additional reference at the line in question to support our argument for not using constant vocal or haptic feedback such a micro-navigation task context.
-    We also added the works the reviewer kindly provided in the Previous Work (Section 2).
+    We also added the works the reviewer kindly provided in the Previous Work section (Section 2).
 
@@
 Content provided elsewhere should be summarized and readapted and not copied.}
-  \item[] Thank you for pointing this out.
-    To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question (see Fig. 1).
+  \item[] To address this, we have completely rewritten the System Description (Section 3) and further modified the figures in question (see Fig. 1).
 
@@
 As the number of visually impaired participants is low, I suggest adding a table presenting participants' demographic characteristics (age, impairment, onset, navigation expertise....)}
-  \item[] We thank the reviewer for this helpful suggestion.
-    To address this, we added in Section 4.4 additional demographic information regarding the distributions of the participants' age, sex, age of impairment onset and level of impairment.
+  \item[] To address this, we added in Section 4.4 additional demographic information regarding the distributions of the participants' age, sex, life period of impairment onset and level of impairment.
     This is summarised in Table 1.
@@
   \item R1.6 \textit{The main result of the work is quite original and the contribution is timely as a lot of the work in the field is currently being done}
-  \item[] We'd thank the reviewer for this kind comment.
+  \item[] We thank the reviewer for this kind comment.
 
@@
 While this system does not provide information about elevation, it is an example of a commercially available navigation aid that uses spatialized audio.
-https://www.microsoft.com/en-us/research/product/soundscape/.
+\url{https://www.microsoft.com/en-us/research/product/soundscape/}.
 While I have reservations about using Fitts’s Law in this paper, probably the single best citation for the justification for using We is [zhai2004].
@@
 Because the behavior of the two groups is so different, these really need to be separated.}
-  \item[] We'd like to thank the reviewer for pointing this out. 
-    We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table 1. 
+  \item[] We have addressed these concerns by reporting the participant demographics separately for each group in Section 4.4 and Table 1. 
     We have also added comments in Section 5.3 to point out that these underlying demographic differences may be the cause of the divergences between the groups.  
@@
 }
-  \item[] Thank you for their insight.
-    Firstly, we neglected to mention this in the text, but the targets were coded to have a 10cm radius, i.e.
+  \item[] Firstly, we neglected to mention this in the text, but the targets were coded to have a 10cm radius, i.e.
 the 512Hz tone was emitted when the camera was within 10cm of the target centre (we have added this detail in Section 4.3).
-    The frequency response plot in in Fig 2b has been adjusted to reflect this pseudo target width.
+    %The frequency response plot in in Fig 2b has been adjusted to reflect this pseudo target width.
     This made the search process somewhat similar to the work by~\cite{kabbash1995prince}, who showed that searching for a point-target with an oversized cursor (analogous to the 10cm radius `searchlight' cursor in our case) is comparable to a normal Fitts-task with a target of known width being searched for with a point-cursor.
-    Furthermore, we were not able to explicitly inform a user when they were within 10cm, because the goal of these experiments is mainly to determine the subjective impressions (as the reviewer put it) we can expect from a participant given some audio parameters.
+    Furthermore, we were not able to explicitly inform a user when they were within 10cm, because the goal of these experiments are firstly to determine the subjective impressions (as the reviewer put it) we can expect from a participant given some audio parameters.
     We have added text in Section 4.3 to point this out more explicitly and also point out that these experiments are at least conceptually similar to those that have been shown to be Fitts's Law-compliant by citing relevant literature.
@@
 Indeed, for the final take-aways that the authors provide, this seems like enormous overkill.}
-  \item[] We'd like to thank the reviewer for this feedback.
-    To address these concerns, we have added text in Section 1, where additional context behind the reason for these experiments and how their results will be used is provided. 
+  \item[] To address these concerns, we have added text in Section 1, where additional context behind the reason for these experiments and how their results will be used is provided. 
     In summary, for this project we were looking into ways to automate an optimisation process where an audio interface changes its own audio parameters to boost the user's target-finding performance.
-    For this, we required a robust model that can provide a quantifiable measure of performance (Fitts Index of Performance).
+    For this, we require a robust model that can provide a quantifiable measure of performance (Fitts Index of Performance).
     %At the time this work was conducted, it was not clear that Fitts's model could provide us with a useful measure based on the literature we had at hand and is the main reason we conducted this analysis.
-    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts's Law'.
+    We acknowledge the reviewer's valid comment about not strictly conforming to the law and we amended the wording in the Introduction (Section 1) and elsewhere to use less absolute language and say that we found that the interface `exhibits a response that is well-modelled by Fitts’s Law'  instead of `conforms to Fitts's Law'.
 
@@
 So I don’t see this as a completely fatal flaw, but the authors would definitely need to modify the manuscript to address these issues if they want to engage with the Fitts’s Law discourse.}
-  \item[] We appreciate this feedback.
-    As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the target position estimation error.
+  \item[] As we mention in R2.3, we could not indicate that the user was on-target any more explicitly than we did, since we would not be able to measure the participants' target position estimation errors.
     However, we agree that from a practical perspective, a more explicit signal (such as the one from~\cite{marentakis2005comparison}) would be advantageous for a real guidance system and we make mention of this in the concluding lines.
@@
 That is, I would say the contribution is not commensurate with the length of the paper.}
-  \item[] Thank you for this helpful feedback.
-    We recognise and respect the reviewer's opinion on this point.
+  \item[] We recognise and respect the reviewer's opinion on this point.
     However, we think that the paper contains enough contributory work to justify its publication for a couple of reasons.
@@
 Explain this threshold more clearly.}
-  \item[] Thank you for this suggestion.
-    We added text in Section 5.2 that explains that we used a linear scale in Figure 7 to highlight the separation between the 3 settings, which was not as clearly evident with the logarithmic semitone scale.
-    We also added text that explains that the median cut-offs in both figures are the same.
+  \item[] We added text in Section 5.2 that explains that we used a linear scale in Figure 7 to highlight the separation between the 3 settings, which was not as clearly evident with the logarithmic semitone scale.
+    We also added text in that section that explains that the median cut-offs in both figures are the same.
 
@@
 Since the Tango has an RGB-D camera to measure both direction and distance, a more practical experiment design should use the real daily objects.}
-  \item[] Thank you for pointing this out.
-    In Section 4.1, we now explain that virtual targets were convenient for these experiments, given that we didn't need to move any physical targets ourselves.
+  \item[] In Section 4.1, we now explain that virtual targets were convenient for these experiments, given that we didn't need to move any physical targets ourselves.
     We also add that in an experiment with a real navigation system, the virtual targets will be replaced with real objects and targets.

### 2020-05-21 paper.tex
Removed hl tags

@@
 \usepackage[most]{tcolorbox}
-%\usepackage{soul}
-%\usepackage{color}
-\usepackage{todonotes}
 
-%\newcommand\hl[1]{\colorbox{yellow}{\textcolor{black}{#1}}}
 \newcommand\hl[1]{\textcolor{red}{#1}}
-%\newcommand\hl[1]{{\sethlcolor{yellow}\hl{#1}}}
-\newtcolorbox{highlighted}{colback=yellow,coltext=black,breakable}
-%\newcommand\hl[1]{%
-  %\bgroup
-  %\hskip0pt\color{yellow!80!black}%
-  %#1%
-  %\egroup
-%}
-%\sethlcolor{yellow}
+
 \citestyle{acmauthoryear}
@@
 
-\hl{The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
+The ActiVis project is an effort to create a fully mobile phone-based navigation aid for people with visual impairments to guide them towards a desired object or location within an unknown indoor environment.
 Improvements to computer vision and machine learning techniques, as well as mobile computing hardware performance, are exploited to make this system possible.
@@
 In previous work we developed a prototype guidance system that uses active vision and machine learning models to gather information and help a person find objects within an unknown indoor environment, showing that these techniques can indeed successfully be applied to direct humans' attention~\citep{lock2019active}.
-However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that could benefit the user experience and boost long-term navigation performance.}
+However, in this work we examine the effectiveness of the proposed interface for a searching task and investigate a metric that can be used in the next phases of the project to enable the aforementioned co-adaptive paradigm that could benefit the user experience and boost long-term navigation performance.
 
@@
 
-\hl{Over the years, commercial and academic groups have devised new and innovative mobile navigation and electronic travel aids (ETA) for people with visual impairments to address macro- and micro-navigation issues.
+Over the years, commercial and academic groups have devised new and innovative mobile navigation and electronic travel aids (ETA) for people with visual impairments to address macro- and micro-navigation issues.
 The latter refers to the scale in which navigation takes place, with macro-navigation addressing directional guidance on a topographical map using turn-by-turn instructions, for example, while micro-navigation focusses on conveying information of the user's immediate surroundings~\citep{petrie1997mobic}.
@@
 Furthermore, in a micro-navigation task, high-resolution guidance and many adjustments are required to reach the target location.
-In this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the overall user experience~\citep{klatzky2006cognitive}.}
+In this regard, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, which could have a detrimental effect on performance and the overall user experience~\citep{klatzky2006cognitive}.
 %Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
@@
 These results have since been supported by other authors, who found that Fitts's Law provided a good explanation for the results from an experiment using visual, limited visual and non-visual feedback cues~\citep{wu2010fitts}.
-\hl{However, it is not clear whether Fitts's Law applies to a spatial tone that uses varying pitch to convey the target's elevation angle, as demonstrated in this paper.}
+However, it is not clear whether Fitts's Law applies to a spatial tone that uses varying pitch to convey the target's elevation angle, as demonstrated in this paper.
 
@@
 
-\hl{Existing electronic navigation aids have typically struggled to gain significant market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
+Existing electronic navigation aids have typically struggled to gain significant market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
 Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
 To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
-This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.}
+This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.
 
-\hl{People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing so can have severe and undesirable effects~\citep{lichtenstein2012headphone}.
+People with visual impairments rely heavily on their hearing~\citep{golledge2004stated} and we wish to avoid blocking this information pathway, since doing so can have severe and undesirable effects~\citep{lichtenstein2012headphone}.
 We therefore use a set of bone-conduction headphones that are placed on a user's cheekbones and conduct audio signals through the skull to the inner ear, completely avoiding the outer ear and does therefore does not impede the user's ambient sound perception abilities.
@@
 The AfterShockz headphones (shown in \cref{fig:participant}) were ultimately selected.
-These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.}
+These headphones have the added benefit of a more discreet form-factor when compared to other over-headphones, thereby addressing the issue of user acceptance.
 
@@
 
-\hl{Humans are able to localise sounds in three dimensions by extracting different cues from audio signals~\citep{blauert1969sound,blauert1997spatial}.
+Humans are able to localise sounds in three dimensions by extracting different cues from audio signals~\citep{blauert1969sound,blauert1997spatial}.
 These include binaural, where the user compares the signals received at both ears (e.g.\ inter-aural time and level differences), and monaural cues, where a cue is extracted from the signal received at each ear (e.g.\ the spectral profile, audio intensity).
@@
 An HRTF is a mathematical function that simulates a human head and ear's response to an external sound and is derived by capturing key characteristics that affect the monaural and binaural responses at the user's ear, such as the hearing level and anatomy.
-An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.}
+An HRTF will produce the most accurate results when it is customised to match a specific user, since each user's hearing response is unique, but this is a complex process and HRTFs generated with average values (head sizes, heights, ear shapes, etc.) produce acceptable results~\citep{gardner1995hrtf}.
 
-\hl{The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:participant}).
+The interface presents the user with guidance instructions in the form of angular adjustments that are required in the pan and elevation dimensions to point a camera at the desired target (see \cref{fig:participant}).
 Spatialised audio is well-suited to this micro-navigation task, displaying accuracy comparable to vocal feedback, but with less cognitive load when used in a high-resolution search task such as this~\citep{klatzky2006cognitive}.
@@
 Indeed, this dimension is unaffected by the use of bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
-This interface was implemented and evaluated in~\citet{lock2019bone}.}
+This interface was implemented and evaluated in~\citet{lock2019bone}.
 
@@
 
-\hl{To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
+To localise a sound on the horizontal plane, the human audition system compares characteristics from the signals received at both ears (binaural cues), such as their volume difference and the time delay between the same sound reaching both ears~\citep{blauert1969sound}.
 For example, a sound placed at a person's right will hit their right ear first with a slightly higher volume compared to the left ear.
@@
 Therefore, in this work a pure sine wave was used, but can easily be replaced with a richer tone once the system's characteristics are better understood. 
-The since was was spatialised using OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.} %which uses the person and targets' positions as input, and outputs a transformed audio signal.}
+The since was was spatialised using OpenAL's default HRTF, based on the MIT's KEMAR dataset~\citep{hiebert2005openal}.
 
@@
 
-\hl{To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a log-linear function of the target's elevation angle, as shown in \cref{fig:pitch-gain}.
+To compensate for the loss of elevation localisation performance when conveying spatialised audio via bone-conduction headphones~\citep{macdonald2006spatial,schonstein2008comparison}, we adjust the sine wave's frequency (i.e.\ audible pitch) as a log-linear function of the target's elevation angle, as shown in \cref{fig:pitch-gain}.
 When the required elevation adjustment is above or below where the camera is currently pointed, the pitch is increased or lowered respectively. 
@@
 The pitch is constantly adjusted and updated at \SI{10}{\hertz} in octave- and semitone-based intervals to ensure perceptible changes, while keeping the tone's timbre constant~\citep{shepard1964circularity}.
-}
 
-\hl{The pitch is changed as a linear function of the elevation angle, the gradient of which is determined by setting the angle and pitch limits.
+The pitch is changed as a linear function of the elevation angle, the gradient of which is determined by setting the angle and pitch limits.
 These limits are set at some number of octaves from the neutral pitch that is emitted when the camera is on-target. 
@@
 For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
-In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a signal fully spatialised in the pan and elevation dimensions~\citep{lock2019bone}.}
+In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a signal fully spatialised in the pan and elevation dimensions~\citep{lock2019bone}.
 
@@
 
-\hl{Even though the Tango is able to detect distances to object, we opted to use virtual targets given the added ability to place targets at any random location without physical manipulation without losing the ability to determine its exact position relative to the device.
-When this interface is used with a real navigation system, it will be extended to work with real targets and objects.}
+Even though the Tango is able to detect distances to object, we opted to use virtual targets given the added ability to place targets at any random location without physical manipulation without losing the ability to determine its exact position relative to the device.
+When this interface is used with a real navigation system, it will be extended to work with real targets and objects.
 
@@
 However, since each participant was presented with a different, randomly generated set of targets, a direct time comparison is not possible.
-\hl{Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
+Instead, we use Fitts's Law~\citep{fitts1954information}, modified by MacKenzie for uncertain target sizes and noisy data~\citep{mackenzie1992fitts}, which states that there is a relation between the time it takes to find a target and its index of difficulty ($ID$, the ratio between the distance to the target and its width).
 It also provides a so-called `index of performance' ($IP$), which can be used to compare the results between the three different configurations used in the experiments.
-Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\citet{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.}
+Furthermore, if a Fitts-like relationship is indeed found, it can be used as an optimisation metric in the co-adaptive interface described by~\citet{lock2017portable}, where interface parameters (e.g.\ pitch gradient, volume setting, etc.) are automatically tweaked in order to maximise target finding performance.
 
@@
 
-\noindent \hl{where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with}
+\noindent where $\sigma$ is the standard deviation of the combined pan and elevation error ($x, y$), calculated with
 
@@
 
-\noindent \hl{as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
-The virtual targets have a programmed radius of approximately} \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
-\hl{This is similar to the work by}~\citet{kabbash1995prince}\hl{, where they had participants search for a point-target with an oversized cursor and elicited a Fitts-like response.
+\noindent as proposed by~\citet{wobbrock2011effects}, taken as the angle between the participant's target selection and target's actual angular position.
+The virtual targets have a programmed radius of approximately \SI{10}{\centi\metre} (equivalent to approximately \SI{0.1}{\radian}) and when the participant pointed the camera within this radius, \SI{512}{\hertz} on-target tone was emitted.
+This is similar to the work by~\citet{kabbash1995prince}, where they had participants search for a point-target with an oversized cursor and elicited a Fitts-like response.
 However, in this case the participants were not explicitly informed when they were within this radius and had to use their own subjective judgement of the audio tone.
 Since the judgement accuracy will vary across different participants, effectively giving different target sizes, it was necessary to use the effective width as an approximation for the actual target size.
-Previous authors have found this to capture the true performance metrics fairly well}~\citep{zhai2004speed}.
+Previous authors have found this to capture the true performance metrics fairly well~\citep{zhai2004speed}.
 Fitts's index of performance, $IP$, can then be calculated using
@@
 Two groups of participants were recruited for the experiments on a volunteer basis. 
-\hl{Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$ years).
+Group~\textit{G1} consisted of 42 undergraduate students (10 male, 32, female) with normal eyesight who were blindfolded for the experiments (mean age: $20\pm2$ years).
 Group \textit{G2} contained 10 people (7 male, 3 female) with severe visual impairments (mean age: $61\pm17$ years).
@@
 None of the participants reported any significant prior experience with electronic navigation aids and none had any hearing or other disabilities that could have influenced their performance in the experiments.
-These demographics are summarised in \cref{tab:demographics}.}
+These demographics are summarised in \cref{tab:demographics}.
 
@@
 The guesses from Group~\textit{G2} are more concentrated around the centre and the majority of incorrect guesses also occurs in the $[-0.25, 0.25]$ semitone-difference interval.
-\hl{The concentration of incorrect guesses around the centre is expected, given the experiment process's progressive increase in difficulty.}
+The concentration of incorrect guesses around the centre is expected, given the experiment process's progressive increase in difficulty.
 
@@
 
-\hl{For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
+For the target search experiment, the pitch differences between the \SI{512}{\hertz} on-target tone and the participants' selected tones were collected and their cut-off threshold were determined in a similar way.
 Each participant's median tone error for each setting was then plotted alongside the groups' median thresholds in \cref{fig:pitch-thresholds-hist}.
-These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.}{}
+These data are plotted on a linear Hertz-based scale instead of a semitone scale to highlight the grouping between the three settings.
 
@@
 These results are included in \cref{tab:target-results}.
-\hl{The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.}
+The Pearson correlation scores for Group~\textit{G1} indicate a moderate to strong positive correlation between the target and the selected locations ($r_{pan} \in [0.72, 0.77],~p < 0.001;~r_{elevation} \in [0.36, 0.49],~p < 0.001$), showing that both the pan and elevation cues in general worked as expected.
 However, the correlation scores for Group~\textit{G2} are significantly weaker, with a pan angle correlation $r_{pan} \in [0.1, 0.21],~p < 0.03$.
@@
 Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting.
-\hl{Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile devices.
+Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile devices.
 Indeed, previous works have suggested that these demographics may have a measurable effect on target-finding performance~\citep{millar1994understanding,pring2008psychological}.
-However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).}
+However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
 The similarity between the distributions is further highlighted by a two-sample Kolmogorov-Smirnov test (the $p$-values are listed in~\cref{tab:inter-group-results}).
-\hl{This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in performance.
+This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in performance.
 Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
@@
 Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.
-}
 
@@
 For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
-\hl{This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
+This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.98,~p_{lo}<0.001;~r_{med}=0.94,~p_{med}<0.001;~r_{hi} = 0.97,~p_{hi}<0.001$).
 Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data interval, indicating less consistency in the time-to-target results for participants with severe sight impairments.
 This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}, as well as the mean age and general level of expertise with mobile devices of this particular group.
-Nevertheless, all three settings exhibit strong Pearson correlation scores ($r_{lo}=0.71,~p=0.005;r_{med}=0.85,~p_{med}<0.001;~r_{hi}=0.84,~p_{hi}<0.001$).}
+Nevertheless, all three settings exhibit strong Pearson correlation scores ($r_{lo}=0.71,~p=0.005;r_{med}=0.85,~p_{med}<0.001;~r_{hi}=0.84,~p_{hi}<0.001$).
 
@@
 For Group~\textit{G1}, there is a fairly consistent level of performance between the three settings, with \textit{med} producing the highest indices of performance overall (i.e.\ the participants found the targets with the smallest error and in the least amount of time).
-\hl{This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{med} setting is significantly different to the \textit{lo} and \textit{hi} settings ($p_{med-lo} < 0.001,~p_{med-hi} < 0.001$).
+This is supported by the results from the Friedman test, showing that there is a significant difference in performance between the settings ($p < 0.001$), as well as post-hoc Wilcoxon tests with Holm-Bonferroni corrections, which show that the \textit{med} setting is significantly different to the \textit{lo} and \textit{hi} settings ($p_{med-lo} < 0.001,~p_{med-hi} < 0.001$).
 The \textit{lo} and \textit{hi} settings, instead, are not significantly different from each other ($p_{lo-hi} = 0.11$).
@@
 Following visual inspection of the distribution and significant results from the Friedman test ($p < 0.001$), it is clear that the \textit{hi} setting produces the highest performance by a large margin, compared to the \textit{lo} and \textit{med} settings.
-This is supported by Wilcoxon tests ($p_{lo-hi}=0.01$, $p_{med-hi}=0.01$), which also show that the results for the \textit{lo} and \textit{med} settings are not different ($p_{lo-med}=0.09$).}
+This is supported by Wilcoxon tests ($p_{lo-hi}=0.01$, $p_{med-hi}=0.01$), which also show that the results for the \textit{lo} and \textit{med} settings are not different ($p_{lo-med}=0.09$).
 
@@
 
-\hl{Since the Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
+Since the Fitts's model we used here is based on the target estimation errors, it is reasonable to expect that the accuracy and time performances will follow similar trends. 
 Indeed, this seems to be the case, with the \textit{hi} pitch setting producing the lowest target acquisition error, followed by the \textit{med} and \textit{lo} settings, respectively. 
@@
 Indeed, Group \textit{G2} seems to respond better to the increased movement resolution that the \textit{hi} affords the user, allowing for finer adjustments to be made to the device's orientation to get closer to the target.
-With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. }
+With the Fitts model discussed here, we can empirically evaluate any changes we make to the audio interface and optimise the parameters it to produce the desired output. 
 %However, this trend is almost wholly reversed in the time-to-target results from the Fitts model, where the \textit{lo} setting gives the highest level of performance, followed by the \textit{hi} and \textit{med} settings respectively.
